### 2023-10-24 Paper/tex/bifacial_peak_shaving_paper.tex
first commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{why-peak-load}{%
\subsection{Why peak load}\label{why-peak-load}}

The world right now requires a quick and efficient transition of most
energy usage to electric and most energy production to renewable
sources. With this changing energy paradigm will come a larger emphasis
on peak load management. Electric load growth from equipment like EV
charging and heat pumps will likely out pace distribution capacity
growth in many areas.

Public EV chargers may especially suffer from a low load factor due to
the convenience of fast charging at high power. Heat pump load factor
may be increased with architectural features such as insulation and
thermal storage, but worsening extreme weather events and challenges to
building efficiency retrofits will mean this can not be achieved
everywhere. And relative to the marginal cost of additional kWh of
energy, the marginal cost of additional kW of peak power is quite
expensive because it necessarily requires new grid infrastructure like
transformers and lines.

Distribution and transmission companies are well aware of this problem,
but infrastructure upgrades are often slowed down by regulation and
permitting. In regulatory areas where companies can own both generation
and distribution, business-as-usual grid upgrades may be prioritized
over construction of new renewable generation, which can often be
complex projects with more difficult permitting and less certain
returns. Largely due to these factors consumer prices on monthly and
annual peak load are generally increasing around the world.

\hypertarget{peak-shaving}{%
\subsection{Peak shaving}\label{peak-shaving}}

Peak load management, or peak shaving, essentially requires choosing a
power threshold and holding the load power below it. Controllable loads,
energy storage, or generation assets behind the billing meter can all be
used to reduce the load power to the threshold power. The threshold may
only apply for only certain time periods. There may be multiple
thresholds and periods each day, month, or year. There are two general
cases of peak shaving worth considering. The most generation formulation
of peak shaving control is formulated in Equation 1.

\begin{figure}
\centering
\includegraphics[width=3in,height=\textheight]{16932411489031.png}
\caption{Figure C: General schematic of case studies. The site is connected
to the electricity utility and pays for consumption according to the
electric meter. Because solar is connected behind the meter it is
directly useful for reducing the site load, and since it has a zero
marginal cost it is always dispatched at maximum available power. The
battery could be said to working on maintaining the net load below the
peak shaving threshold, where net load is load less solar.}
\end{figure}

\begin{equation}
  \begin{align}
I_{load,t} - \Sigma_i I_{gen,i,t} - \Sigma_j I_{gen\uarr,j,t} - \Sigma_k I_{load\darr,k,t} < I_{threshold,t} \\
where \\
i=generation\ asset\ with\ no\ flexibility \\
j=generation\ asset\ with\ upward\ flexibility \\
k=controllable\ load\ asset\ with\ downward\ flexibility \\
t=applicable\ timesteps\
  \end{align}
\end{equation}

Here we consider the case of no controllable load, a single battery,
solar which reduces the site load, and all values in units of average
real power over the interval \(\Delta h = 1\ hour\).

\[(2)\ P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}  < P_{threshold,h} \\
where \\
P_{batt,discharge,h} \ge 0 \\
P_{batt,charge,h} \le 0 \\
h \in \{0,1,2,...23\} \\\]

\hypertarget{technical-case}{%
\subsection{Technical case}\label{technical-case}}

Technical peak shaving refers to the case where a load must operate
under a technical limitation such as a maximum power agreement or
distribution transformer size. The load power must remain under the
threshold at all times, otherwise there may be a technical failure such
an activated overcurrent protection. Even if the load is technically
able to rise above the threshold, doing so may violate a contract
regarding maximum load power. The important consideration is that the
economic cost of failure to hold the load under the threshold is
prohibitively high. The time resolution of technical peak shaving
control and modeling may need to be as low as seconds or milliseconds.
Although this may be a challenging problem if the current limit is
dynamically set or if a larger network is considered, from the
perspective of dispatching the assets to shave the peak the problem is a
relatively simple one: economic dispatch such that the the load current
remains below the threshold current. Technical peak shaving might be
performed on current or apparent power rather than active power.

\begin{figure}
\centering
\includegraphics{/home/mjw/Insync/michael.wood@mugrid.com/Google Drive - Shared drives/Polimi/Publications/Bifacial solar and peakshaving/bifacial_peak_shaving_paper.assets/tech_shaving.png}
\caption{technical peak shaving}
\end{figure}

\emph{Figure A: The threshold is 20 kW. The battery begins the day full
at 100 kWh. By 8:00 the load has increased above the threshold to 25 kW,
but solar has also increased to 9 kW, so the site load is still below
the threshold. However at 9:00 the battery must discharge at 13 kW to
reduce to site load to 20 kW. At 12:00 the battery can recharge somewhat
due to an increase in solar and slight decrease in load. Then by 18:00
the load is less than the threshold and the battery can recharge,
increasing the site load up to the threshold.}

An example of technical peak shaving with a threshold of 20 kW is seen
in Figure A. The actual load climbs well above the threshold, but the
solar energy for that day reduces the site load considerably. Battery
discharge is required in the morning and afternoon to keep the site load
below the threshold, with some opportunistic midday charging. The
battery recharges in the evening and overnight.

\hypertarget{economic-case}{%
\subsection{Economic case}\label{economic-case}}

Rather, economic peak shaving aims to reduce what a consumer pays for
power and possibly also energy. Medium and large electric consumers
often pay a price on energy (€\(/kWh\)) and a price on power
(€\(/kWh_{peak}\)), which is often referred to as a demand charge. The
energy cost (€\(/kWh \times E_{consumed}\)) may vary with time of day,
day of week, and season of the year, which is often referred to as time
of use or peak pricing. Where there is a sufficient spread between the
peak and off-peak prices there may be the opportunity to curtail load
during high prices, use controllable loads to shift from a high price
period to a lower one, or to use energy storage to buy energy at the
lower price and reduce load during a higher price period. Instead, the
power cost (€\(/kW \times P_{max}\) ) typically applies to the max power
during the billing period, where the peak power is the average power
measured over a short interval (often 15 or 60 minutes) and only applies
to a peak period (such as )

The peak power is typically defined as the maximum load power during
certain hours of the day for a certain billing period. The peak is
calculated from a non-moving average, with a typical interval of 15
minutes or one hour.

\begin{figure}
\centering
\includegraphics{/home/mjw/Insync/michael.wood@mugrid.com/Google Drive - Shared drives/Polimi/Publications/Bifacial solar and peakshaving/bifacial_peak_shaving_paper.assets/econ_shaving.png}
\caption{}
\end{figure}

\emph{Figure B: The threshold is comprised of two parts: Threshold0 at
20 kW from 12:00-18:00, and Threshold1 at 40 kW from 9:00-12:00 and
18:00-21:00. The battery begins the day full at 100 kWh. By 9:00 the
load has increased above Threshold0, solar decreases this greatly, and
the battery is discharged to further reduce the site load. However at
9:00 the battery must discharge at 13 kW to reduce to site load to 20
kW. At 11:00 and 12:00 the battery can recharge somewhat due to an
increase in solar and slight decrease in load. Then by 18:00 the load is
significantly less than the threshold and the battery can recharge,
increasing the site load up to the threshold.}

Solar contributes significantly to the load, but once the peak period
begins the battery must discharge to keep the

\begin{longtable}[]{@{}lll@{}}
\toprule
Feature & Technical Peak Shaving & Economic Peak Shaving\tabularnewline
\midrule
\endhead
Cost of violating the threshold & Prohibitively high & Depends on
tariff\tabularnewline
Averaging interval & \textless\textless{} 1 minute & 15 minutes or 1
hour (typical)\tabularnewline
Valid times of day & All & Limited (e.g. 16:00 to 21:00)\tabularnewline
Peak is reset every.. & Never & Month, year, day
(typical)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{bibliography}{%
\section{Bibliography}\label{bibliography}}

\end{document}

### 2023-10-24 Versions/230720/bifacial_peak_shaving.py

@@ -1,0 +1,124 @@
+""" Bifacial Peak Shaving
+"""
+import pandas as pd
+from _utils import *
+
+def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
+    all_results = pd.DataFrame(columns=['TOU begin [h]',
+                                        'TOU end [h]',
+                                        'max peak reduction [kW]',
+                                        'avg peak reduction [kW]',
+                                        'min peak reduction [kW]'])
+    for peak_begin in list(range(8,21)):
+        for peak_end in list(range(9,22)):
+            if (peak_end-peak_begin) >= 2:
+                peaks = calc_monthly_peaks(df[f'netload_{angle1}'],peak_begin,peak_end)
+                
+                peaks = pd.concat((peaks,calc_monthly_peaks(df[f'netload_{angle2}'],
+                                                            peak_begin,peak_end)),
+                                  axis=1)
+                peaks['peak_reduction'] = peaks[f'netload_{angle1} kw'] - peaks[f'netload_{angle2} kw']
+                
+                pr_max = peaks.peak_reduction.max().round(1)
+                pr_avg = peaks.peak_reduction.mean().round(1)
+                pr_min = peaks.peak_reduction.min().round(1)
+                #print(f'{peak_begin:3d} {peak_end:3d} -- {pr_max:7.2f} {pr_avg:7.2f} {pr_min:7.2f}')
+                all_results.loc[len(all_results)] = [peak_begin,peak_end,pr_max,pr_avg,pr_min]
+                #results
+                
+    all_results['TOU begin [h]'] = all_results['TOU begin [h]'].astype(int)
+    all_results['TOU end [h]'] = all_results['TOU end [h]'].astype(int)
+    return all_results
+
+def batt_request(soe,power,soe0):
+    if len(soe) == 0:
+        last_soe = soe0
+    else:
+        last_soe = soe[-1]
+        
+    if power > 0: # discharge
+        power = min(power,last_soe*0.9)
+    elif power < 0: # charge
+        power = max(power,-1*(soe0-last_soe)/.9)
+    else:
+        power = 0
+    return power
+
+def update_soe(soe,power,soe0):
+    if len(soe) == 0:
+        last_soe = soe0
+    else:
+        last_soe = soe[-1]
+            
+    if power > 0: # discharge
+        next_soe = last_soe - power/0.9
[…]

### 2023-10-24 Versions/230720/utils.py

@@ -1,0 +1,247 @@
+""" utils.py
+Generally useufl utility functions
+"""
+
+import pandas as pd
+import plotly.graph_objects as go
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+from plotly.subplots import make_subplots  
+
+def plot_weekly(ds,
+                title:str=None,
+                ylabel:str=None,
+                interval_min:int=60,
+                alpha:float=0.1,
+                begin_on_monday:bool=True,
+                colors:list=['indigo','gold','magenta']):
+    """ Plot a series with weeks super-imposed on each other. Index should be complete (no gaps)
+    for this to work right. Trims any remaining data after an integer number of weeks.
+
+    Args:
+        ds (pd.Series or list): pandas series(es) to plot
+        title (str, optional): title
+        ylabel (str, optional): what to call the y-axis        
+        interval_min (int): timeseries data interval
+        alpha (float, optional): transparency of plot lines, defaults to 0.1
+        begin_on_monday (bool, optional): have the first day on the plot be monday, defaults to True
+        colors (list, optional): list of colors strings
+    """
+    dpd = int(24*60/interval_min) # data per day
+    plt.figure(figsize=(10,5))
+    t = [x/dpd for x in range(7*dpd)] # days    
+    if not isinstance(ds,(list,tuple)):
+        ylabel = ds.name
+        ds = [ds]
+    for ds2,color in zip(ds,colors):
+        ds2 = ds2.copy(deep=True)
+        dt_start = ds2.index.min()
+        if dt_start != dt_start.floor('1d'):
+            dt_start = dt_start.floor('1d') + pd.Timedelta(hours=24)
+        if begin_on_monday and (dt_start.weekday() != 0):
+            days = 7 - dt_start.weekday()
+            dt_start += pd.Timedelta(hours=24*days)
+        ds2 = ds2[dt_start:]
+        n_weeks = len(ds2)//(7*dpd)
+        ds2 = ds2.iloc[:int(n_weeks*7*dpd)]
+        if len(ds)>1:
+            plt.plot(t,ds2.values.reshape(n_weeks,7*dpd).T,color,alpha=alpha)
+        else:
+            plt.plot(t,ds2.values.reshape(n_weeks,7*dpd).T,alpha=alpha)
+    plt.ylabel(ylabel)
+    plt.xlabel('Days from Monday 0:00')
+    plt.title(title)
+    if len(ds)>1:
+        legend_items = []
+        for s,color in zip(ds,colors):
[…]

### 2023-10-24 Versions/caltech_ev_mjw3.py

@@ -1,0 +1,273 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech_profile_1y.csv',
+                   #index_col=0,
+                   #parse_dates=True,
+                   comment='#',
+                   usecols=[2],
+                   )
+                    #.resample('1h').mean()
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.resample('1h').mean()
+print(load.info())
+#plot_weekly(load['Load (kW)'])
+#load.plot()
+
+# %%
+#load.plot.box(x=load.index,y=load['Load (kW)'])
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w20','w90','s20w90']
+solar = pd.concat(( 
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_s20deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w20deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w90deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_3.5kwp_s20deg_3.5kwp_w90deg.csv',index_col=0),
+                   ),
+                  axis=1)
[…]

### 2023-10-24 Versions/caltech_ev_mjw4.py

@@ -1,0 +1,546 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech_profile_1y.csv',
+                   #index_col=0,
+                   #parse_dates=True,
+                   comment='#',
+                   usecols=[2],
+                   )
+                    #.resample('1h').mean()
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.resample('1h').mean()
+print(load.info())
+#plot_weekly(load['Load (kW)'])
+#load.plot()
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w20','w90','s20w90']
+solar = pd.concat(( 
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_s20deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w20deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w90deg.csv',index_col=0),
+                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_3.5kwp_s20deg_3.5kwp_w90deg.csv',index_col=0),
+                   ),
+                  axis=1)
+solar.index = pd.date_range('1900-1-1 0:00',periods=8760,freq='1h')
+solar.columns = solar_angles
[…]

### 2023-10-24 Versions/caltech_ev_mjw5.py

@@ -1,0 +1,542 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech.csv',
+                   index_col=0,
+                   parse_dates=True,
+                   comment='#',
+                   )
+                    #.resample('1h').mean()\
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.fillna(method='ffill')
+load = load.resample('1h').mean()
+print(load.info())
+#plot_weekly(load['Load (kW)'])
+#load.plot()
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w90']
+
+s20 = pd.concat((pd.read_csv(dir+'Solar/Modelled/pasadena_2018_1h_367mods_s20.csv',index_col=0,parse_dates=True),
+                 pd.read_csv(dir+'Solar/Modelled/pasadena_2019_1h_367mods_s20.csv',index_col=0,parse_dates=True)))
+
+w90 = pd.concat((pd.read_csv(dir+'Solar/Modelled/pasadena_2018_1h_367mods_w90.csv',index_col=0,parse_dates=True),
+                 pd.read_csv(dir+'Solar/Modelled/pasadena_2019_1h_367mods_w90.csv',index_col=0,parse_dates=True)))
+
+solar = pd.concat((s20,w90),axis=1)
+solar.columns=solar_angles
+
+solar = solar.loc[load.index]
+
[…]

### 2023-10-24 Versions/caltech_ev_mjw6.py

@@ -1,0 +1,578 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech.csv',
+                   index_col=0,
+                   parse_dates=True,
+                   comment='#',
+                   )
+                    #.resample('1h').mean()\
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.fillna(method='ffill')
+#interval_min = int(load.index.to_series().diff().mean().seconds/60)
+load = load.resample('60min').mean()
+load = load.loc['2018-5-1':'2019-2-28']
+print(load.info())
+plot_weekly(load['Load (kW)'])
+load.plot()
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w90']
+
+dir_solar = dir+'Solar/Modelled/'
+
+s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
+                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
+
+w90 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_w90.csv',index_col=0,parse_dates=True,comment='#'),
[…]

### 2023-10-24 bifacial_peak_shaving.py

@@ -1,0 +1,273 @@
+""" Bifacial Peak Shaving
+"""
+import math
+import pandas as pd
+from _utils import *
+
+def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
+    all_results = pd.DataFrame(columns=['TOU begin [h]',
+                                        'TOU end [h]',
+                                        'max peak reduction [kW]',
+                                        'avg peak reduction [kW]',
+                                        'min peak reduction [kW]'])
+    for peak_begin in list(range(8,21)):
+        for peak_end in list(range(9,22)):
+            if (peak_end-peak_begin) >= 2:
+                peaks = calc_monthly_peaks(df[f'netload_{angle1}'],peak_begin,peak_end)
+                
+                peaks = pd.concat((peaks,calc_monthly_peaks(df[f'netload_{angle2}'],
+                                                            peak_begin,peak_end)),
+                                  axis=1)
+                peaks['peak_reduction'] = peaks[f'netload_{angle1} kw'] - peaks[f'netload_{angle2} kw']
+                
+                pr_max = peaks.peak_reduction.max().round(1)
+                pr_avg = peaks.peak_reduction.mean().round(1)
+                pr_min = peaks.peak_reduction.min().round(1)
+                #print(f'{peak_begin:3d} {peak_end:3d} -- {pr_max:7.2f} {pr_avg:7.2f} {pr_min:7.2f}')
+                all_results.loc[len(all_results)] = [peak_begin,peak_end,pr_max,pr_avg,pr_min]
+                #results
+                
+    all_results['TOU begin [h]'] = all_results['TOU begin [h]'].astype(int)
+    all_results['TOU end [h]'] = all_results['TOU end [h]'].astype(int)
+    return all_results
+
+def update_soe(soe:list,power:float,soe0:float,interval_min:int=60)->float:
+    """Update state of energy from actual battery power
+
+    Args:
+        soe (list of floats): state of energy vector
+        power (float): battery power (+ is discharge, - is charge)
+        soe0 (float): initial state of energy
+
+    Returns:
+        float: next timestep state of energy
+    """
+    if len(soe) == 0:
+        last_soe = soe0
+    else:
+        last_soe = soe[-1]
+
[…]

### 2023-10-24 caltech_ev_mjw7.py

@@ -1,0 +1,583 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+output_filename = 'Output/caltech_ev_mjw7__output__15min-noScaling-peak16-21__'+pd.Timestamp.now().strftime('%y-%m-%d_%H-%M-%S')+'.csv'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech.csv',
+                   index_col=0,
+                   parse_dates=True,
+                   comment='#',
+                   )
+                    #.resample('1h').mean()\
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.fillna(method='ffill')
+#interval_min = int(load.index.to_series().diff().mean().seconds/60)
+#load = load.resample('1h').mean()
+load = load.loc['2018-5-1':'2019-2-28']
+print(load.info())
+#plot_weekly(load['Load (kW)'])
+#load.plot()
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w90','s20w90']
+
+dir_solar = dir+'Solar/Modelled/'
+
+s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
+                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
+
[…]

### 2023-10-24 caltech_ev_mjw7b.py

@@ -1,0 +1,585 @@
+# %%
+import pandas as pd
+from bifacial_peak_shaving import *
+from _utils import *
+pd.options.plotting.backend='plotly'
+
+# %% [markdown]
+# # Data
+
+# %%
+dir = './Data/'
+output_filename = 'Output/caltech_ev_mjw7b__output__15min-doubleSolar-peak16-21__'+pd.Timestamp.now().strftime('%y-%m-%d_%H-%M-%S')+'.csv'
+
+# %% [markdown]
+# ## Load
+
+# %%
+load = pd.read_csv(dir+'acn_caltech.csv',
+                   index_col=0,
+                   parse_dates=True,
+                   comment='#',
+                   )
+                    #.resample('1h').mean()\
+                    #.fillna(method='ffill')
+                    #.loc['2018-4-26':'2019-3-22']
+#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
+#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
+#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
+#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
+#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
+load = load.fillna(method='ffill')
+#interval_min = int(load.index.to_series().diff().mean().seconds/60)
+#load = load.resample('1h').mean()
+load = load.loc['2018-5-1':'2019-2-28']
+print(load.info())
+#plot_weekly(load['Load (kW)'])
+#load.plot()
+
+# %% [markdown]
+# ## Solar
+# 
+# - 7 kWp, TMY
+# 
+# - Net zero capacity
+# 
+#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
+
+# %%
+solar_angles = ['s20','w90','s20w90']
+
+dir_solar = dir+'Solar/Modelled/'
+
+s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
+                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
+
[…]

### 2023-10-24 data_processing.py

@@ -1,0 +1,1204 @@
+__version__ = '0.0.1'
+
+
+from os import listdir
+from configparser import ConfigParser
+from numpy import array, arange, nan, std, mean, sin, concatenate, argmax, pi, fft, empty, logical_and, abs, corrcoef, exp
+import numpy as np
+from pandas import DataFrame, infer_freq, read_csv, read_excel, date_range, concat, options, Timestamp, Timedelta, to_datetime, concat
+from scipy.optimize import curve_fit
+#from statsmodels.tsa.seasonal import STL
+import matplotlib.pyplot as plt
+
+import math
+import pandas as pd
+import plotly.graph_objects as go
+import matplotlib.patches as mpatches
+from plotly.subplots import make_subplots  
+
+# Versions
+# 1.0 - option to define dir
+
+"""
+Notes
+
+1. try define all the right inputs to DataClass() and import_data(), otherwise make a good guess
+2. no need for a config file now
+3. all this code assumed the raw input data is in kw or kwh (otherwise convert manually)
+4. for the year profile, there is untested code at the end of the file.. or do it manually
+5. for me "df" (dataframe) is real measured data (but maybe cleaned)
+    - whereas "profile" includes estimations (e.g. we dont have data for 9/2022 but it could be..)
+"""
+
+#
+#
+# Classes
+#
+#
+
+class Data:
+    def __init__(me, name, interval, timezone, max_export=None, main_breaker_rating_A=None, n_phases=3, voltage_ln_V=120, theme='plotly_white', egauge=False, dir='', config_file=True, units='kW'):
+        options.plotting.backend = 'plotly' 
+        me.theme = theme
+        me.name = name
+        me.interval = me.interval_lookup(interval) # prefer to use df.index.freq
+        me.interval_h = {'1S':1/3600, '1T':1/60, '15T':0.25, '1H':1, '6H':6}[me.interval]
+        me.timezone_name = timezone
+        me.timezone = me.timezone_lookup(timezone)
+        me.df = DataFrame([])
+        me.units = units
+        me.rolling_stdev = []
+        me.rolling_mean = []
+        me.np = nan # best naive persistence according to autocorrelation
+        me.nan = nan # convenient to have
+        me.profile = DataFrame( [], 
+                                index=date_range(   start='2022-1-1 0:00', 
+                                                    end='2022-12-31 23:45',
+                                                    freq='15T'              ),
[…]

### 2023-10-24 bifacial_peak_shaving.py
various cleanup

@@ -2,7 +2,8 @@
 """
 import math
 import pandas as pd
-from _utils import *
+#from _utils import *
+from data_processing import *
 
 def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
     all_results = pd.DataFrame(columns=['TOU begin [h]',
@@ -20,9 +21,9 @@ def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
                                   axis=1)
                 peaks['peak_reduction'] = peaks[f'netload_{angle1} kw'] - peaks[f'netload_{angle2} kw']
                 
-                pr_max = peaks.peak_reduction.max().round(1)
-                pr_avg = peaks.peak_reduction.mean().round(1)
-                pr_min = peaks.peak_reduction.min().round(1)
+                pr_max = round(peaks.peak_reduction.max(),1)
+                pr_avg = round(peaks.peak_reduction.mean(),1)
+                pr_min = round(peaks.peak_reduction.min(),1)
                 #print(f'{peak_begin:3d} {peak_end:3d} -- {pr_max:7.2f} {pr_avg:7.2f} {pr_min:7.2f}')
                 all_results.loc[len(all_results)] = [peak_begin,peak_end,pr_max,pr_avg,pr_min]
                 #results

### 2023-10-24 data_processing.py

@@ -876,7 +876,8 @@ def calc_monthly_peaks(ds:pd.Series,peak_begin:int,peak_end:int) -> pd.Series:
         for month in ds_year.index.month.unique():
             ds_month = ds_year[ds_year.index.month==month]
             idx = [peak_begin<=h<peak_end for h in ds_month.index.hour]
-            r.loc[len(r)] = [ds_month[idx].max().round(1),ds_month[idx].idxmax()]
+            r.loc[len(r)] = [round(ds_month[idx].max(),1),
+                             ds_month[idx].idxmax()]
     return r
 
 

### 2023-10-27 bifacial_peak_shaving.py
5 min timestep, paper work

@@ -5,7 +5,19 @@ import pandas as pd
 #from _utils import *
 from data_processing import *
 
-def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
+def net_load_peak_reduction_variable_TOU(df:pd.DataFrame,angle1:str,angle2:str)->pd.DataFrame:
+    """Calculate the reduction of peak net load for a range of TOU windows
+    
+    MAY NOT WORK CORRECTLY
+
+    Args:
+        df (pd.DataFrame): net load data
+        angle1 (str): reference angle (usually s20)
+        angle2 (str): comparison angle
+
+    Returns:
+        pd.DataFrame: results
+    """
     all_results = pd.DataFrame(columns=['TOU begin [h]',
                                         'TOU end [h]',
                                         'max peak reduction [kW]',
@@ -111,7 +123,7 @@ def peak_shaving_sim_old(df2,nl_col,threshold,soe0,TOU_hours,soe_max=None):
     
     return any( df2[[tou_first<=h<=tou_last for h in df2.index.hour]].utility>(threshold+tol) ), df2
 
-def peak_shaving_sim(df:pd.DataFrame,
+def peak_shaving_sim( df:pd.DataFrame,
                       netload_col:str,
                       soe_max:float,                      
                       thresholds:list=None,
@@ -122,10 +134,12 @@ def peak_shaving_sim(df:pd.DataFrame,
     """Simulate peak shaving battery dispatch
 
     Args:
-        ds_netload (pd.Series): net load vector
+        df (pd.DataFrame): load solar and netload data
+        netload_col (str): netload column name
+        soe_max (float): maximum battery state of energy
         thresholds (float): battery will be dispatched to keep import from utility below this value
             during threshold_h
-        soe_max (float): maximum battery state of energy
+        TOU (list of dicts): list of TOU dicts like {'price':float and 'hours':list of ints}
         soe0 (float): initial battery state of energy
         utility_chg_max (float, optional): max absolute value that battery will charge at during 
             non-TOU hours. Defaults to 0.

### 2023-10-27 data_processing.py

@@ -843,11 +843,11 @@ def order_of_magnitude(x:float)->int:
     return math.floor(math.log(x, 10))
 
 
-def upsample_df(df,periods,freq,method='ffill'):
+def upsample_ffill(df,periods,freq):
     df2 = pd.DataFrame([],index=pd.date_range(df.index[0],periods=periods,freq=freq))
     for col in df.columns:
         df2.loc[df.index,col] = df[col].values
-    df2 = df2.fillna(method=method)
+    df2 = df2.fillna(method='ffill')
     return df2
 
 
@@ -904,8 +904,8 @@ def plot_daily(ds:pd.Series,
     n_days = len(ds2)//(dpd)
     ds2 = ds2.iloc[:int(n_days*dpd)]
     
-    t = list(range(24)) # hours
-    plt.plot(t, ds2.values.reshape(n_days,dpd).T,alpha=alpha)
+    #t = list(range(24)) # hours
+    plt.plot(ds2.values.reshape(n_days,dpd).T,alpha=alpha)
     plt.ylabel(ds.name)
     plt.xlabel('Hours from 0:00')
     plt.title(title)
@@ -1010,7 +1010,7 @@ def plotly_stacked(_df:pd.DataFrame,
     if upsample_min is not None:
         freq_min = int(df.index.to_series().diff().dropna().mean().seconds/60)
         new_length = len(df) * (freq_min / upsample_min)
-        df = upsample_df(df,freq=f'{upsample_min}min',periods=new_length)
+        df = upsample_ffill(df,freq=f'{upsample_min}min',periods=new_length)
         
     # threshold vectors
     if threshold0 is not None:

### 2023-10-27 bifacial_peak_shaving.py
BUG FOUND! cost calc was sometimes negative

@@ -247,7 +247,8 @@ def calc_power_cost(ds:pd.Series,tou:list,peak_interval_min:int=60)->float:
     cost = 0
     for tou_level in tou:
         price,hours = tou_level['price'],tou_level['hours']
-        cost += ds[[True if h in hours else False for h in ds.index.hour]].max() * price
+        max_power = ds[[True if h in hours else False for h in ds.index.hour]].max()
+        cost += max(0,max_power) * price
     return cost
 
 

### 2023-10-27 caltech_ev_mjw7.py

@@ -1,583 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-output_filename = 'Output/caltech_ev_mjw7__output__15min-noScaling-peak16-21__'+pd.Timestamp.now().strftime('%y-%m-%d_%H-%M-%S')+'.csv'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech.csv',
-                   index_col=0,
-                   parse_dates=True,
-                   comment='#',
-                   )
-                    #.resample('1h').mean()\
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.fillna(method='ffill')
-#interval_min = int(load.index.to_series().diff().mean().seconds/60)
-#load = load.resample('1h').mean()
-load = load.loc['2018-5-1':'2019-2-28']
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w90','s20w90']
-
-dir_solar = dir+'Solar/Modelled/'
-
-s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
-                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
-
[…]

### 2023-10-27 caltech_ev_mjw7a.py

@@ -1,585 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-output_filename = 'Output/caltech_ev_mjw7a__output__15min-halfSolar-peak16-21__'+pd.Timestamp.now().strftime('%y-%m-%d_%H-%M-%S')+'.csv'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech.csv',
-                   index_col=0,
-                   parse_dates=True,
-                   comment='#',
-                   )
-                    #.resample('1h').mean()\
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.fillna(method='ffill')
-#interval_min = int(load.index.to_series().diff().mean().seconds/60)
-#load = load.resample('1h').mean()
-load = load.loc['2018-5-1':'2019-2-28']
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w90','s20w90']
-
-dir_solar = dir+'Solar/Modelled/'
-
-s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
-                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
-
[…]

### 2023-12-07 Versions/230720/bifacial_peak_shaving.py
dont track tex files and old vers

@@ -1,124 +1,0 @@
-""" Bifacial Peak Shaving
-"""
-import pandas as pd
-from _utils import *
-
-def net_load_peak_reduction_variable_TOU(df,angle1,angle2):
-    all_results = pd.DataFrame(columns=['TOU begin [h]',
-                                        'TOU end [h]',
-                                        'max peak reduction [kW]',
-                                        'avg peak reduction [kW]',
-                                        'min peak reduction [kW]'])
-    for peak_begin in list(range(8,21)):
-        for peak_end in list(range(9,22)):
-            if (peak_end-peak_begin) >= 2:
-                peaks = calc_monthly_peaks(df[f'netload_{angle1}'],peak_begin,peak_end)
-                
-                peaks = pd.concat((peaks,calc_monthly_peaks(df[f'netload_{angle2}'],
-                                                            peak_begin,peak_end)),
-                                  axis=1)
-                peaks['peak_reduction'] = peaks[f'netload_{angle1} kw'] - peaks[f'netload_{angle2} kw']
-                
-                pr_max = peaks.peak_reduction.max().round(1)
-                pr_avg = peaks.peak_reduction.mean().round(1)
-                pr_min = peaks.peak_reduction.min().round(1)
-                #print(f'{peak_begin:3d} {peak_end:3d} -- {pr_max:7.2f} {pr_avg:7.2f} {pr_min:7.2f}')
-                all_results.loc[len(all_results)] = [peak_begin,peak_end,pr_max,pr_avg,pr_min]
-                #results
-                
-    all_results['TOU begin [h]'] = all_results['TOU begin [h]'].astype(int)
-    all_results['TOU end [h]'] = all_results['TOU end [h]'].astype(int)
-    return all_results
-
-def batt_request(soe,power,soe0):
-    if len(soe) == 0:
-        last_soe = soe0
-    else:
-        last_soe = soe[-1]
-        
-    if power > 0: # discharge
-        power = min(power,last_soe*0.9)
-    elif power < 0: # charge
-        power = max(power,-1*(soe0-last_soe)/.9)
-    else:
-        power = 0
-    return power
-
-def update_soe(soe,power,soe0):
-    if len(soe) == 0:
-        last_soe = soe0
-    else:
-        last_soe = soe[-1]
-            
-    if power > 0: # discharge
-        next_soe = last_soe - power/0.9
[…]

### 2023-12-07 Versions/230720/utils.py

@@ -1,247 +1,0 @@
-""" utils.py
-Generally useufl utility functions
-"""
-
-import pandas as pd
-import plotly.graph_objects as go
-import matplotlib.pyplot as plt
-import matplotlib.patches as mpatches
-from plotly.subplots import make_subplots  
-
-def plot_weekly(ds,
-                title:str=None,
-                ylabel:str=None,
-                interval_min:int=60,
-                alpha:float=0.1,
-                begin_on_monday:bool=True,
-                colors:list=['indigo','gold','magenta']):
-    """ Plot a series with weeks super-imposed on each other. Index should be complete (no gaps)
-    for this to work right. Trims any remaining data after an integer number of weeks.
-
-    Args:
-        ds (pd.Series or list): pandas series(es) to plot
-        title (str, optional): title
-        ylabel (str, optional): what to call the y-axis        
-        interval_min (int): timeseries data interval
-        alpha (float, optional): transparency of plot lines, defaults to 0.1
-        begin_on_monday (bool, optional): have the first day on the plot be monday, defaults to True
-        colors (list, optional): list of colors strings
-    """
-    dpd = int(24*60/interval_min) # data per day
-    plt.figure(figsize=(10,5))
-    t = [x/dpd for x in range(7*dpd)] # days    
-    if not isinstance(ds,(list,tuple)):
-        ylabel = ds.name
-        ds = [ds]
-    for ds2,color in zip(ds,colors):
-        ds2 = ds2.copy(deep=True)
-        dt_start = ds2.index.min()
-        if dt_start != dt_start.floor('1d'):
-            dt_start = dt_start.floor('1d') + pd.Timedelta(hours=24)
-        if begin_on_monday and (dt_start.weekday() != 0):
-            days = 7 - dt_start.weekday()
-            dt_start += pd.Timedelta(hours=24*days)
-        ds2 = ds2[dt_start:]
-        n_weeks = len(ds2)//(7*dpd)
-        ds2 = ds2.iloc[:int(n_weeks*7*dpd)]
-        if len(ds)>1:
-            plt.plot(t,ds2.values.reshape(n_weeks,7*dpd).T,color,alpha=alpha)
-        else:
-            plt.plot(t,ds2.values.reshape(n_weeks,7*dpd).T,alpha=alpha)
-    plt.ylabel(ylabel)
-    plt.xlabel('Days from Monday 0:00')
-    plt.title(title)
-    if len(ds)>1:
-        legend_items = []
-        for s,color in zip(ds,colors):
[…]

### 2023-12-07 Versions/caltech_ev_mjw3.py

@@ -1,273 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech_profile_1y.csv',
-                   #index_col=0,
-                   #parse_dates=True,
-                   comment='#',
-                   usecols=[2],
-                   )
-                    #.resample('1h').mean()
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.resample('1h').mean()
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %%
-#load.plot.box(x=load.index,y=load['Load (kW)'])
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w20','w90','s20w90']
-solar = pd.concat(( 
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_s20deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w20deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w90deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_3.5kwp_s20deg_3.5kwp_w90deg.csv',index_col=0),
-                   ),
-                  axis=1)
[…]

### 2023-12-07 Versions/caltech_ev_mjw4.py

@@ -1,546 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech_profile_1y.csv',
-                   #index_col=0,
-                   #parse_dates=True,
-                   comment='#',
-                   usecols=[2],
-                   )
-                    #.resample('1h').mean()
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.resample('1h').mean()
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w20','w90','s20w90']
-solar = pd.concat(( 
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_s20deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w20deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_7kwp_w90deg.csv',index_col=0),
-                    pd.read_csv(dir+'Solar/Modelled/lemooreCA_3.5kwp_s20deg_3.5kwp_w90deg.csv',index_col=0),
-                   ),
-                  axis=1)
-solar.index = pd.date_range('1900-1-1 0:00',periods=8760,freq='1h')
-solar.columns = solar_angles
[…]

### 2023-12-07 Versions/caltech_ev_mjw5.py

@@ -1,542 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech.csv',
-                   index_col=0,
-                   parse_dates=True,
-                   comment='#',
-                   )
-                    #.resample('1h').mean()\
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.fillna(method='ffill')
-load = load.resample('1h').mean()
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w90']
-
-s20 = pd.concat((pd.read_csv(dir+'Solar/Modelled/pasadena_2018_1h_367mods_s20.csv',index_col=0,parse_dates=True),
-                 pd.read_csv(dir+'Solar/Modelled/pasadena_2019_1h_367mods_s20.csv',index_col=0,parse_dates=True)))
-
-w90 = pd.concat((pd.read_csv(dir+'Solar/Modelled/pasadena_2018_1h_367mods_w90.csv',index_col=0,parse_dates=True),
-                 pd.read_csv(dir+'Solar/Modelled/pasadena_2019_1h_367mods_w90.csv',index_col=0,parse_dates=True)))
-
-solar = pd.concat((s20,w90),axis=1)
-solar.columns=solar_angles
-
-solar = solar.loc[load.index]
-
[…]

### 2023-12-07 Versions/caltech_ev_mjw6.py

@@ -1,578 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech.csv',
-                   index_col=0,
-                   parse_dates=True,
-                   comment='#',
-                   )
-                    #.resample('1h').mean()\
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.fillna(method='ffill')
-#interval_min = int(load.index.to_series().diff().mean().seconds/60)
-load = load.resample('60min').mean()
-load = load.loc['2018-5-1':'2019-2-28']
-print(load.info())
-plot_weekly(load['Load (kW)'])
-load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w90']
-
-dir_solar = dir+'Solar/Modelled/'
-
-s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
-                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
-
-w90 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_w90.csv',index_col=0,parse_dates=True,comment='#'),
[…]

### 2023-12-07 Versions/caltech_ev_mjw7b.py

@@ -1,585 +1,0 @@
-# %%
-import pandas as pd
-from bifacial_peak_shaving import *
-from _utils import *
-pd.options.plotting.backend='plotly'
-
-# %% [markdown]
-# # Data
-
-# %%
-dir = './Data/'
-output_filename = 'Output/caltech_ev_mjw7b__output__15min-doubleSolar-peak16-21__'+pd.Timestamp.now().strftime('%y-%m-%d_%H-%M-%S')+'.csv'
-
-# %% [markdown]
-# ## Load
-
-# %%
-load = pd.read_csv(dir+'acn_caltech.csv',
-                   index_col=0,
-                   parse_dates=True,
-                   comment='#',
-                   )
-                    #.resample('1h').mean()\
-                    #.fillna(method='ffill')
-                    #.loc['2018-4-26':'2019-3-22']
-#load = pd.DataFrame({'Load (kW)':list(load.loc['2019-1-2 0:00':'2019-1-2 16:00','Load (kW)'])+list(load.loc[:,'Load (kW)'])},
-#                     index=pd.date_range('2019-1-1 0:00',periods=8760,freq='1h'))
-#load.loc['2019-5-20'] = load.loc['2019-5-22'].values
-#load.loc['2019-5-21'] = load.loc['2019-5-22'].values
-#load.index = pd.date_range('1901-1-1 0:00',periods=35040,freq='15min')
-load = load.fillna(method='ffill')
-#interval_min = int(load.index.to_series().diff().mean().seconds/60)
-#load = load.resample('1h').mean()
-load = load.loc['2018-5-1':'2019-2-28']
-print(load.info())
-#plot_weekly(load['Load (kW)'])
-#load.plot()
-
-# %% [markdown]
-# ## Solar
-# 
-# - 7 kWp, TMY
-# 
-# - Net zero capacity
-# 
-#   - $capacity[kWp] = production[kWh] \times yield [\frac{kWh}{kWp}]^{-1}$
-
-# %%
-solar_angles = ['s20','w90','s20w90']
-
-dir_solar = dir+'Solar/Modelled/'
-
-s20 = pd.concat((pd.read_csv(dir_solar+'pasadena_2018_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#'),
-                 pd.read_csv(dir_solar+'pasadena_2019_15min_367mods_s20.csv',index_col=0,parse_dates=True,comment='#')))
-
[…]

### 2023-12-07 Paper/tex/bifacial_peak_shaving_paper.tex
results text and plotting

@@
 
+-\/-
+
 \hypertarget{introduction}{%
@@
 
-The world right now requires a quick and efficient transition of most
-energy usage to electric and most energy production to renewable
-sources. With this changing energy paradigm will come a larger emphasis
-on peak load management. Electric load growth from equipment like EV
-charging and heat pumps will likely out pace distribution capacity
-growth in many areas.
+The renewable energy transition will oversee a global shift toward
+electric energy consumption and renewable electric energy production in
+the coming decades. Since most electric transmission and distribution
+networks were previously built slowly over the span of many decades,
+electric load growth will almost definitely outpace network upgrades.
+And where these upgrades are completed they are necessarily an
+additional cost paid by all electricity consumers, due to the decrease
+in the load factor. Furthermore in some markets where companies can own
+both generation and distribution, business-as-usual infrastructure
+upgrades may be prioritized over the new construction of more complex
+and financially risky renewable generators. So while there are some
+creative solutions around dynamic capacity limits, two important
+solution areas for overall deployment speed, cost effectiveness, and
+overall decarbonization goals are (a) more local energy production and
+(b) increasing the load factor.
 
-Public EV chargers may especially suffer from a low load factor due to
-the convenience of fast charging at high power. Heat pump load factor
-may be increased with architectural features such as insulation and
-thermal storage, but worsening extreme weather events and challenges to
-building efficiency retrofits will mean this can not be achieved
-everywhere. And relative to the marginal cost of additional kWh of
-energy, the marginal cost of additional kW of peak power is quite
-expensive because it necessarily requires new grid infrastructure like
-transformers and lines.
-
-Distribution and transmission companies are well aware of this problem,
-but infrastructure upgrades are often slowed down by regulation and
-permitting. In regulatory areas where companies can own both generation
-and distribution, business-as-usual grid upgrades may be prioritized
-over construction of new renewable generation, which can often be
-complex projects with more difficult permitting and less certain
-returns. Largely due to these factors consumer prices on monthly and
-annual peak load are generally increasing around the world.
+Electric vehicle (EV) charging and electric heating and cooling,
+including traditional air conditioning and heat pumps, are two common
+new loads that will strain networks in most countries. Heat pump and air
+conditioning load factor may be increased with architectural features
+such as insulation and thermal storage, but building retrofits are often
+slowed down due to permitting and other challenges. Meanwhile extreme
+weather events, especially heat waves, will likely further reduce the
+load factor of these devices. Many EV users will choose to slowly charge
+overnight at home for convenience and to minimize their energy cost.
+However workplace, fleet, and public EV charging stations will likely
+still be required, and these may especially suffer from a low load
+factor due to the convenience or need of fast charging at high power.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=3in,height=\textheight]{16932411489031.png}
-\caption{Figure C: General schematic of case studies. The site is connected
-to the electricity utility and pays for consumption according to the
-electric meter. Because solar is connected behind the meter it is
-directly useful for reducing the site load, and since it has a zero
-marginal cost it is always dispatched at maximum available power. The
-battery could be said to working on maintaining the net load below the
-peak shaving threshold, where net load is load less solar.}
-\end{figure}
-
 \begin{equation}
-  \begin{align}
-I_{load,t} - \Sigma_i I_{gen,i,t} - \Sigma_j I_{gen\uarr,j,t} - \Sigma_k I_{load\darr,k,t} < I_{threshold,t} \\
-where \\
-i=generation\ asset\ with\ no\ flexibility \\
-j=generation\ asset\ with\ upward\ flexibility \\
-k=controllable\ load\ asset\ with\ downward\ flexibility \\
-t=applicable\ timesteps\
-  \end{align}
+\begin{split}
+I_{threshold,t} &> I_{j,t} - \Sigma_i I_{gen,i,t} - \Sigma_j I_{gen\uarr,j,t} - \Sigma_k I_{load\darr,k,t}  \\
+\\
+&\text{where:} \\
+&i\text{ is generation asset with no flexibility} \\
+&j\text{ is generation asset with upward flexibility} \\
+&k\text{ is controllable load asset with downward flexibility} \\
+&t\text{ is relevant timesteps}
+\end{split}
 \end{equation}
@@
 
-\[(2)\ P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}  < P_{threshold,h} \\
-where \\
-P_{batt,discharge,h} \ge 0 \\
-P_{batt,charge,h} \le 0 \\
-h \in \{0,1,2,...23\} \\\]
+\begin{equation}
+\begin{split}
+P_{threshold,h} &> P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}   \\
+P_{batt,discharge,h} &\ge 0 \\
+P_{batt,charge,h} &\le 0 \\
+h &\in \{0,1,2,...23\} \\
+\end{split}
+\end{equation}
 
-\hypertarget{technical-case}{%
-\subsection{Technical case}\label{technical-case}}
+\hypertarget{technical}{%
+\subsubsection{Technical}\label{technical}}
 
@@
 \centering
-\includegraphics{/home/mjw/Insync/michael.wood@mugrid.com/Google Drive - Shared drives/Polimi/Publications/Bifacial solar and peakshaving/bifacial_peak_shaving_paper.assets/tech_shaving.png}
-\caption{technical peak shaving}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/tech_shaving.png}
+\caption{}
 \end{figure}
 
+\begin{quote}
 \emph{Figure A: The threshold is 20 kW. The battery begins the day full
@@
 increasing the site load up to the threshold.}
+\end{quote}
 
@@
 
-\hypertarget{economic-case}{%
-\subsection{Economic case}\label{economic-case}}
+\hypertarget{economic}{%
+\subsubsection{Economic}\label{economic}}
 
@@
 often pay a price on energy (€\(/kWh\)) and a price on power
-(€\(/kWh_{peak}\)), which is often referred to as a demand charge. The
-energy cost (€\(/kWh \times E_{consumed}\)) may vary with time of day,
-day of week, and season of the year, which is often referred to as time
-of use or peak pricing. Where there is a sufficient spread between the
-peak and off-peak prices there may be the opportunity to curtail load
-during high prices, use controllable loads to shift from a high price
-period to a lower one, or to use energy storage to buy energy at the
-lower price and reduce load during a higher price period. Instead, the
-power cost (€\(/kW \times P_{max}\) ) typically applies to the max power
-during the billing period, where the peak power is the average power
-measured over a short interval (often 15 or 60 minutes) and only applies
-to a peak period (such as )
+(€\(/kWh_{peak}\)), or demand charge. The energy cost
+(€\(/kWh \times E_{consumed}\)) may vary with time of day, day of week,
+and season of the year, which is often referred to as time of use or
+peak pricing. Where there is a sufficient spread between the peak and
+off-peak prices there may be the opportunity to curtail load during high
+prices, use controllable loads to shift from a high price period to a
+lower one, or to use energy storage to buy energy at the lower price and
+reduce load during a higher price period. A peak shaving approach
+applied to the energy cost could be effective and maybe even
+advantageous. However there are several key differences between an
+energy based approach and a power one, where peak shaving is better
+suited for the latter.
 
-The peak power is typically defined as the maximum load power during
-certain hours of the day for a certain billing period. The peak is
-calculated from a non-moving average, with a typical interval of 15
-minutes or one hour.
+Instead, the power cost (€\(/kW \times P_{max}\) ) typically applies to
+the max power during the billing period, where the peak power is the
+maximum non-moving average in a given period (e.g. 12:00-18:00 on
+weekdays) calculated on a given interval (e.g. 60 minutes). Similar to
+the energy cost, there may be multiple time of use periods and
+associated prices, such as peak, mid-peak, and off-peak. And where the
+spread price is sufficiently high, the period peak can be reduced with
+load curtailment or rescheduling, distributed generation such as solar,
+or energy storage.
 
@@
 \centering
-\includegraphics{/home/mjw/Insync/michael.wood@mugrid.com/Google Drive - Shared drives/Polimi/Publications/Bifacial solar and peakshaving/bifacial_peak_shaving_paper.assets/econ_shaving.png}
-\caption{}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/econ_shaving.png}
+\caption{technical peak shaving}
 \end{figure}
 
+\begin{quote}
 \emph{Figure B: The threshold is comprised of two parts: Threshold0 at
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=5.14583in,height=\textheight]{17019217180021.png}
+\caption{}
+\end{figure}
+
+\begin{quote}
+\emph{Figure E: Simplified one-line schematic of the simulated EV
+charging station with true measured EV charging power, modelled on-site
+solar PV generation, and a modelled stationary battery for economic peak
+shaving.}
+\end{quote}
+
+The methodology of this study is a set of offline simulations involving
+(a) EV charging power measurements, (b) modelled solar PV production
+power, and (b) AC-coupled battery dispatch, all behind the retail
+electric meter. In each simulation the battery power is chosen such that
+the net load (natural load less solar production) is held below a given
+threshold, which is optimally chosen by a gradient descent optimizer.
+The optimal threshold changes for each TOU period. A single simulation
+is defined for one solar configuration and battery capacity and lasts
+one calendar month, which is the shortest period for which the cost
+function is defined. Simulations are repeated for several months of
+data, and many different solar and battery design sizes, allowing for a
+retail energy cost comparison among different design scenarios. EV
+charging power or solar are never curtailed. The primary decision
+variables in each timestep are (a) battery charge or discharge, and (b)
+battery power.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+\hypertarget{ev-charging-load}{%
+\subsubsection{EV Charging Load}\label{ev-charging-load}}
+
+The measured EV charging power ("load") is from the Caltech Adaptive
+Charging Network database at the JPL site. Each charging session
+provides timeseries active power, averaged over a 10 second interval. In
+the cases when complete timeseries data is not available for a session,
+the charging profile is estimated and the total charging energy
+delivered is the same. The disaggrated session timeseries data is summed
+into a single timeseries of total site charging power, which is then
+averaged over 15-minute intervals. Timestamp indices refer to the
+beginning of the 15-minute interval. The data period is from 2018-5-1
+00:00 to 2019-2-28 23:45.
+
+\hypertarget{solar-production}{%
+\subsubsection{Solar Production}\label{solar-production}}
+
+The modelled PV production power begins life as GOES satellite solar
+irradiance data from the US National Solar Resource Database (NSRDB),
+and is specific to the exact time and date rather as opposed to typical
+meteorological year data. Prism Solar 350 W bifacial solar module DC
+electrical power is estimated using the California Energy Commission
+Performance Model, a 6-parameter physical PV cell model. The full AC
+array power is estimated given loss assumptions and an inverter
+efficiency lookup table in the NREL SAM database for the Enphase IQH 380
+W microinverter. All these functions are implemented in SAM v2022.11.21
+(Gilman 2015).
+
+Three different solar array orientations are modelled and simulated in
+different case studies. Each orientation has the same number and type of
+modules: all modules facing South at 20° tilt, all modules facing West
+at 90° tilt, and half the modules facing South at 20° tilt and half the
+modules facing West at 90° tilt. Tilt is defined as 90° minus the
+altitude angle of the normal vector of the primary active face of the
+module. No shading is considered. Of the two sides of the bi-facial
+module, the primary active face is oriented West since afternoon load is
+generally subject to higher prices.
+
+\begin{longtable}[]{@{}lllll@{}}
+\toprule
+Timeseries Description & Location & Type & Interval / Length &
+Source\tabularnewline
+\midrule
+\endhead
+\vtop{\hbox{\strut EV charging power}\hbox{\strut (\(kW_{ac}\))}} & Jet
+Propulsion Lab, Pasadena CA, USA & Measured and aggregated from multiple
+EV chargers at single site & 10 sec (average downsampled to 15 min) / 10
+months & Caltech ACN\tabularnewline
+\vtop{\hbox{\strut Solar irradiance }\hbox{\strut (\(W/m^2\))}} & GPS:
+34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance & 5
+minute / 10 months & NSRDB PSMv3\tabularnewline
+PV array production (\(kW_{ac}\)) & GPS: 34.2013, -118.1721 (2x2 km
+square) & Modelled from satellite irradiance, 368 Prism Solar 350 W
+bifacial modules, 368 Enphase IQH 380 W microinverters & 15 minute / 10
+months & SAM (Gilman 2015)\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{quote}
+\emph{Table C: Timeseries Data Summary. EV charging power is measured
+every 10 seconds for 10 months at the Jet Propulsion Laboratory, CA,
+USA. Solar irradiance from the GOES satellite is acquired for the same
+location. Solar PV array production is modelled from the satellite
+irradiance using a 6 parameter PV cell model and inverter efficiency
+lookup table.}
+\end{quote}
+
+\hypertarget{battery}{%
+\subsection{Battery}\label{battery}}
+
+A stationary, storage battery system is simulated as the primary
+decision variable in the peak shaving algorithm. In each timestep the
+battery is chosen to charge or discharge within its technical limits.
+Because the control action is to hold the power exchange with the grid
+to below a certain threshold, batteries with a larger power capacity or
+energy capacity will necessarily achieve a lower threshold if the entire
+battery capacity is used. For a given energy capacity (\(kWh\)) those
+limits are a charge or discharge rate no more than 1C and SOC between 0
+and 100\% of rate. Charge and discharge efficiency is assumed constant
+and no self discharge or thermal limiting are considered.
+
+There are many strategies for optimal battery sizing, but the emphasis
+in this work is instead on understanding the dynamics between load,
+shape of the solar curve, and peak shaving algorithm for a given battery
+size. Therefore a sensitivity analysis is performed on the battery
+energy capacity, but no one battery size is declared economically
+optimal.
+
+\begin{longtable}[]{@{}l@{}}
+\toprule
+Battery Sizes (kWh)\tabularnewline
+\midrule
+\endhead
+25, 50, 75, 100, 125, 150, 200, 400, 600\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{quote}
+\emph{Table A: Vector of battery sizes chosen for peak shaving
+simulations. These were identified as interesting values
+experimentally.}
+\end{quote}
+
+Each simulation assumed charge and discharge rate are limited to 1C,
+usable SOC is assumed 100\%, and self discharge, parasitic losses, and
+thermal limiting are not considered.
+
+\hypertarget{electric-tariff}{%
+\subsection{Electric Tariff}\label{electric-tariff}}
+
+A typical California electric tariff is applied at the point of the
+retail electric meter, with several different TOU periods and prices.
+For the chosen tariff each TOU period may have an energy price
+(\(\$/kWh\)), a power price (\(\$/kW\)), or both. The prices may also
+change between seasons, and have long term trends like any retail
+electric prices. Here a price on power ("demand charge") is understood
+as a \(\$/kW\) price applied to the monthly maximum power observed at
+the meter, calculated as the 15-minute average of real power.
+
+\begin{longtable}[]{@{}lllll@{}}
+\toprule
+Name & TOU Period & Summer (Jun 1 - Sept 30) {[}\${]} & Winter (Oct 1 -
+Feb 28) {[}\${]} & Spring (Mar 1 - May 30) {[}\${]}\tabularnewline
+\midrule
+\endhead
+All hours & 0:00-0:00 & 26.07 / kW & 26.07 / kW & 26.07 /
+kW\tabularnewline
+Super off-peak & 9:00-14:00 & -\/- & -\/- & 0.079 / kWh\tabularnewline
+Off-peak spring & \vtop{\hbox{\strut 0:00-9:00,
+14:00-16:00,}\hbox{\strut 21:00-0:00}} & -\/- & -\/- & 0.132 /
+kWh\tabularnewline
+Off-peak winter & 0:00-16:00, 21:00-0:00 & -\/- & 0.132 / kWh &
+-\/-\tabularnewline
+Off-peak summer & 0:00-14:00, 23:00-0:00 & 0.132 / kWh & -\/- &
+-\/-\tabularnewline
+Partial-peak & 14:00-16:00, 21:00-23:00 & \vtop{\hbox{\strut 6.81 /
+kW,}\hbox{\strut 0.159 / kWh}} & -\/- & -\/-\tabularnewline
+Peak & 16:00-21:00 & \vtop{\hbox{\strut 32.90 / kW,}\hbox{\strut 0.196 /
+kWh}} & \vtop{\hbox{\strut 2.22 / kW,}\hbox{\strut 0.172 / kWh}} &
+\vtop{\hbox{\strut 2.22 / kW}\hbox{\strut ,0.172 / kWh}}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{quote}
+\emph{Table B: Retail Electric Tariff. An applicable electric tariff
+schedule with seven different TOU periods for energy and power prices,
+varying by hours of the day and season of the year. From California
+PG\&E.}
+\end{quote}
+
+The total retail electric cost \(C\) for each month is then the sum of
+the energy cost and power cost for the month, where the energy and power
+costs are calculated separately for each TOU period. The energy cost is
+the energy delivered to the site multiplied by the energy price for that
+TOU period. The power cost is the maximum 15-minute average power for
+the month multiplied by the power price for that TOU period.
+
+\begin{equation}
+\begin{split}
+NL(t) &= L(t) - S(t) \\
+NL_{p}(t) &= NL(t),\ \forall \ NL(t)>0 \\
+B(t) &= B_d(t) - B_c(t) \\
+C_m &= \Sigma_k^K [ p_{p,k,m} max(NL_{p,k,m}-B) + p_{e,k,m} \Sigma (NL_{p,k,m}-B) ] \\
+\\
+& \text{where:} \\
+&L \text{ is EV charging load}\ (kW) \\
+&S \text{ is solar production}\ (kW)\\
+&NL \text{ is net load}\ (kW) \\
+&B_c \text{ is battery charging power (non-negative)}\ (kW) \\
+&B_d \text{ is battery discharging power (non-negative)}\ (kW) \\
+&C_m \text{ is total retail electric cost for month}\ m\ (\$) \\
+&p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  (\$/kW) \\
+&p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ (\$/kWh) \\
+&K \text{ is number of TOU periods}
+\end{split}
+\end{equation}
+
+\hypertarget{peak-shaving-algorithm}{%
+\subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}}
+
+An optimal peak shaving strategy is used to minimized the total retail
+electric cost to the EV charging station. The strategy is operational
+only, and assumes the solar production timeseries and battery capacity
+are fixed. The state variable controlled by the algorithm is battery
+charge or discharge power. However the algorithm reframes the problem as
+one of choosing a power threshold \(T\ (kW)\) applied to the point of
+injection to the grid, the electric meter. The battery is then
+dispatched, within its technical limits, to hold the net load (natural
+load less solar production) below the threshold. When the algorithm is
+successful the different thresholds for each TOU period are met for an
+entire month. If the battery reaches a technical limit and net load
+exceeds a threshold, the simulation is not necessarily invalid but is
+not likely to minimize the retail electric cost to the site for that
+combination of solar and battery size. The peak shaving logic is
+described in Figure D.
+
+\begin{figure}
+\centering
+\includegraphics[width=6.59375in,height=\textheight]{17019217180102.png}
+\caption{}
+\end{figure}
+
+\begin{quote}
+\emph{Figure D: Peak shaving dispatch. Net load is the timeseries of
+load less solar. There is one threshold value for one for each TOU
+period with a non-zero power price. For each timestep of the simulation
+the net load is compared to the threshold of that TOU period, and the
+battery is discharged if the net load is greater than the threshold and
+charged if the net load is less than the threshold. If the two are equal
+the battery does nothing. For timesteps with no price on power the the
+battery does nothing.}
+\end{quote}
+
+The peak shaving algorithm describes stepping through time and
+dispatching the battery according to power thresholds, but not how the
+thresholds are chosen.
+
+\hypertarget{threshold-optimizer}{%
+\subsection{Threshold Optimizer}\label{threshold-optimizer}}
+
+The optimal demand thresholds (one per TOU period) are determined by a
+custom gradient descent optimizer. The objective function \(C\)
+minimizes the retail energy cost of one month, which is the billing
+interval of this retail electric tariff. In practice the optimal
+thresholds are different for each month. The threshold for each TOU
+period \(T_k\) is not enforced to be non-negative, but in practice is
+always is because the cost function \(C_m()\) cannot evaluate to a
+negative value.
+
+\begin{equation}
+\begin{split}
+min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)] \\
+& s.t. \\
+B_c(t) & \le B_{c,max} \\
+B_d(t) & \le B_{d,max} \\
+SOC_{min} & \le SOC(t) \le SOC_{max} \\
+\\
+& \text{where:} \\
+B_c & \text{ is battery charge power timeseries}\ (kW) \\
+B_d & \text{ is battery discharge power timeseries}\ (kW) \\
+T_k & \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
+SOC & \text{ is battery state of charge timeseries}\ (\frac{kWh}{kWh}) \\
+\end{split}
+\end{equation}
+
+Beginning from an initial guess the Newton-Raphson gradient descent
+optimizer calculates the batch gradient and updates parameters based on
+a learning rate of 0.01. This continues until the stopping condition is
+met, minimum cost for a patience of 50 iterations. The Newton-Raphson
+gradient descent based optimization method is preferred over linear
+programming because it will minimize over a variety of cost functions
+without needing to reformulate the linear program.
+
+\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}}
+
+Simulations are run one month at a time for a given solar array
+orientation and battery capacity, according to the flowchart in Figure
+C. The computational environment is Python 3.8 in Windows 10 64-bit, on
+an Intel i9 CPU with 64 GB of RAM.
+
+\begin{figure}
+\centering
+\includegraphics[width=4.91667in,height=\textheight]{17019217180163.png}
+\caption{}
+\end{figure}
+
+\begin{quote}
+Figure C: Simulation Flowchart. Given a solar orientation and chosen
+battery capacity, the net load timeseries is calculated from EV charging
+load and solar production. The threshold optimizer produces one
+threshold value (kW) for each TOU period with non-zero power prices.
+This returns both optimal thresholds and a minimum cost. Lastly a 1
+month simulation of the battery charging and discharging is performed to
+ensure no violations of the battery technical limits, and to produce the
+battery power timeseries for evaluation.
+\end{quote}
+
+\hypertarget{case-studies}{%
+\section{Case Studies}\label{case-studies}}
+
+Three case studies are evaluated, each relating to the orientation of
+the solar array but not changing the overall \(kWp\) capacity. All case
+studies use the Prism 350 W bifacial solar PV modules and the Enphase
+IQH 380 W microinverters.
+
+The first and baseline case is a South-facing array of 368 modules,
+tilted at 20˚. This is intended to be a typical rooftop solar plant,
+especially in northern latitudes where lower sun angles and winter snow
+make the research question of vertical bifacial modules even more
+relevant. The daily clearsky solar power curve is the familiar rounded
+triangle centered at solar noon. The array is sized such that the total
+energy produced is equal to the total energy consumption of the EV
+charging station. This "net zero" sizing is not necessarily economically
+optimal, but rather it is a reasonable or typical size solar plant for
+the load.
+
+The second case instead orients the active high-power face of the
+bifacial module West and tilts the module vertically at 90˚. This is an
+extreme case, especially at this large number of modules, but should be
+investigated since it represents the maximum amount that the daily
+clearsky power curve can be pushed toward the morning and evening from
+solar noon, making a two-peaked M-shape curve.
+
+The third case only orients half the modules West and 90°, which is a
+linear combination of the first two cases and physically represents a
+more realistic physical design. The motivation for including this case
+in the investigation is that while the time of solar production is
+important for peak shaving, too much production in a small later
+afternoon window may not be well timed with the late afternoon peak and
+more energy overall would have been sufficient.
+
+\begin{longtable}[]{@{}lllll@{}}
+\toprule
+Case & Orientation & Tilt & \vtop{\hbox{\strut Total Energy
+}\hbox{\strut {[}\(MWh\){]}}} & \vtop{\hbox{\strut Solar
+Yield}\hbox{\strut  {[}\(\frac{kWh}{kW_p}\){]}}}\tabularnewline
+\midrule
+\endhead
+1 (baseline) & South (368 modules) & 20° & 151.7 & 1180.8\tabularnewline
+2 & West (368 modules) & 90° & 131.0 & 1019.3\tabularnewline
+3 & \vtop{\hbox{\strut South (184 modules)}\hbox{\strut West (184
+modules)}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}} & 141.1 &
+1098.2\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{quote}
+\emph{Table D: Case Studies. All modules are the Prism 350 W bifacial.
+The baseline Case 1 is a South-facing array tilted to 20°. In Case 2 the
+primary high power surface faces West and the modules are tilted to 90°.
+In Case 3 half the array modules face West and are tilted at 90˚, and
+half the modules face South and are tilted at 20˚.}
+\end{quote}
+
 \hypertarget{results}{%
 \section{Results}\label{results}}
+
+The peak shaving methodology produces an optimally low retail electric
+cost for each of the 10 months of data, which are summed up for total
+electric cost in Figure A versus the battery capacity sensitivity
+analysis. The costs monotonically decrease with battery capacity as
+expected because every marginal unit of added battery energy capacity
+allows the algorithm to hold a power threshold for longer, and since
+each battery is rated for 1C at charging and discharging, the battery
+will also have more power capacity to achieve lower thresholds relative
+to the same size peak. The West 90° array never achieves a lower total
+cost than the baseline South 20°. The combination South 20° / West 90°
+array does for all battery sizes below 400 kWh, with a maximum reduction
+of \$1120 (3.05\%) relative to the South 20° at a very small battery
+size of 50 kWh. The largest percentage improvement of 3.54\% (\$890)
+occurs for the 125 kWh battery. The absolute cost reduction is likely
+more important than the relative reduction since it would be treated
+directly as revenue in a cash flow analysis to determine the economic
+performance of a given battery.
+
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/total retail electric cost.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/reduction in total retail electric cost.png}
+
+\begin{quote}
+\textbf{Figure A: Total Retail Electric Cost and Percentage Reduction.}
+Left: The West 90° array does not reduce the total cost compared to the
+baseline South 20°array, but the combination South 20°/ West 90° array
+with 50 kWh battery does reduce the cost \$1120 (3.05\%) over the 10
+month data period. Right: The largest percentage decrease in total cost
+is 3.54\% (\$890) for the 125 kWh battery.
+\end{quote}
+
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 1.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 2.png}
+
+\begin{quote}
+\textbf{Figure F: Single Day of Peak Shaving.} Left: The South 20° solar
+array overproduces during the middle hours of the day but falls to 28 kW
+while the evening peak
+\end{quote}
+
+\begin{longtable}[]{@{}llllllll@{}}
+\toprule
+Battery Capacity (kWh) & \vtop{\hbox{\strut South 20°
+}\hbox{\strut (Baseline)}} & West 90° & \vtop{\hbox{\strut 50\% South
+20°}\hbox{\strut 50\% West 90°}} & \vtop{\hbox{\strut West
+90°}\hbox{\strut Reduction}} & \vtop{\hbox{\strut 50\% South
+20°}\hbox{\strut 50\% West 90° }\hbox{\strut Reduction}} &
+\vtop{\hbox{\strut West 90°}\hbox{\strut Reduction}\hbox{\strut \%}} &
+\vtop{\hbox{\strut 50\% South 20°}\hbox{\strut 50\% West 90°
+}\hbox{\strut Reduction \%}}\tabularnewline
+\midrule
+\endhead
+25 & 29588.0 & 29221.0 & 29133.0 & 367.0 & 455.0 & 1.24 &
+1.53\tabularnewline
+50 & 23747.0 & 22972.0 & 22876.0 & 775.0 & 871.0 & 3.26 &
+3.66\tabularnewline
+75 & 19797.0 & 18721.0 & 19058.0 & 1076.0 & 739.0 & 5.43 &
+3.73\tabularnewline
+100 & 16230.0 & 15495.0 & 15279.0 & 735.0 & 951.0 & 4.52 &
+5.85\tabularnewline
+125 & 13388.0 & 12682.0 & 12454.0 & 706.0 & 934.0 & 5.27 &
+6.97\tabularnewline
+150 & 11155.0 & 11112.0 & 10519.0 & 43.0 & 636.0 & 0.38 &
+5.70\tabularnewline
+200 & 8445.0 & 8715.0 & 8017.0 & -270.0 & 428.0 & -3.19 &
+5.06\tabularnewline
+400 & 4850.0 & 5372.0 & 5024.0 & -522.0 & -174.0 & -10.76 &
+-3.58\tabularnewline
+600 & 3694.0 & 4180.0 & 3807.0 & -486.0 & -113.0 & -13.15 &
+-3.05\tabularnewline
+\bottomrule
+\end{longtable}
+
+Table C: Battery size sensitivity analysis for each of the two solar
+configuration cases, standard rate tariff
+
+\begin{longtable}[]{@{}lll@{}}
+\toprule
+Solar Capacity (\% of net zero) & Best s20-\textgreater w90 Reduction
+{[}\$,\%{]} (Batt {[}kWh{]}) & Best s20-\textgreater s20w90 Reudction
+{[}\$,\%{]} (Batt {[}kWh{]})\tabularnewline
+\midrule
+\endhead
+50\% & 183, 0.6\% (25) & 360, 1.1\% (25)\tabularnewline
+100\% & 1076, 5.4\% (75) & 951, 5.9\% (100)\tabularnewline
+125\% & 1158, 7.0\% (75) & 1091, 5.6\% (75)\tabularnewline
+150\% & 1527, 7.9\% (75) & 1281, 8.4\% (100)\tabularnewline
+175\% & 1621, 13.5\% (125) & 1668, 13.9\% (125)\tabularnewline
+200\% & 1618, 13.9\% (125) & 1656, 14.2\% (125)\tabularnewline
+\bottomrule
+\end{longtable}
+
+Table D: Solar capacity sensitivity analysis fo
 

### 2023-12-07 data_processing.py

@@ -971,7 +971,7 @@ def plot_weekly(ds,
 
 
 
-def plotly_stacked(_df:pd.DataFrame,
+def     plotly_stacked(_df:pd.DataFrame,
                    solar='solar',
                    solar_name='Solar',
                    load='load',
@@ -982,7 +982,7 @@ def plotly_stacked(_df:pd.DataFrame,
                    charge='charge',
                    load_charge_name='Load + Charge',
                    utility='utility',
-                   utility_name='Site Load',        
+                   utility_name='Import',        
                    soc='soc',
                    soc_name='SOC (right axis)',
                    soe='soe',
@@ -1000,8 +1000,13 @@ def plotly_stacked(_df:pd.DataFrame,
                    units_power='kW',
                    units_energy='kWh',
                    round_digits=1,
-                   upsample_min=None):
-    """ Make plotly graph with some data stacked in area-fill style
+                   upsample_min=None,
+                   template='plotly_white'):
+    """ Make plotly graph with some data stacked in area-fill style.
+    
+    Template options are :['ggplot2', 'seaborn', 'simple_white', 'plotly',
+         'plotly_white', 'plotly_dark', 'presentation', 'xgridoff',
+         'ygridoff', 'gridon', 'none']
     """
     
     df = _df.copy(deep=True) # we'll be modifying this
@@ -1159,17 +1164,17 @@ def plotly_stacked(_df:pd.DataFrame,
                       plot_bgcolor='rgba(0,0,0,0)',
                       legend=dict(orientation='h'),
                       legend_traceorder='reversed',
+                      template=template,
                       title=title,)
     if size is not None:
         fig.update_layout(width=size[0],height=size[1])
+
+        fig.update_yaxes(title_text=units_power, secondary_y=False)
     
     if soc in df.columns:
         fig.update_yaxes(title_text='%',range=(0, 100),secondary_y=True)
     elif soe in df.columns:
         fig.update_yaxes(title_text=units_energy,range=(0, df[soe].max()),secondary_y=True)
-
-    else:
-        fig.update_yaxes(title_text=units_power, secondary_y=False)
 
     if ylim is None:
         ymax = max(df[loadPlusCharge].max(),df[utility].max(),df[solar].max())

### 2023-12-07 Paper/tex/bifacial_peak_shaving_paper.tex
move images location

@@
 \centering
-\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/tech_shaving.png}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/tech_shaving.png}
 \caption{}
@@
 \centering
-\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/econ_shaving.png}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/econ_shaving.png}
 \caption{technical peak shaving}
@@
 \centering
-\includegraphics[width=5.14583in,height=\textheight]{17019217180021.png}
+\includegraphics[width=5.14583in,height=\textheight]{17019611651481.png}
 \caption{}
@@
 \centering
-\includegraphics[width=6.59375in,height=\textheight]{17019217180102.png}
+\includegraphics[width=6.59375in,height=\textheight]{17019611651552.png}
 \caption{}
@@
 \centering
-\includegraphics[width=4.91667in,height=\textheight]{17019217180163.png}
+\includegraphics[width=4.91667in,height=\textheight]{17019611651613.png}
 \caption{}
@@
 
-\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/total retail electric cost.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/reduction in total retail electric cost.png}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/total retail electric cost.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/reduction in total retail electric cost.png}
 
@@
 
-\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 1.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 2.png}
+\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/single day of peak shaving 1.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/single day of peak shaving 2.png}
 

### 2023-12-18 Paper/paper.tex
working paper .tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{geometry}

\author{}
\date{}

\begin{document}

\hypertarget{abstract}{%
  \section{Abstract}\label{abstract}}

Electric load peak shaving is a challenging and important problem
considering the rapid growth of high power electric vehicle charging
sites. Co-located solar photovoltaic provides locally produced energy,
but an additional storage battery is required for reliable peak shaving.
With occasional evening load peaks and an electric tariff with a
16:00-21:00 peak time of use period, vertical bifacial modules facing
West have an economic advantage due to more of the production shifted
into the late afternoon and early evening. Exploiting this, an optimal
electric load peak shaving simulator dispatches a stationary battery to
minimize the retail electric cost incurred by a real electric vehicle
charging site over 10 months. Five different case studies of co-located
bifacial solar photovoltaic arrays are simulated, a base case oriented
South and tilted at 20° and four experimental cases where a percentage
(25\%, 50\%, 75\%, or 100\%) of the array is oriented West and tilted at
90°. The problem is formulated such that the optimizer minimizes the
retail electric cost by adjusting three peak power thresholds, each
corresponding to a time of use period with an associated power price in
\(\$/kW\). The optimizer is implemented using a Newton-Raphson gradient
descent approach and the optimality of the method is verified to within
0.1 \(kW\). A sensitivity analysis on battery energy capacity results in
a largest cost reduction, relative to the South 20° base case, of \$1422
(6.7\%) achieved by the 50\% West 90° case and a modest 25 kWh battery.
A second sensitivity analysis on solar power capacity shows that the
cost reduction increases monotonically and logarithmically for all cases
and battery capacities. The largest cost decrease is \$2579 (16.1\%),
achieved by the 75\% West 90° case at 200\% of nominal solar capacity
along with a 125 kWh battery. Both data and code are shared to the
public on GitHub.

\hypertarget{introduction}{%
  \section{Introduction}\label{introduction}}

\hypertarget{why-peak-load}{%
  \subsection{Why peak load}\label{why-peak-load}}

The renewable energy transition will oversee a global shift toward
electric energy consumption and renewable electric energy production in
the coming decades. Since most electric transmission and distribution
networks were previously built slowly over the span of many decades,
electric load growth will almost definitely outpace network upgrades.
And where these upgrades are completed they are necessarily an
additional cost paid by all electricity consumers, due to the decrease
in the load factor. Furthermore in some markets where companies can own
both generation and distribution, business-as-usual infrastructure
upgrades may be prioritized over the new construction of more complex
and financially risky renewable generators. So while there are some
creative solutions around dynamic capacity limits, two important
solution areas for overall deployment speed, cost effectiveness, and
overall decarbonization goals are (a) more local energy production and
(b) increasing the load factor.

Electric vehicle (EV) charging and electric heating and cooling,
including traditional air conditioning and heat pumps, are two common
new loads that will strain networks in most countries. Heat pump and air
conditioning load factor may be increased with architectural features
such as insulation and thermal storage, but building retrofits are often
slowed down due to permitting and other challenges. Meanwhile extreme
weather events, especially heat waves, will likely further reduce the
load factor of these devices. Many EV users will choose to slowly charge
overnight at home for convenience and to minimize their energy cost.
However workplace, fleet, and public EV charging stations will likely
still be required, and these may especially suffer from a low load
factor due to the convenience or need of fast charging at high power.

\hypertarget{peak-shaving}{%
  \subsection{Peak shaving}\label{peak-shaving}}

Peak load management, or peak shaving, essentially requires choosing a
power threshold and holding the load power below it. Controllable loads,
energy storage, or generation assets behind the billing meter can all be
used to reduce the load power to the threshold power. The threshold may
only apply for only certain time periods. There may be multiple
thresholds and periods each day, month, or year. There are two general
cases of peak shaving worth considering. The most generation formulation
of peak shaving control is formulated in Equation \ref{eg:peakshaving-general}.

\begin{equation}
  \label{eg:peakshaving-general}
  \begin{split}
    I_{threshold,t} &> I_{j,t} - \Sigma_i I_{gen,i,t} - \Sigma_j I_{gen,up,j,t} - \Sigma_k I_{load,dn,k,t}  \\
    \\
    &\text{where:} \\
    &i\text{ is generation asset with no flexibility} \\
    &j\text{ is generation asset with upward flexibility} \\
    &k\text{ is controllable load asset with downward flexibility} \\
    &t\text{ is relevant timesteps}
  \end{split}
\end{equation}

Here we consider the case of no controllable load, a single battery,
solar which reduces the site load, and all values in units of average
real power over the interval \(\Delta h = 1\ hour\). This is descrbied in Equation \ref{eq:peakshaving}.

\begin{equation}
  \label{eq:peakshaving}
  \begin{split}
    P_{threshold,h} &> P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}   \\
    &\text{where:} \\
    P_{batt,discharge,h} &\ge 0 \\
    P_{batt,charge,h} &\le 0 \\
    h &\in \{0,1,2,...23\} \\
  \end{split}
\end{equation}

\hypertarget{technical}{%
  \subsubsection{Technical}\label{technical}}

Technical peak shaving refers to the case where a load must operate
under a technical limitation such as a maximum power agreement or
distribution transformer size. The load power must remain under the
threshold at all times, otherwise there may be a technical failure such
an activated overcurrent protection. Even if the load is technically
able to rise above the threshold, doing so may violate a contract
regarding maximum load power. The important consideration is that the
economic cost of failure to hold the load under the threshold is
prohibitively high. The time resolution of technical peak shaving
control and modeling may need to be as low as seconds or milliseconds.
Although this may be a challenging problem if the current limit is
dynamically set or if a larger network is considered, from the
perspective of dispatching the assets to shave the peak the problem is a
relatively simple one: economic dispatch such that the the load current
remains below the threshold current. Technical peak shaving might be
performed on current or apparent power rather than active power.

\hypertarget{economic}{%
  \subsubsection{Economic}\label{economic}}

Rather, economic peak shaving aims to reduce what a consumer pays for
power and possibly also energy. Medium and large electric consumers
often pay a price on energy (€\(/kWh\)) and a price on power
(€\(/kWh_{peak}\)), also called a demand charge. The energy cost
(€\(/kWh \times E_{consumed}\)) may vary with time of day, day of week,
and season of the year, which is often referred to as time of use or
peak pricing. Where there is a sufficient spread between the peak and
off-peak prices there may be the opportunity to curtail load during high
prices, use controllable loads to shift from a high price period to a
lower one, or to use energy storage to buy energy at the lower price and
reduce load during a higher price period. A peak shaving approach
applied to the energy cost could be effective and maybe even
advantageous. However there are several key differences between an
energy based approach and a power one, where peak shaving is better
suited for the latter.

Instead, the power cost (€\(/kW \times P_{max}\) ) typically applies to
the max power during the billing period, where the peak power is the
maximum non-moving average in a given period (e.g. 12:00-18:00 on
weekdays) calculated on a given interval (e.g. 60 minutes). Similar to
the energy cost, there may be multiple time of use periods and
associated prices, such as peak, mid-peak, and off-peak. And where the
spread price is sufficiently high, the period peak can be reduced with
load curtailment or rescheduling, distributed generation such as solar,
or energy storage.

\begin{table}
    \centering
    \caption{Economic and Technical Peak Shaving Comparison}
    \label{tab:econ-tech-peak-shaving}
    \begin{tabularx}{\textwidth}{XXX}
    \toprule
    Feature & Technical Peak Shaving & Economic Peak Shaving  \\
    \midrule
    Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
    Averaging interval                     & 1 minute                                 & 15 minutes or 1 hour (typical) \\
    Valid times of day                     & All                                      & Limited (e.g. 16:00 to 21:00) \\
    Peak is reset every..                  & Never                                    & Month, year, day (typical) \\
    \bottomrule
    \end{tabularx}
\end{table}

\hypertarget{methodology}{%
  \section{Methodology}\label{methodology}}

\begin{figure}
  \centering
  \includegraphics[width=5cm,height=\textheight]{./images/oneline.png}
  \caption{Charging Site One Line Schematic. Simplified
  one-line schematic of the simulated EV charging station with true
  measured EV charging power, modelled on-site solar generation, and a
  modelled stationary battery for economic peak shaving.}
  \label{fig:oneline}
\end{figure}

The methodology of this study is a set of offline simulations involving
(a) EV charging power measurements, (b) modelled solar photovoltaic (PV)
production power, and (b) AC-coupled battery dispatch, all behind the
retail electric meter. These are represented in in Figure \ref{fig:oneline}.
In each simulation the battery power is chosen
such that the net load (natural load less solar production, Equation \ref{eq:net-load}) is held
below a given threshold, which is optimally chosen by a gradient descent
optimizer.

\begin{equation}
  \label{eq:net-load}
  \begin{split}
    NL &= L - S \\
    &\text{where:} \\
    &L(t) \text{ is EV charging load time series (non-negative)}\ [kW]\\
    &S(t) \text{ is solar production time series}\ [kW] \\
  \end{split}
\end{equation}

The optimal threshold changes for each time of use (TOU)
period. A single simulation is defined for one solar configuration and
battery capacity and lasts one calendar month, which is the shortest
period for which the cost function is defined. Simulations are repeated
for several months of data, and many different solar and battery design
sizes, allowing for a retail energy cost comparison among different
design scenarios. EV charging power or solar are never curtailed. The
primary decision variables in each time step are (a) battery charge or
discharge, and (b) battery power.

\hypertarget{data}{%
  \subsection{Data}\label{data}}

\hypertarget{ev-charging-load}{%
  \subsubsection{\texorpdfstring{EV Charging Load
    }{EV Charging Load }}\label{ev-charging-load}}

The measured EV charging power ("load") is from the Caltech Adaptive
Charging Network database at the Jet Propulsion Lab (JPL) site. Each
charging session provides time series active power, averaged over a 10
second interval. In the cases when complete time series data is not
available for a session, the charging profile is estimated and the total
charging energy delivered is the same. The disaggregated session time
series data is summed into a single time series of total site charging
power, which is then averaged over 15-minute intervals. Time stamp
indices refer to the beginning of the 15-minute interval. The data
period is from 2018-5-1 00:00 to 2019-2-28 23:45.

\hypertarget{solar-production}{%
  \subsubsection{Solar Production}\label{solar-production}}

The modelled PV production power begins life as Geostationary
Operational Environmental Satellite (GOES) satellite solar irradiance
data from the US National Solar Resource Database (NSRDB), and is
specific to the exact time and date rather as opposed to typical
meteorological year data. See Table \ref{tab:data-summary}. Prism Solar 350 W bifacial solar module DC
electrical power is estimated using the California Energy Commission
Performance Model, a 6-parameter physical PV cell model. The full AC
array power is estimated given loss assumptions and an inverter
efficiency lookup table in the US National Renewable Energy Laboratory
(NREL) System Advisor Model (SAM) database for the Enphase IQH 380 W
microinverter. All these functions are implemented in SAM v2022.11.21.

Five different solar array orientations are modelled and simulated in
different case studies. See Table \ref{tab:casestudies}. Each orientation has the same number and type of bifacial
modules. In the first orienation all modules facing South at 20° tilt. In the remaining four
orientation a percentage of the modules face all modules face West at 90° tilt: 25\%, 50\%, 75\%, and then 100\%.
Tilt is defined as 90° minus the altitude angle of the normal vector of the primary active face of 
the module. No shading is considered. Of the two sides of the bi-facial module, the primary active 
face is oriented West since afternoon load is generally subject to higher prices.

\begin{table}[!h]
  \centering
  \caption{Timeseries Data Summary. EV charging power is
  measured every 10 seconds for 10 months at the Jet Propulsion
  Laboratory, CA, USA. Solar irradiance from the GOES satellite is
  acquired for the same location. Solar PV array production is modelled
  from the satellite irradiance using a 6 parameter PV cell model and
  inverter efficiency lookup table.\label{tab:loadsectors}}
  \label{tab:data-summary}
  \begin{tabularx}{\textwidth}{XXXXX}
  \toprule
  Timeseries Description & Location & Type & Interval / Length & Source  \\
  \midrule
  \vtop{\hbox{\strut EV charging power}\hbox{\strut (\(kW_{ac}\))}} & Jet
  Propulsion Lab, Pasadena CA, USA                                  & Measured and aggregated from multiple
  EV chargers at single site                                        & 10 sec (average downsampled to 15 min) / 10
  months                                                            & Caltech ACN \\

  \vtop{\hbox{\strut Solar irradiance }\hbox{\strut (\(W/m^2\))}}   & GPS:
  34.2013, -118.1721 (2x2 km square)                                & GOES satellite irradiance                                 & 5
  minute / 10 months                                                & NSRDB PSMv3 \\

  PV array production (\(kW_{ac}\))                                 & GPS: 34.2013, -118.1721 (2x2 km
  square)                                                           & Modelled from satellite irradiance, 368 Prism Solar 350 W
  bifacial modules, 368 Enphase IQH 380 W microinverters            & 15 minute / 10
  months                                                            & SAM (Gilman 2015) \\

  \bottomrule
  \end{tabularx}
\end{table}

\hypertarget{battery}{%
  \subsection{Battery}\label{battery}}

A stationary, storage battery system is simulated as the primary
decision variable in the peak shaving algorithm. In each timestep the
battery is chosen to charge or discharge within its technical limits.
Because the control action is to hold the power exchange with the grid
to below a certain threshold, batteries with a larger power capacity or
energy capacity will necessarily achieve a lower threshold if the entire
battery capacity is used. For a given energy capacity (\(kWh\)) those
limits are a charge or discharge rate no more than 1C and state of
charge (SOC) between 0 and 100\% of rate. State of energy (SOE) is the
SOC multiplied by nominal energy capacity and is used in plots because
the units are more meaningful when comparing dispatch time series.
Half-round-trip charge and discharge efficiency is constant at 90\% and
no self discharge or thermal limiting are considered.

There are many strategies for optimal battery sizing, but the emphasis
in this work is instead on understanding the dynamics between load,
shape of the solar curve, and peak shaving algorithm for a given battery
size. Therefore a sensitivity analysis is performed on the battery
energy capacity, but no one battery size is declared economically
optimal.

Each simulation assumed charge and discharge rate are limited to 1C,
usable SOC is assumed 100\%, and self discharge, parasitic losses, and
thermal limiting are not considered.

\hypertarget{electric-tariff}{%
  \subsection{Electric Tariff}\label{electric-tariff}}

A typical California electric tariff is applied at the point of the
retail electric meter with several different TOU periods and prices. See Table \ref{tab:tariff}.
For the chosen tariff each TOU period may have an energy price
(\(\$/kWh\)), a power price (\(\$/kW\)), or both. The prices may also
change between seasons, and have long term trends like any retail
electric prices. Here a price on power ("demand charge") is understood
as a \(\$/kW\) price applied to the monthly maximum power observed at
the meter, calculated as the 15-minute average of real power.

\begin{table}[!h]
  \centering
  \caption{Retail Electric Tariff. An applicable electric
  tariff schedule with seven different TOU periods for energy and power
  prices, varying by hours of the day and season of the year. From
  California PG\&E.}
  \label{tab:tariff}
  \begin{tabularx}{\textwidth}{XXXXX}
  \toprule
  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) {[}\${]}                   & Winter (Oct 1 -Feb 28) {[}\${]}   & Spring (Mar 1 - May 30) {[}\${]}  \\
  \midrule
  All hours                              & 0:00-0:00                                                & 26.07 / kW                                          & 26.07 / kW      & 26.07 / kW \\
  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-            & 0.079 / kWh \\
  Off-peak spring                        & \vtop{\hbox{\strut 0:00-9:00,14:00-16:00,}\hbox{\strut 21:00-0:00}} & -\/-                                                     & -\/-              & 0.132 / kWh \\
  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132 / kWh     & -\/-\\
  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132 / kWh                                         & -\/-            & -\/-\\
  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & \vtop{\hbox{\strut 6.81 /
  kW,}\hbox{\strut 0.159 / kWh}}         & -\/-                                                     & -\/-\\
  Peak                                   & 16:00-21:00                                              & \vtop{\hbox{\strut 32.90 / kW,}\hbox{\strut 0.196 /
  kWh}}                                  & \vtop{\hbox{\strut 2.22 / kW,}\hbox{\strut 0.172 / kWh}} & \vtop{\hbox{\strut 2.22 / kW}\hbox{\strut ,0.172 / kWh}}\\

  Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
  \bottomrule
  \end{tabularx}
\end{table}

The total retail electric cost \(C\) for each month is then the sum of
the energy cost and power cost for the month, where the energy and power
costs are calculated separately for each TOU period. See Equation \ref{eq:cost}. The energy cost is
the energy delivered to the site multiplied by the energy price for that
TOU period. The power cost is the maximum 15-minute average power for
the month multiplied by the power price for that TOU period. Only
positive values of site load \(SL\) are used in the cost calculation
since the monthly peak power for each TOU period must always be positive
and necessarily cannot benefit from net metering (export to the grid).

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m &= \Sigma_k^K [ p_{p,k,m} max(NL^+_{k,m} + B_d - B_c + p_{e,k,m} \Sigma (NL^+_{k,m} + B_d(t) - B_c(t)) ] \\
    \\
    & \text{where:} \\
    & NL^+(t) = NL(t),\ \forall\ NL(t)>0\\
    &B_c(t) \text{ is battery charging power time series(non-negative)}\ [kW]\\
    &B_d(t) \text{ is battery discharging power time series(non-negative)}\ [kW] \\
    &C_m \text{ is total retail electric cost for month}\ m\ [\$] \\
    &p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  [\$/kW] \\
    &p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ [\$/kWh] \\
    &K \text{ is number of TOU periods}
  \end{split}
\end{equation}

\hypertarget{peak-shaving-algorithm}{%
  \subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}}

An optimal peak shaving strategy is used to minimized the total retail
electric cost to the EV charging station. The strategy is operational
only, and assumes the solar production timeseries and battery capacity
are fixed. The state variable controlled by the algorithm is battery
charge or discharge power. However the algorithm reframes the problem as
one of choosing a power threshold \(T\ (kW)\) applied to the point of
injection to the grid, the electric meter. The battery is then
dispatched, within its technical limits, to hold the net load (natural
load less solar production) below the threshold. When the algorithm is
successful the different thresholds for each TOU period are met for an
entire month. If the battery reaches a technical limit and net load
exceeds a threshold, the simulation is not necessarily invalid but is
not likely to minimize the retail electric cost to the site for that
combination of solar and battery size. The peak shaving logic is
described in Figure \ref{fig:peakshaving-flowchart}.

\begin{figure}
  \centering
  \includegraphics[width=10cm,height=\textheight]{./images/peak shaving flowchart.png}
  \caption{Peak Shaving Flowchart. Net load is the
  timeseries of load less solar. There is one threshold value for one for
  each TOU period with a non-zero power price. For each timestep of the
  simulation the net load is compared to the threshold of that TOU period,
  and the battery is discharged if the net load is greater than the
  threshold and charged if the net load is less than the threshold. If the
  two are equal the battery does nothing. For timesteps with no price on
  power the the battery does nothing.}
  \label{fig:peakshaving-flowchart}
\end{figure}

The peak shaving algorithm describes stepping through time and
dispatching the battery according to power thresholds, but not how the
thresholds are chosen.

\hypertarget{threshold-optimizer}{%
  \subsection{Threshold Optimizer}\label{threshold-optimizer}}

The optimal demand thresholds (one per TOU period) are determined by a
custom gradient descent optimizer. The objective function \(C\)
minimizes the retail energy cost of one month, which is the billing
interval of this retail electric tariff. See Equation \ref{eq:optimization}. In practice the optimal
thresholds are different for each month. The threshold for each TOU
period \(T_k\) is not enforced to be non-negative, but in practice is
always is because the cost function \(C_m()\) cannot evaluate to a
negative value.

\begin{equation}
  \label{eq:optimization}
  \begin{split}
    min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)] \\
    & s.t. \\
    B_c(t) & \le B_{c,max} \\
    B_d(t) & \le B_{d,max} \\
    SOC_{min} & \le SOC \le SOC_{max} \\
    \\
    & \text{where:} \\
    T_k & \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
    SOC(t) & \text{ is battery state of charge timeseries}\ [\frac{kWh}{kWh}] \\
  \end{split}
\end{equation}

Beginning from an initial guess the Newton-Raphson gradient descent
optimizer calculates the batch gradient and updates parameters based on
a learning rate of 0.01. This continues until the stopping condition is
met, minimum cost for a patience of 50 iterations. The Newton-Raphson
gradient descent based optimization method is preferred over linear
programming because it will minimize over a variety of cost functions
without needing to reformulate the linear program.

\hypertarget{simulations}{%
  \subsection{Simulations}\label{simulations}}

Simulations are run one month at a time for a given solar array
orientation and battery capacity, according to the flowchart in Figure \ref{fig:simulation-flowchart}.
The computational environment is Python 3.8 in Windows 10 64-bit, on
an Intel i9 CPU with 64 GB of RAM.

\begin{figure}
  \centering
  \includegraphics[width=15cm,height=\textheight]{./images/simulation flowchart.png}
  \caption{Simulation Flowchart. Given a solar orientation
  and chosen battery capacity, the net load timeseries is calculated from
  EV charging load and solar production. The threshold optimizer produces
  one threshold value (kW) for each TOU period with non-zero power prices.
  This returns both optimal thresholds and a minimum cost. Lastly a 1
  month simulation of the battery charging and discharging is performed to
  ensure no violations of the battery technical limits, and to produce the
  battery power timeseries for evaluation.}
  \label{fig:simulation-flowchart}
\end{figure}

\hypertarget{case-studies}{%
  \section{Case Studies}\label{case-studies}}

Five case studies are evaluated, each relating to the orientation of the
solar array but not changing the overall \(kW_{DC}\) capacity. See Table \ref{tab:casestudies}. All case
studies use the Prism 350 W bifacial solar PV modules and the Enphase
IQH 380 W microinverters.

The first and baseline case is a South-facing array of 368 modules,
tilted at 20˚. This is intended to be a typical rooftop solar plant,
especially in northern latitudes where lower sun angles and winter snow
make the research question of vertical bifacial modules even more
relevant. The daily clearsky solar power curve is the familiar rounded
triangle centered at solar noon. The array is sized such that the total
energy produced is equal to the total energy consumption of the EV
charging station. This "net zero" sizing is not necessarily economically
optimal, but rather it is a reasonable or typical size solar plant for
the load.

The remaining case studies each consider a portion of the array to be
instead rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%.
Especially the last case is relatively extreme from a design
perspective, but should be investigated since it represents the maximum
amount that the daily clear sky power curve can be pushed toward the
morning and evening hours. This M-shaped power curve rather than the
typical rounded-triangle power curve is the basis of any advantage
vertical bifacial modules have regarding peak shaving. Micro inverters
are used in the design so that the cases with part of the array facing
west can be thought of a linear combination of the M-shaped and
rounded-triangle power curves.

\begin{table}
  \centering
  \caption{Case Studies. All modules are the Prism 350 W
  bifacial. The base case is South-facing array tilted to 20°. In the
  following four cases a percentage of the modules are oriented such that
  the primary high power module surface faces West and the modules are
  tilted to 90°: 25\%, 50\%, 75\%, and 100\%. As an increasing portion of
  the array is oriented West and vertical the total energy and solar yield
  decrease linearly as expected.}
  \label{tab:casestudies}
  \begin{tabularx}{\textwidth}{XXXXXX}
  \toprule
  Case Study                                   & No. Modules                               & Orientation & Tilt & \vtop{\hbox{\strut Total Energy }\hbox{\strut {[}\(MWh\){]}}}         & \vtop{\hbox{\strut Solar Yield}\hbox{\strut  {[}\(\frac{kWh}{kW_{DC}}\){]}}}\\
  \midrule
  South 20°                                    & 368                                       & South       & 20°  & 151.7                    & 1180.8\\
  25\% West 90°                                & \vtop{\hbox{\strut 276}\hbox{\strut 92}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 146.5                                     & 1140.4\\
  50\% West 90°                                & \vtop{\hbox{\strut 184}\hbox{\strut 184}} & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 141.1                                     & 1098.2\\
  75\% West 90°                                & \vtop{\hbox{\strut 92}\hbox{\strut 276}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 136.1                                     & 1059.6\\
  100\% West 90°                               & 368                                       & West        & 90°  & 131.0                    & 1019.3\\
  \bottomrule
  \end{tabularx}
\end{table}

\hypertarget{results}{%
  \section{Results}\label{results}}

The peak shaving methodology produces an optimally low retail electric
cost for each of the 10 months of data, which are summed up for total
electric cost versus the battery capacity sensitivity analysis. See Figure \ref{fig:total-cost}.
The costs monotonically decrease with battery capacity as
expected because every marginal unit of added battery energy capacity
allows the algorithm to hold a power threshold for longer, and since
each battery is rated for 1C at charging and discharging, the battery
will also have more power capacity to achieve lower thresholds relative
to the same size peak. The 100\% West 90° array achieves a lower total
cost than the baseline South 20°. All three combination arrays achieve a
lower cost for all battery capacities up to 200 kWh, with a maximum
reduction of \$1422 (6.7\%) relative to the South 20° with a 100 kWh
battery. The largest percentage improvement of 7.10\% (\$1208) occurs
for the same array but 150 kWh battery. The absolute cost reduction is
likely more important than the relative reduction since it would be
treated directly as revenue in a cash flow analysis to determine the
economic performance of a given battery.

\begin{figure}[!h]
  \centering
  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost.png}
  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost reduction.png}
  \caption{Total Cost. Total Retail Electric Cost is calculated for each
  solar array case study and a sensitivity analysis is performed on
  battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90°
  arrays have similarly high total costs, whereas the three combination
  arrays are somewhat grouped a few percent below. Above 150 kW the total
  costs for each case diverge somewhat, with the South 20° base case
  attaining the lowest cost for the 400 kWh battery and larger.
  RIGHT: Reduction in Total Retail Cost is likely the most important metric for
  evaluating the peak shaving efficacy, since it can be directly used as
  revenue in a cash flow analysis to calculate economic performance. The
  combination 50\% West 90° array with 100 kWh battery achieve the largest
  cost reduction of \$1422 (6.7\%) over the 10 month data period. A
  selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
  \label{fig:total-cost}
\end{figure}

The benefit of vertical bifacial modules can be seen when comparing the
simulated battery charge and discharge time series data. Figure \ref{fig:peak-shaving} shows
the same day (June 6) for both the base Solar 20° case and the 100\%
West 90° case, which is presented here as a clearer graphical example
than the better performing 50\% West 90° array. For both cases June 6 is
the limiting day for the month, where the battery reaches a technical
limit, in these cases zero SOC. This is likely due to a particularly
large evening peak load event from approximately 17:30 to 21:30, with a
maximum power of 56 kW and total energy of 201 kW. For these simulations
the battery capacity is 125 kWh nominal and 112.5 kWh after losses, and
as specified the battery will charge and discharge at a maximum of 1C or
125 kW.

In Figure \ref{fig:peak-shaving} the base case of South 20° overproduces in the middle hours
of the day and solar is exported to the network starting around 12:00.
During the peak load event the South 20° only produces 18.8 kWh whereas
the 100\% West 90° array produces 104 kWh. In each case the battery
charges to 100\% (125 kWh) before the evening peak load event. The
result is that the evening net load peak in the 100\% West 90° case
starts later and contains less energy, though it reaches the same
maximum power. Due to this the battery in the 100\% West 90° case can
hold the site load to a lower threshold in \(kW\), which is directly
proportional to reducing the retail electric cost. During the expensive
"Peak" TOU period of 14:00-21:00 the base South 20° case only achieves a
low threshold of 13.0 kW, whereas the 100\% West 90° case holds a
threshold of 3.1 kW in the same period, a 76\% improvement.

The retail electric cost isn't defined for only one day out of a typical
month, since the power portion of the cost is calculated on the monthly
peak. However if June 6 was the only day of the month with non-zero load
the total cost would be \$983 for the South 20° case and \$560 for the
50\% West 90° case, which is a 43\% reduction.

\begin{figure}[!h]
  \centering
  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving south.png}
  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving west.png}
  \caption{Single Day of Peak Shaving. The stacked
  dispatch plots use a convention where EV charging load (magenta) and
  stationary battery charging additional load (blue) are the solid lines,
  whereas any source of energy including the discharging battery are solid
  areas. Since load must always be equal to the sum of supplied energy,
  the areas always stack up to meet the load lines. The only exception is
  when energy is exported back to the network, as is the case with
  afternoon solar production here. The TOU power thresholds are
  represented by the four dashed line segments, which begin and end based
  on the begin and end of the TOU period, and overlap in time where the
  TOU periods overlap. SOE is the dash-dot line referenced to the right
  vertical axis. The base South 20° solar array overproduces midday
  and exports energy to the grid, leaving more energy in the evening peak
  that the stationary battery needs to serve.
  RIGHT: The 100\% West 90°
  case exports less solar to the grid, and has more late afternoon
  production aligned with the evening load peak, allowing the peak shaving
  algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than
  the South 20° array.}
  \label{fig:peak-shaving}
\end{figure}

In Table \ref{tab:total-cost} are some of the data from Figure \ref{fig:total-cost}, though not shown for
conciseness are the 75\% West 90° and the 25\% West 90° cases. The
largest cost reduction is \$1422 for the 50\% West 90° case and 100 kWh
battery. Note that the largest reduction in retail cost may not be the
best solution economically, since the 25 kWh battery achieves 65\% of
the cost reduction at 20\% of the battery energy capacity, which is
roughly proportional to capital cost.

\begin{table}[!h]
  \centering
  \caption{Total Retail Electric Cost. Simulated total
  retail electric cost for three of the case studies (some omitted for
  conciseness) over the 10 months of available data and a given battery
  capacity. Cost reduction is calculated with respect to the South 20°
  base case. The best reduction in total retail cost is \$1422 for the
  50\% West 90° case.}
  \label{tab:total-cost}
  \begin{tabularx}{\textwidth}{XXXXXXXX}
  \toprule
  Battery {[}kWh{]} & Cost South 20° {[}\${]}                & Cost 50\% West 90°
  {[}\${]}          & Cost 100\% West 90° {[}\${]}           & Cost Reduction 50\% West 90°
  {[}\${]}          & Cost Reduction 100\% West 90° {[}\${]} & Cost Reduction 50\%
  West 90° {[}\%{]} & Cost Reduction 100\% West 90°
  {[}\%{]}\\
  \midrule
  25                & 31314.0                                & 30391.0                      & 31730.0 & 923.0           & -416.0  & 3.0  & -1.3\\
  50                & 27132.0                                & 25773.0                      & 27022.0 & 1359.0          & 110.0   & 5.0  & 0.4\\
  75                & 23893.0                                & 22775.0                      & 23625.0 & 1118.0          & 268.0   & 4.7  & 1.1\\
  100               & 21229.0                                & 19807.0                      & 20804.0 & \textbf{1422.0} & 425.0   & 6.7  & 2.0\\
  125               & 18954.0                                & 17623.0                      & 18564.0 & 1331.0          & 390.0   & 7.0  & 2.1\\
  150               & 17094.0                                & 15886.0                      & 17286.0 & 1208.0          & -192.0  & 7.1  & -1.1\\
  200               & 14547.0                                & 13689.0                      & 15282.0 & 858.0           & -735.0  & 5.9  & -5.0\\
  400               & 10730.0                                & 10969.0                      & 12131.0 & -239.0          & -1401.0 & -2.2 & -13.1\\
  600               & 8859.0                                 & 9140.0                       & 10333.0 & -281.0          & -1474.0 & -3.2 & -16.6\\
  \bottomrule
  \end{tabularx}
\end{table}

A sensitivity analysis on the size of the solar array is performed with
the results in Figure \ref{fig:solar-sensitivity} and Table \ref{tab:solar-sensitivity}. The total retail cost decreases monotonically
with the larger solar capacities, and the cost reduction increases by a
factor of 10 from the smallest to largest solar capacity. This result is
expected since the larger capacities create a more pronounced difference
between the late afternoon production of the two arrays which the peak
shaving strategy translates into lower power thresholds for the cases
with some portion of the array in the 100\% West 90° orientation.

The 50\% West 90° case performs best in the first four solar capacities
at which point, for the first time, the best performing case is one
where the majority of the modules are in the 100\% West 90° orientation
(75\%). However the difference of \$19 is not substantial. At larger
solar capacities the cost reductions for each case study are both larger
in magnitude and closer together, however the increase in cost reduction
is clearly less than linear with solar capacity. This suggests a
diminishing returns problem where, after a certain capacity of 100\%
West 90° modules is met, the additional South 20° and 100\% West 90°
modules are providing energy when the battery is already at 100\% SOC.

\begin{table}[!h]
  \centering
  \caption{Solar capacity sensitivity analysis based on reduction in total
  retail cost relative to the base South 20° case. While the 50\% West 90°
  array continues to achieve the highest cost reduction, the battery
  capacity increases from 25 kWh to 125 kWh.}
  \label{tab:solar-sensitivity}
  \begin{tabularx}{\textwidth}{XXXX}
    \toprule
    Solar Capacity {[}\(kW_{DC}\){]} & Best Case for Cost Reduction         & Best
    Cost Reduction {[}\${]}          & Best Cost Reduction Battery Capacity
    {[}kWh{]}\\
    \midrule
    64.4 (0.5x)                      & 50\% West 90°                        & 260  & 25\\
    128.8 (1.0x)                     & 50\% West 90°                        & 1422 & 100\\
    193.2 (1.5x)                     & 50\% West 90°                        & 2211 & 125\\
    257.6 (2.0x)                     & 75\% West 90°                        & 2579 & 125\\
    \bottomrule
  \end{tabularx}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=10cm,height=\textheight]{./images/total cost reduction solar sensitivity.png}
  \caption{Solar Capacity Sensitivity. A sensitivity
  analysis on solar capacity shows more available cost reduction, which
  increases less than linearly with solar capacity.}
  \label{fig:solar-sensitivity}
\end{figure}

The battery capacities increase from 25 kWh up to 125 kWh across the
solar sizes, which is an unexpected finding. Despite the extra capacity
the 100\% West 90° case in Figure \ref{fig:weekly-load-solar} is still mostly unable to affect the
peak power of the evening peaks, and thus both the base South 20° and
combination array cases have a similar maximum power to shave. Indeed
the average of the monthly peak net load values is 74.5 kW for the South
20° 2.0x case and 74.7 kW for the 100\% West 90° 2.0x case. However,
when increasing the solar to 2.0x, the energy under the net load time
series during the 17:00 to 22:00 period decreases by only 164 kWh for
the South 20° versus 886 kWh for the 100\% West 90° case. With more
solar production in the evening peak the optimizer is able to pursue
driving the "Peak" TOU period to zero, which has a large economic
benefit. This is unachievable with the small battery capacities and is
more difficult without the late afternoon solar production of the 100\%
West 90° modules. Indeed a large 200 kWh battery is required to achieve
the first 0 kW "Peak" period threshold in the South 20° case for all
solar capacities. Rather, the 100\% West 90° case achieves a 0 kW Peak
period threshold with the 150 kWh battery at 100\% solar capacity and
with the 125 kWh battery at 2.0x solar capacity.

\begin{figure}
  \centering
  \includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
  \caption{Weekly Overlaid Load and Solar Power. The
  entire 10 month time series of EV charging load, Solar 20°, and 100\%
  West 90° are superimposed on a weekly basis, beginning on Monday. The
  100\% West 90° case provides a clearer graphical example than the better
  performing cases.}
  \label{fig:weekly-load-solar}
\end{figure}

\hypertarget{conclusion}{%
  \section{Conclusion}\label{conclusion}}

An optimal electric load peak shaving strategy is simulated on 10 months
of EV charging power time series. The peak shaving asset is a storage
battery with a maximum charge and discharge rate of 1C and a constant
discharge and charge efficiency of 90\%. A co-located solar array is
included in the simulation to study the effects of typical South facing
modules vs West facing vertical bifacial modules. Five different array
orientations are presented as different case studies. In addition
sensitivity analyses on battery energy capacity and solar array capacity
provide information about the dynamics of the optimal peak shaving
algorithm. The best performing case is designed with 50\% of the array
South facing tilted at 20° and 50\% facing West at 90°, which achieved a
reduction in the total retail cost of energy of \$1422 (6.7\%) with a 25
kWh battery. The cost reduction is relative to the base case array with
all the modules facing South and tilted at 20°. When solar is increased
to twice the net-zero capacity the best performing case is 75\% West 90°
with a cost reduction of \$2579 (16.1\%) with a 125 kWh battery. The
best percentage cost reduction overall is 20.0\%. Both data and code are
shared to the public on GitHub.

Peak shaving a monthly peak power typically, depending on the load
factor, results in dispatching the battery until its technical limits to
achieve a minimum monthly peak power. Because the load, or net load
after solar is dispatched, is often not very homogeneous there will be
one limiting day where the battery is bound by its technical limits and
the peak power of the month is set. The presence of this limiting day in
the month simulation of Figure \ref{fig:peak-shaving} does not guarantee a global minimum
cost, but the lack of a limiting day would suggest the global minimum
was not found. Intuitively the limiting day can be thought of as the
most difficult day for the battery to achieve the given thresholds, and
if the day was somehow easier for the battery (less and more uniform net
load) the power thresholds could be lowered and therefore a lower retail
electric cost achieved. Because the results of each month typically
depend strongly on one limiting day, small changes in the load or solar
magnitude or temporal relationship can have a large impact on the
overall results. For this reason peak shaving simulations require
particular care into data selection, cleaning, and acquiring an
appropriate large amount of data such that the probability space of true
possible limiting is well represented in the selected sample of limiting
days.

Confidence in the results presented is medium-high given the use of true
EV charging measurements, a robust Newton-Raphson gradient descent
optimizer with verified optimality, a true electric tariff appropriate
for the load site and solar data location, and sensitivity analyses
performed on two variables. Future work should include a more load data
sets with more months of data, a more comprehensive battery model, an
operational version of the peak shaving strategy, and testing at the
Politecnico di Milano M2GLab microgrid.

\hypertarget{bibliography}{%
  \section{Bibliography}\label{bibliography}}

\end{document}

### 2023-12-19 Paper/tex/paper.tex
working mdpi format and bibtex

--- 2023-12-18 Paper/paper.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+
+%=================================================================
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
+
+%=================================================================
+% MDPI internal commands - do not modify
+\firstpage{1} 
 \makeatletter 
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\setcounter{page}{\@firstpage} 
 \makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2023}
+\copyrightyear{2023}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{ } 
+\daterevised{ } % Comment out if no revised date
+\dateaccepted{ } 
+\datepublished{ } 
+%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
+%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%\pdfoutput=1 % Uncommented for upload to arXiv.org
 
-\usepackage{tabularx}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage{geometry}
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
+% cleveref: load \crefname definitions after \begin{document}
 
-\author{}
-\date{}
+\usepackage[acronym]{glossaries}
+\usepackage{hhline}
+\usepackage{threeparttable} % to use table notes
+%\usepackage[draft]{changes} % usage: \deleted{old} \added{new} \replaced{new}{old} also \hl{} for highlighted text
+%\usepackage[final]{changes}
 
-\begin{document}
+%=================================================================
+% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\hypertarget{abstract}{%
-  \section{Abstract}\label{abstract}}
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}
 
-Electric load peak shaving is a challenging and important problem
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}
+
+\newcommand{\orcidauthorA}{0000-0003-0237-4148} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-2106-0374} % Add \orcidB{} behind the author's name
+
+\newcommand{\orcidauthorC}{0000-0002-7883-0034}
+
+% Authors, for the paper (add full first names)
+\Author{
+  Michael Wood $^{1,2,*}$\orcidA{},
+  Emanuele Ogliari $^{1}$\orcidB{},
+  Travis Simpkins $^{2}$, and
+  Sonia Leva $^{1}$\orcidC{}}
+
+%\longauthorlist{yes}
+
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Michael Wood, Emanuele Ogliari, Travis Simpkins, and Sonia Leva}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Wood, M.; Ogliari, E.; Simpkins, T.; Leva, S.}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Energy, Politecnico di Milano, Via Lambruschini 4a, 20156, Milan, Italy; emanuelegiovanni.ogliari@polimi.it (E.O.); sonia.leva@polimi.it (S.L.) \\
+$^{2}$ \quad muGrid Analyics LLC., 14143 Denver West Parkway Ste 100, Golden, CO, USA; travis@mugrid.com}
+
+% Contact information of the corresponding author
+\corres{Correspondence: michael.wood@polimi.it}
+
+\abstract{Electric load peak shaving is a challenging and important problem
 considering the rapid growth of high power electric vehicle charging
@@
 along with a 125 kWh battery. Both data and code are shared to the
-public on GitHub.
+public on GitHub.}
 
-\hypertarget{introduction}{%
-  \section{Introduction}\label{introduction}}
+% Keywords
+\keyword{electric load; peak shaving; bifacial solar PV; EV charging;}
 
-\hypertarget{why-peak-load}{%
-  \subsection{Why peak load}\label{why-peak-load}}
+\begin{document}
+
+\section{Introduction}\label{introduction}
+
+\subsection{Why peak load}\label{why-peak-load}
 
@@
 
-\hypertarget{peak-shaving}{%
-  \subsection{Peak shaving}\label{peak-shaving}}
+%\hypertarget{peak-shaving}{%
+\subsection{Peak shaving}\label{peak-shaving}%}
 
@@
 
-\hypertarget{technical}{%
-  \subsubsection{Technical}\label{technical}}
+%\hypertarget{technical}{%
+\subsubsection{Technical}\label{technical}%}
 
@@
 
-\hypertarget{economic}{%
-  \subsubsection{Economic}\label{economic}}
+%\hypertarget{economic}{%
+\subsubsection{Economic}\label{economic}%}
 
@@
 
-\hypertarget{methodology}{%
-  \section{Methodology}\label{methodology}}
+%\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}%}
 
@@
   \centering
-  \includegraphics[width=5cm,height=\textheight]{./images/oneline.png}
+  \includegraphics[width=7.5cm]{./images/oneline.png}
   \caption{Charging Site One Line Schematic. Simplified
@@
 
-\hypertarget{data}{%
-  \subsection{Data}\label{data}}
+%\hypertarget{data}{%
+\subsection{Data}\label{data}%}
 
-\hypertarget{ev-charging-load}{%
-  \subsubsection{\texorpdfstring{EV Charging Load
-    }{EV Charging Load }}\label{ev-charging-load}}
+%\hypertarget{ev-charging-load}{%
+%\subsubsection{\texorpdfstring{EV Charging Load
+%    }{EV Charging Load }}\label{ev-charging-load}%}
+\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}
 
@@
 
-\hypertarget{solar-production}{%
-  \subsubsection{Solar Production}\label{solar-production}}
+%\hypertarget{solar-production}{%
+\subsubsection{Solar Production}\label{solar-production}%}
 
@@
   \label{tab:data-summary}
-  \begin{tabularx}{\textwidth}{XXXXX}
+  \begin{tabularx}{\linewidth}{XXXXX}
+    % { >{\hsize=.25\hsize\linewidth=\hsize}X
+    %   >{\hsize=.25\hsize\linewidth=\hsize}X
+    %   >{\hsize=.7\hsize\linewidth=\hsize}X
+    %   >{\hsize=.1\hsize\linewidth=\hsize}X
+    %   >{\hsize=.2\hsize\linewidth=\hsize}X
+    % }
+  %\begin{tabularx}{llllll}
   \toprule
-  Timeseries Description & Location & Type & Interval / Length & Source  \\
+  Description & Location & Type & Interval & Source  \\
   \midrule
-  \vtop{\hbox{\strut EV charging power}\hbox{\strut (\(kW_{ac}\))}} & Jet
-  Propulsion Lab, Pasadena CA, USA                                  & Measured and aggregated from multiple
-  EV chargers at single site                                        & 10 sec (average downsampled to 15 min) / 10
-  months                                                            & Caltech ACN \\
-
-  \vtop{\hbox{\strut Solar irradiance }\hbox{\strut (\(W/m^2\))}}   & GPS:
-  34.2013, -118.1721 (2x2 km square)                                & GOES satellite irradiance                                 & 5
-  minute / 10 months                                                & NSRDB PSMv3 \\
-
-  PV array production (\(kW_{ac}\))                                 & GPS: 34.2013, -118.1721 (2x2 km
-  square)                                                           & Modelled from satellite irradiance, 368 Prism Solar 350 W
-  bifacial modules, 368 Enphase IQH 380 W microinverters            & 15 minute / 10
-  months                                                            & SAM (Gilman 2015) \\
+  EV charging power ($kW_{ac}$) & Jet Propulsion Lab, Pasadena CA, USA & Measured and aggregated from multiple  EV chargers at single site & 10 sec (average downsampled to 15 min) & Caltech ACN \\
+  Solar irradiance ($W/m^2$)   & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance & 5 min & NSRDB PSMv3 \\
+  PV array production ($kW_{ac}$) & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min & SAM (Gilman 2015) \\
 
@@
 
-\hypertarget{battery}{%
-  \subsection{Battery}\label{battery}}
+%\hypertarget{battery}{%
+\subsection{Battery}\label{battery}%}
 
@@
 
-\hypertarget{electric-tariff}{%
-  \subsection{Electric Tariff}\label{electric-tariff}}
+%\hypertarget{electric-tariff}{%
+\subsection{Electric Tariff}\label{electric-tariff}%}
 
@@
   \toprule
-  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) {[}\${]}                   & Winter (Oct 1 -Feb 28) {[}\${]}   & Spring (Mar 1 - May 30) {[}\${]}  \\
+  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) $[\$]$                   & Winter (Oct 1 -Feb 28) $[\$]$   & Spring (Mar 1 - May 30) $[\$]$  \\
   \midrule
-  All hours                              & 0:00-0:00                                                & 26.07 / kW                                          & 26.07 / kW      & 26.07 / kW \\
-  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-            & 0.079 / kWh \\
-  Off-peak spring                        & \vtop{\hbox{\strut 0:00-9:00,14:00-16:00,}\hbox{\strut 21:00-0:00}} & -\/-                                                     & -\/-              & 0.132 / kWh \\
-  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132 / kWh     & -\/-\\
-  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132 / kWh                                         & -\/-            & -\/-\\
-  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & \vtop{\hbox{\strut 6.81 /
-  kW,}\hbox{\strut 0.159 / kWh}}         & -\/-                                                     & -\/-\\
-  Peak                                   & 16:00-21:00                                              & \vtop{\hbox{\strut 32.90 / kW,}\hbox{\strut 0.196 /
-  kWh}}                                  & \vtop{\hbox{\strut 2.22 / kW,}\hbox{\strut 0.172 / kWh}} & \vtop{\hbox{\strut 2.22 / kW}\hbox{\strut ,0.172 / kWh}}\\
-
-  Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
+  All hours                              & 0:00-0:00                                                & 26.07/$kW$                                          & 26.07/$kW$                        & 26.07/$kW$ \\
+  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-                              & 0.079/$kWh$ \\
+  Off-peak spring                        & 0:00-9:00, 14:00-16:00, 21:00-0:00                       & -\/-                                                & -\/-                              & 0.132/$kWh$ \\
+  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132/$kWh$                       & -\/-\\
+  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132/$kWh$                                         & -\/-                              & -\/-\\
+  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & 6.81/$kW$, 0.159/$kWh$                              & -\/-                              & -\/-\\
+  Peak                                   & 16:00-21:00                                              & 32.90/$kW$, 0.196/$kWh$                             & 2.22/$kW$, 0.172/$kWh$            & 2.22/$kW$, 0.172/$kWh$    \\
   \bottomrule
@@
 
-\hypertarget{peak-shaving-algorithm}{%
-  \subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}}
+%\hypertarget{peak-shaving-algorithm}{%
+\subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}%}
 
@@
   \centering
-  \includegraphics[width=10cm,height=\textheight]{./images/peak shaving flowchart.png}
+  \includegraphics[width=7.5cm]{./images/peak shaving flowchart.png}
   \caption{Peak Shaving Flowchart. Net load is the
@@
 
-\hypertarget{threshold-optimizer}{%
-  \subsection{Threshold Optimizer}\label{threshold-optimizer}}
+%\hypertarget{threshold-optimizer}{%
+\subsection{Threshold Optimizer}\label{threshold-optimizer}%}
 
@@
 
-\hypertarget{simulations}{%
-  \subsection{Simulations}\label{simulations}}
+%\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}%}
 
@@
   \centering
-  \includegraphics[width=15cm,height=\textheight]{./images/simulation flowchart.png}
+  \includegraphics[width=12cm]{./images/simulation flowchart.png}
   \caption{Simulation Flowchart. Given a solar orientation
@@
 
-\hypertarget{case-studies}{%
-  \section{Case Studies}\label{case-studies}}
+%\hypertarget{case-studies}{%
+\section{Case Studies}\label{case-studies}%}
 
@@
   \toprule
-  Case Study                                   & No.
-Modules                               & Orientation & Tilt & \vtop{\hbox{\strut Total Energy }\hbox{\strut {[}\(MWh\){]}}}         & \vtop{\hbox{\strut Solar Yield}\hbox{\strut  {[}\(\frac{kWh}{kW_{DC}}\){]}}}\\
+  Case Study                      & Modules     & Orientation & Tilt  & Total Energy ($MWh$)        & Solar Yield ($\frac{kWh}{kW_{DC}}$) \\
   \midrule
   South 20°                       & 368         & South       & 20°   & 151.7                       & 1180.8\\
-  25\% West 90°                                & \vtop{\hbox{\strut 276}\hbox{\strut 92}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 146.5                                     & 1140.4\\
-  50\% West 90°                                & \vtop{\hbox{\strut 184}\hbox{\strut 184}} & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 141.1                                     & 1098.2\\
-  75\% West 90°                                & \vtop{\hbox{\strut 92}\hbox{\strut 276}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 136.1                                     & 1059.6\\
-  100\% West 90°                               & 368                                       & West        & 90°  & 131.0                    & 1019.3\\
+  \hline
+  \multirow{2}{*}{25\% West 90°}  & 276         & South       & 20°   &\multirow{2}{*}{146.5}       & \multirow{2}{*}{1140.4}\\
+                                  & 92          & West        & 90°   &                             &                         \\
+  \hline
+  \multirow{2}{*}{50\% West 90°}  & 184         & South       & 20°   & \multirow{2}{*}{141.1}      & \multirow{2}{*}{1098.2}\\
+                                  & 184         & West        & 90°   &                             & \\                              
+  \hline                                  
+  \multirow{2}{*}{75\% West 90°}  & 92          & South       & 20°   & \multirow{2}{*}{136.1}      & \multirow{2}{*}{1059.6}\\
+                                  & 276         & West        & 90°   &                             & \\                       
+  \hline
+  100\% West 90°                  & 368         & West        & 90°   & 131.0                       & 1019.3 \\                                                                              
   \bottomrule
@@
 
-\hypertarget{results}{%
-  \section{Results}\label{results}}
+%\hypertarget{results}{%
+\section{Results}\label{results}%}
 
@@
   \centering
-  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost.png}
-  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost reduction.png}
+  \includegraphics[width=6.8cm]{./images/total cost.png}
+  \includegraphics[width=6.8cm]{./images/total cost reduction.png}
   \caption{Total Cost. Total Retail Electric Cost is calculated for each
@@
   \centering
-  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving south.png}
-  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving west.png}
+  \includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
+  \includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
   \caption{Single Day of Peak Shaving. The stacked
@@
   \toprule
-  Battery {[}kWh{]} & Cost South 20° {[}\${]}                & Cost 50\% West 90°
-  {[}\${]}          & Cost 100\% West 90° {[}\${]}           & Cost Reduction 50\% West 90°
-  {[}\${]}          & Cost Reduction 100\% West 90° {[}\${]} & Cost Reduction 50\%
-  West 90° {[}\%{]} & Cost Reduction 100\% West 90°
-  {[}\%{]}\\
+  Battery $[kWh]$ & Cost South 20° $[\$]$ & Cost 50\% West 90° $[\$]$  & Cost 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\$]$ & Cost Reduction 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\%]$ & Cost Reduction 100\% West 90° $[\%]$\\
   \midrule
-  25                & 31314.0                                & 30391.0                      & 31730.0 & 923.0           & -416.0  & 3.0  & -1.3\\
-  50                & 27132.0                                & 25773.0                      & 27022.0 & 1359.0          & 110.0   & 5.0  & 0.4\\
-  75                & 23893.0                                & 22775.0                      & 23625.0 & 1118.0          & 268.0   & 4.7  & 1.1\\
-  100               & 21229.0                                & 19807.0                      & 20804.0 & \textbf{1422.0} & 425.0   & 6.7  & 2.0\\
-  125               & 18954.0                                & 17623.0                      & 18564.0 & 1331.0          & 390.0   & 7.0  & 2.1\\
-  150               & 17094.0                                & 15886.0                      & 17286.0 & 1208.0          & -192.0  & 7.1  & -1.1\\
-  200               & 14547.0                                & 13689.0                      & 15282.0 & 858.0           & -735.0  & 5.9  & -5.0\\
-  400               & 10730.0                                & 10969.0                      & 12131.0 & -239.0          & -1401.0 & -2.2 & -13.1\\
-  600               & 8859.0                                 & 9140.0                       & 10333.0 & -281.0          & -1474.0 & -3.2 & -16.6\\
+  25              & 31314                                & 30391                      & 31730 & 923           & -416  & 3.0  & -1.3\\
+  50              & 27132                                & 25773                      & 27022 & 1359          & 110   & 5.0  & 0.4\\
+  75              & 23893                                & 22775                      & 23625 & 1118          & 268   & 4.7  & 1.1\\
+  100             & 21229                                & 19807                      & 20804 & \textbf{1422} & 425   & 6.7  & 2.0\\
+  125             & 18954                                & 17623                      & 18564 & 1331          & 390   & 7.0  & 2.1\\
+  150             & 17094                                & 15886                      & 17286 & 1208          & -192  & 7.1  & -1.1\\
+  200             & 14547                                & 13689                      & 15282 & 858           & -735  & 5.9  & -5.0\\
+  400             & 10730                                & 10969                      & 12131 & -239          & -1401 & -2.2 & -13.1\\
+  600             & 8859                                 & 9140                       & 10333 & -281          & -1474 & -3.2 & -16.6\\
   \bottomrule
@@
   \centering
-  \includegraphics[width=10cm,height=\textheight]{./images/total cost reduction solar sensitivity.png}
+  \includegraphics[width=10cm]{./images/total cost reduction solar sensitivity.png}
   \caption{Solar Capacity Sensitivity. A sensitivity
@@
   \centering
-  \includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
+  \includegraphics[width=10cm]{./images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
   \caption{Weekly Overlaid Load and Solar Power. The
@@
 
-\hypertarget{conclusion}{%
-  \section{Conclusion}\label{conclusion}}
+%\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}%}
 
@@
 sets with more months of data, a more comprehensive battery model, an
-operational version of the peak shaving strategy, and testing at the
-Politecnico di Milano M2GLab microgrid.
+operational peak shaving strategy, and testing at the
+Politecnico di Milano M2GLab microgrid. \cite{Wagner2019}
 
-\hypertarget{bibliography}{%
-  \section{Bibliography}\label{bibliography}}
+%\hypertarget{bibliography}{%
+\section{Bibliography}\label{bibliography}%}
+
+\bibliography{mendeley.bib}
 

### 2023-12-19 Paper/make.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+cp paper.tex ./tex/paper.tex;
+cp mendeley.bib ./tex/mendeley.bib;
+cd tex;
+pdflatex -interaction=nonstopmode paper;
+bibtex paper;
+pdflatex -interaction=nonstopmode paper;
+pdflatex -interaction=nonstopmode paper;
+mv paper.pdf ../paper.pdf;

### 2023-12-20 Paper/paper.tex
paper v1 sent to ema

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+
+%=================================================================
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
+
+%=================================================================
+% MDPI internal commands - do not modify
+\firstpage{1} 
 \makeatletter 
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\setcounter{page}{\@firstpage} 
 \makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2023}
+\copyrightyear{2023}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{ } 
+\daterevised{ } % Comment out if no revised date
+\dateaccepted{ } 
+\datepublished{ } 
+%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
+%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%\pdfoutput=1 % Uncommented for upload to arXiv.org
 
-\usepackage{tabularx}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage{geometry}
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
+% cleveref: load \crefname definitions after \begin{document}
 
-\author{}
-\date{}
+\usepackage[acronym]{glossaries}
+\usepackage{hhline}
+\usepackage{threeparttable} % to use table notes
+%\usepackage[draft]{changes} % usage: \deleted{old} \added{new} \replaced{new}{old} also \hl{} for highlighted text
+%\usepackage[final]{changes}
+
+%=================================================================
+% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load at the Jet Propulsion Laboratory}
+
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}
+
+\newcommand{\orcidauthorA}{0000-0003-0237-4148} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-2106-0374} % Add \orcidB{} behind the author's name
+
+\newcommand{\orcidauthorC}{0000-0002-7883-0034}
+
+% Authors, for the paper (add full first names)
+\Author{
+  Michael Wood $^{1,2,*}$\orcidA{},
+  Emanuele Ogliari $^{1}$\orcidB{},
+  Travis Simpkins $^{2}$, and
+  Sonia Leva $^{1}$\orcidC{}}
+
+%\longauthorlist{yes}
+
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{Michael Wood, Emanuele Ogliari, Travis Simpkins, and Sonia Leva}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Wood, M.; Ogliari, E.; Simpkins, T.; Leva, S.}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Department of Energy, Politecnico di Milano, Via Lambruschini 4a, 20156, Milan, Italy; emanuelegiovanni.ogliari@polimi.it (E.O.); sonia.leva@polimi.it (S.L.) \\
+$^{2}$ \quad muGrid Analyics LLC., 14143 Denver West Parkway Ste 100, Golden, CO, USA; travis@mugrid.com}
+
+% Contact information of the corresponding author
+\corres{Correspondence: michael.wood@polimi.it}
+
+\abstract{Electric load peak shaving is a challenging and important problem considering the rapid growth of high-power electric vehicle charging sites.
+A co-located solar array provides locally produced energy, but an additional storage battery is required for reliable peak shaving.
+With occasional evening load peaks and an electric tariff with a 16:00-21:00 peak time of use period, vertical bifacial modules facing West have an economic advantage due to more of the production being shifted into the late afternoon and early evening.
+Exploiting this, an optimal electric load peak shaving simulator dispatches a stationary battery to minimize the retail electric cost incurred by a real electric vehicle charging site over 10 months.
+Five different case studies of co-located bifacial solar photovoltaic arrays are simulated, a base case oriented South and tilted at 20° and four experimental cases where a percentage (25\%, 50\%, 75\%, or 100\%) of the array is oriented West and tilted at 90°.
+The problem is formulated such that the optimizer minimizes the retail electric cost by adjusting three peak power thresholds, each corresponding to a time of use period with an associated power price in \(\$/kW\).
+The optimizer is implemented using a Newton-Raphson gradient descent approach and the optimality of the method is verified to within 0.1 \(kW\).
+A sensitivity analysis on battery energy capacity results in the largest cost reduction, relative to the South 20° base case, of \$1422 (6.7\%) achieved by the 50\% West 90° case and a modest 25 kWh battery.
+A second sensitivity analysis on solar power capacity shows that the cost reduction increases monotonically and logarithmically for all cases and battery capacities.
+The largest cost decrease is \$2579 (16.1\%), achieved by the 75\% West 90° case at 200\% of nominal solar capacity along with a 125 kWh battery.
+Both data and code are shared with the public on GitHub.}
+
+% Keywords
+\keyword{electric load; peak shaving; bifacial solar PV; EV charging;}
 
@@
 
-\hypertarget{abstract}{%
-  \section{Abstract}\label{abstract}}
+\section{Introduction}\label{introduction}
 
-Electric load peak shaving is a challenging and important problem
-considering the rapid growth of high power electric vehicle charging
-sites. Co-located solar photovoltaic provides locally produced energy,
-but an additional storage battery is required for reliable peak shaving.
-With occasional evening load peaks and an electric tariff with a
-16:00-21:00 peak time of use period, vertical bifacial modules facing
-West have an economic advantage due to more of the production shifted
-into the late afternoon and early evening. Exploiting this, an optimal
-electric load peak shaving simulator dispatches a stationary battery to
-minimize the retail electric cost incurred by a real electric vehicle
-charging site over 10 months. Five different case studies of co-located
-bifacial solar photovoltaic arrays are simulated, a base case oriented
-South and tilted at 20° and four experimental cases where a percentage
-(25\%, 50\%, 75\%, or 100\%) of the array is oriented West and tilted at
-90°. The problem is formulated such that the optimizer minimizes the
-retail electric cost by adjusting three peak power thresholds, each
-corresponding to a time of use period with an associated power price in
-\(\$/kW\). The optimizer is implemented using a Newton-Raphson gradient
-descent approach and the optimality of the method is verified to within
-0.1 \(kW\). A sensitivity analysis on battery energy capacity results in
-a largest cost reduction, relative to the South 20° base case, of \$1422
-(6.7\%) achieved by the 50\% West 90° case and a modest 25 kWh battery.
-A second sensitivity analysis on solar power capacity shows that the
-cost reduction increases monotonically and logarithmically for all cases
-and battery capacities. The largest cost decrease is \$2579 (16.1\%),
-achieved by the 75\% West 90° case at 200\% of nominal solar capacity
-along with a 125 kWh battery. Both data and code are shared to the
-public on GitHub.
+%\subsection{Why peak load}\label{why-peak-load}
 
-\hypertarget{introduction}{%
-  \section{Introduction}\label{introduction}}
+The renewable energy transition will oversee a global shift toward electric energy consumption and renewable electric energy production in the coming decades.
+Since most electric transmission and distribution networks were built slowly over many decades, electric load growth will almost definitely outpace network upgrades.
+And where these upgrades are completed they are necessarily an additional cost paid by all electricity consumers, due to the decrease in the load factor.
+Furthermore, in some markets where companies can own both generation and distribution, business-as-usual infrastructure upgrades with cost plus or rate of return regulation may be prioritized over the new construction of more complex and financially riskier renewable generators \cite{Wagner2019}.
+For these reasons, two important solution areas for overall clean generation deployment speed and cost-effectiveness are distributed energy production and peak load reduction, or peak shaving.
 
-\hypertarget{why-peak-load}{%
-  \subsection{Why peak load}\label{why-peak-load}}
+Two new categories of load growth that will strain electric networks in most countries are electric heating and cooling, including traditional air conditioning and heat pumps, and Electric vehicle (EV) charging \cite{Bobmann2015}.
+Heat pump and air conditioning load factor may be increased with architectural features such as insulation and thermal storage, but building efficiency retrofits often experience barriers such as regulation and financing mechanisms due to permitting and other challenges \cite{Bertone2016}.
+Meanwhile, extreme weather events, especially heat waves, will likely further reduce the load factor of these loads \cite{Villa2022}.
+EV charging load differs in that consumers will have the flexibility to slowly charge overnight at home for convenience and to minimize their energy costs.
+However, workplace, fleet, and public EV charging stations will likely still be required and will experience large peaks as consumers require the convenience of fast charging at stations capable of hundreds of kW per vehicle.
 
-The renewable energy transition will oversee a global shift toward
-electric energy consumption and renewable electric energy production in
-the coming decades. Since most electric transmission and distribution
-networks were previously built slowly over the span of many decades,
-electric load growth will almost definitely outpace network upgrades.
-And where these upgrades are completed they are necessarily an
-additional cost paid by all electricity consumers, due to the decrease
-in the load factor. Furthermore in some markets where companies can own
-both generation and distribution, business-as-usual infrastructure
-upgrades may be prioritized over the new construction of more complex
-and financially risky renewable generators. So while there are some
-creative solutions around dynamic capacity limits, two important
-solution areas for overall deployment speed, cost effectiveness, and
-overall decarbonization goals are (a) more local energy production and
-(b) increasing the load factor.
+%\hypertarget{peak-shaving}{%
+%\subsection{Peak shaving}\label{peak-shaving}%}
 
-Electric vehicle (EV) charging and electric heating and cooling,
-including traditional air conditioning and heat pumps, are two common
-new loads that will strain networks in most countries. Heat pump and air
-conditioning load factor may be increased with architectural features
-such as insulation and thermal storage, but building retrofits are often
-slowed down due to permitting and other challenges. Meanwhile extreme
-weather events, especially heat waves, will likely further reduce the
-load factor of these devices. Many EV users will choose to slowly charge
-overnight at home for convenience and to minimize their energy cost.
-However workplace, fleet, and public EV charging stations will likely
-still be required, and these may especially suffer from a low load
-factor due to the convenience or need of fast charging at high power.
+Peak load management, or peak shaving, is the process of reducing the maximum load at a given point in an electrical network.
+This will necessarily increase the load factor,$P_{load,avg} P_{load,max}^{-1}$, even if load curtailment is the only method used.
+Other methods include load scheduling, load shifting using energy storage, and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}.
+Peak shaving may include the concept of a peak load threshold which defines a maximum desired peak load during a period, typically on the order of hours.
+Grid operators may use peak shaving to increase power quality, defer future infrastructure upgrades, decrease losses, or reduce energy costs.
+End-users typically reduce their peaks solely on a cost basis.
+Lastly, some carbon reduction is possible by reducing the on/off transitions of peaker plants due to load peaks \cite{Uddin2018}.
+Broadly speaking there are two categories of peak shaving goals: technical and economic.
 
-\hypertarget{peak-shaving}{%
-  \subsection{Peak shaving}\label{peak-shaving}}
+%\hypertarget{technical}{%
+%\subsubsection{Technical}\label{technical}%}
 
-Peak load management, or peak shaving, essentially requires choosing a
-power threshold and holding the load power below it. Controllable loads,
-energy storage, or generation assets behind the billing meter can all be
-used to reduce the load power to the threshold power. The threshold may
-only apply for only certain time periods. There may be multiple
-thresholds and periods each day, month, or year. There are two general
-cases of peak shaving worth considering. The most generation formulation
-of peak shaving control is formulated in Equation \ref{eg:peakshaving-general}.
-
-\begin{equation}
-  \label{eg:peakshaving-general}
-  \begin{split}
-    I_{threshold,t} &> I_{j,t} - \Sigma_i I_{gen,i,t} - \Sigma_j I_{gen,up,j,t} - \Sigma_k I_{load,dn,k,t}  \\
-    \\
-    &\text{where:} \\
-    &i\text{ is generation asset with no flexibility} \\
-    &j\text{ is generation asset with upward flexibility} \\
-    &k\text{ is controllable load asset with downward flexibility} \\
-    &t\text{ is relevant timesteps}
-  \end{split}
-\end{equation}
-
-Here we consider the case of no controllable load, a single battery,
-solar which reduces the site load, and all values in units of average
-real power over the interval \(\Delta h = 1\ hour\). This is descrbied in Equation \ref{eq:peakshaving}.
-
-\begin{equation}
-  \label{eq:peakshaving}
-  \begin{split}
-    P_{threshold,h} &> P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}   \\
-    &\text{where:} \\
-    P_{batt,discharge,h} &\ge 0 \\
-    P_{batt,charge,h} &\le 0 \\
-    h &\in \{0,1,2,...23\} \\
-  \end{split}
-\end{equation}
-
-\hypertarget{technical}{%
-  \subsubsection{Technical}\label{technical}}
-
-Technical peak shaving refers to the case where a load must operate
-under a technical limitation such as a maximum power agreement or
-distribution transformer size. The load power must remain under the
-threshold at all times, otherwise there may be a technical failure such
-an activated overcurrent protection. Even if the load is technically
-able to rise above the threshold, doing so may violate a contract
-regarding maximum load power. The important consideration is that the
-economic cost of failure to hold the load under the threshold is
-prohibitively high. The time resolution of technical peak shaving
-control and modeling may need to be as low as seconds or milliseconds.
-Although this may be a challenging problem if the current limit is
-dynamically set or if a larger network is considered, from the
-perspective of dispatching the assets to shave the peak the problem is a
-relatively simple one: economic dispatch such that the the load current
-remains below the threshold current. Technical peak shaving might be
-performed on current or apparent power rather than active power.
-
-\hypertarget{economic}{%
-  \subsubsection{Economic}\label{economic}}
-
-Rather, economic peak shaving aims to reduce what a consumer pays for
-power and possibly also energy. Medium and large electric consumers
-often pay a price on energy (€\(/kWh\)) and a price on power
-(€\(/kWh_{peak}\)), also called a demand charge. The energy cost
-(€\(/kWh \times E_{consumed}\)) may vary with time of day, day of week,
-and season of the year, which is often referred to as time of use or
-peak pricing. Where there is a sufficient spread between the peak and
-off-peak prices there may be the opportunity to curtail load during high
-prices, use controllable loads to shift from a high price period to a
-lower one, or to use energy storage to buy energy at the lower price and
-reduce load during a higher price period. A peak shaving approach
-applied to the energy cost could be effective and maybe even
-advantageous. However there are several key differences between an
-energy based approach and a power one, where peak shaving is better
-suited for the latter.
-
-Instead, the power cost (€\(/kW \times P_{max}\) ) typically applies to
-the max power during the billing period, where the peak power is the
-maximum non-moving average in a given period (e.g. 12:00-18:00 on
-weekdays) calculated on a given interval (e.g. 60 minutes). Similar to
-the energy cost, there may be multiple time of use periods and
-associated prices, such as peak, mid-peak, and off-peak. And where the
-spread price is sufficiently high, the period peak can be reduced with
-load curtailment or rescheduling, distributed generation such as solar,
-or energy storage.
+Technical peak shaving refers to the case where a load must operate under a technical limitation such as a maximum power agreement or distribution transformer size.
+The load power must remain under the threshold at all times, otherwise, overcurrent protection may be activated or permanent damage to equipment such as lines or transformers.
+Even if the current is technically able to rise above the threshold, doing so may violate a contract regarding maximum load power.
+The important consideration is that the economic cost of exceeding the threshold is prohibitively high.
+The time resolution of technical peak shaving control may need to be as low as seconds or milliseconds \cite{Iannarelli2020}.
+Although technical peak shaving is complicated by a large network, many assets, or a dynamic threshold, from the perspective of dispatching the assets to shave the peak the problem is relatively simple.
+Technical peak shaving might be performed on current or apparent power rather than active power.
 
@@
     \midrule
-    Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
-    Averaging interval                     & 1 minute                                 & 15 minutes or 1 hour (typical) \\
+    Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
+    Time resolution                     & $\mu s$ to 10 s                                & 15-60 min or 1 h (typical)    \\
     Valid times of day                     & All                                      & Limited (e.g. 16:00 to 21:00)     \\
@@
 
-\hypertarget{methodology}{%
-  \section{Methodology}\label{methodology}}
+%\hypertarget{economic}{%
+%\subsubsection{Economic}\label{economic}%}
+
+Economic peak shaving aims to reduce what a consumer pays for power and or energy.
+Medium and large electric consumers often pay an energy price ($p_e\ [\$/kWh]$) and a power price ($p_p\ [\$/kW]$), also called a demand charge.
+Each may vary with time of day, day of week, and season of the year, which is often referred to as time of use (TOU) or peak pricing.
+The power cost ($p_p max(P_{load}\ [\$])$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes.
+Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to load reschedule, shift, or curtail, or dispatch DG.
+
+This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:peakshaving}.
+The load may not be curtailed or rescheduled, but solar DG naturally reduces the load and a storage battery is dispatched in a threshold-based peak shaving strategy.
+The minimum time interval of the threshold is 1 hour.
+
+\begin{equation}
+  \label{eq:peakshaving}
+  \begin{split}
+    P_{threshold,h} & \ge P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}                     \\
+                    & \text{where:}                                                                               \\
+    P               & \text{ is average power (threshold, load, solar, battery) }\ [kW]                             \\
+    0               & \le  P_{load,h}, P_{solar,h}, P_{batt,discharge,h}, P_{batt,discharge,h}, P_{batt,charge,h} \\
+    h               & \in \{0,1,2,...,23\}                                                                        \\
+  \end{split}
+\end{equation}
+
+%\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}%}
 
@@
   \centering
-  \includegraphics[width=5cm,height=\textheight]{./images/oneline.png}
-  \caption{Charging Site One Line Schematic. Simplified
-  one-line schematic of the simulated EV charging station with true
-  measured EV charging power, modelled on-site solar generation, and a
-  modelled stationary battery for economic peak shaving.}
+  \includegraphics[width=7.5cm]{./images/oneline.png}
+  \caption{Charging Site One Line Schematic.
+Simplified one-line schematic of the simulated EV charging station with true measured EV charging power, modeled on-site solar generation, and a modeled stationary battery for economic peak shaving.}
   \label{fig:oneline}
@@
 
-The methodology of this study is a set of offline simulations involving
-(a) EV charging power measurements, (b) modelled solar photovoltaic (PV)
-production power, and (b) AC-coupled battery dispatch, all behind the
-retail electric meter. These are represented in in Figure \ref{fig:oneline}.
-In each simulation the battery power is chosen
-such that the net load (natural load less solar production, Equation \ref{eq:net-load}) is held
-below a given threshold, which is optimally chosen by a gradient descent
-optimizer.
+The methodology of this study is a set of offline simulations involving (a) EV charging power measurements, (b) modeled solar photovoltaic (PV) production power, and (b) AC-coupled battery dispatch, all behind a retail electric meter.
+These are represented in Figure \ref{fig:oneline}.
+In each simulation, the battery power is chosen such that the net load (true load less solar production, Equation \ref{eq:net-load}) is held below a given threshold, which is optimally chosen by a gradient descent optimizer.
 
@@
   \begin{split}
-    NL &= L - S \\
-    &\text{where:} \\
-    &L(t) \text{ is EV charging load time series (non-negative)}\ [kW]\\
-    &S(t) \text{ is solar production time series}\ [kW] \\
+    NL & = L - S                                                           \\
+       & \text{where:}                                                     \\
+       & NL(t) \text{ is the net load time series (non-negative)}\ [kW] \\
+       & L(t) \text{ is the EV charging load time series (non-negative)}\ [kW] \\
+       & S(t) \text{ is the solar production time series}\ [kW]                \\
   \end{split}
@@
 
-The optimal threshold changes for each time of use (TOU)
-period. A single simulation is defined for one solar configuration and
-battery capacity and lasts one calendar month, which is the shortest
-period for which the cost function is defined. Simulations are repeated
-for several months of data, and many different solar and battery design
-sizes, allowing for a retail energy cost comparison among different
-design scenarios. EV charging power or solar are never curtailed. The
-primary decision variables in each time step are (a) battery charge or
-discharge, and (b) battery power.
+The optimal threshold changes for each TOU period.
+A single simulation is defined for one solar configuration and battery capacity and lasts one calendar month, which is the shortest period for which the cost function is defined.
+Simulations are repeated for several months of data, and many different solar and battery design sizes, allowing for a retail energy cost comparison among different design scenarios.
+EV charging power and solar production are never curtailed.
+The primary decision variable in each time step is battery charge or discharge power, which is not necessarily formulated as a binary variable.
+Nonetheless, the battery can only charge, discharge, or do nothing in each time step.
 
-\hypertarget{data}{%
-  \subsection{Data}\label{data}}
+%\hypertarget{data}{%
+\subsection{Data}\label{data}%}
 
-\hypertarget{ev-charging-load}{%
-  \subsubsection{\texorpdfstring{EV Charging Load
-    }{EV Charging Load }}\label{ev-charging-load}}
+%\hypertarget{ev-charging-load}{%
+%\subsubsection{\texorpdfstring{EV Charging Load
+%    }{EV Charging Load }}\label{ev-charging-load}%}
+\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}
 
-The measured EV charging power ("load") is from the Caltech Adaptive
-Charging Network database at the Jet Propulsion Lab (JPL) site. Each
-charging session provides time series active power, averaged over a 10
-second interval. In the cases when complete time series data is not
-available for a session, the charging profile is estimated and the total
-charging energy delivered is the same. The disaggregated session time
-series data is summed into a single time series of total site charging
-power, which is then averaged over 15-minute intervals. Time stamp
-indices refer to the beginning of the 15-minute interval. The data
-period is from 2018-5-1 00:00 to 2019-2-28 23:45.
+The measured EV charging power ("load") is from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}.
+Each charging session provides time series active power, averaged over a 10-second interval.
+In the cases when complete time series data is not available for a session, the charging power is assumed constant such that the total charging energy delivered is consistent with the primary data.
+The disaggregated session data is summed into a total site charging power time series, which is then averaged over 15-minute intervals.
+Timestamp indices refer to the beginning of the 15-minute interval.
+The data period is from 2018-5-1 00:00 to 2019-2-28 23:45.
 
-\hypertarget{solar-production}{%
-  \subsubsection{Solar Production}\label{solar-production}}
+%\hypertarget{solar-production}{%
+\subsubsection{Solar Production}\label{solar-production}%}
 
-The modelled PV production power begins life as Geostationary
-Operational Environmental Satellite (GOES) satellite solar irradiance
-data from the US National Solar Resource Database (NSRDB), and is
-specific to the exact time and date rather as opposed to typical
-meteorological year data. See Table \ref{tab:data-summary}. Prism Solar 350 W bifacial solar module DC
-electrical power is estimated using the California Energy Commission
-Performance Model, a 6-parameter physical PV cell model. The full AC
-array power is estimated given loss assumptions and an inverter
-efficiency lookup table in the US National Renewable Energy Laboratory
-(NREL) System Advisor Model (SAM) database for the Enphase IQH 380 W
-microinverter. All these functions are implemented in SAM v2022.11.21.
-
-Five different solar array orientations are modelled and simulated in
-different case studies. See Table \ref{tab:casestudies}. Each orientation has the same number and type of bifacial
-modules. In the first orienation all modules facing South at 20° tilt. In the remaining four
-orientation a percentage of the modules face all modules face West at 90° tilt: 25\%, 50\%, 75\%, and then 100\%.
-Tilt is defined as 90° minus the altitude angle of the normal vector of the primary active face of 
-the module. No shading is considered. Of the two sides of the bi-facial module, the primary active 
-face is oriented West since afternoon load is generally subject to higher prices.
+The modeled PV production power begins life as Geostationary Operational Environmental Satellite (GOES) satellite solar irradiance data from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}.
+These data are specific to the years in question and are not from a typical meteorological year (TMY) set.
+See Table \ref{tab:data-summary}.
+Prism Solar 350 W bifacial solar module DC electrical power is estimated using the California Energy Commission Performance Model, a 6-parameter physical PV cell model.
+The full AC array power is estimated given loss assumptions and an inverter efficiency lookup table in the US National Renewable Energy Laboratory (NREL) System Advisor Model (SAM) database \cite{NREL2022} for the Enphase IQH 380 W microinverter.
+All these functions are implemented in SAM v2022.11.21 \cite{NREL2022}.
+Five different solar array orientations are modeled and simulated in different case studies, summarized in Table \ref{tab:casestudies}.
+Each orientation has the same number and type of bifacial modules.
+In the first orientation, all modules face South at a 20° tilt.
+In the remaining four orientations a percentage of the modules face all modules face West at 90° tilt: 25\%, 50\%, 75\%, and then 100\%.
+Tilt is defined as 90° minus the altitude angle of the normal vector of the primary active face of the module.
+No shading is considered.
+Of the two sides of the bi-facial module, the primary active face is oriented West since the afternoon load is generally subject to higher prices.
 
@@
   \centering
-  \caption{Timeseries Data Summary. EV charging power is
-  measured every 10 seconds for 10 months at the Jet Propulsion
-  Laboratory, CA, USA. Solar irradiance from the GOES satellite is
-  acquired for the same location. Solar PV array production is modelled
-  from the satellite irradiance using a 6 parameter PV cell model and
-  inverter efficiency lookup table.\label{tab:loadsectors}}
+  \caption{Timeseries Data Summary.
+EV charging power is measured every 10 seconds for 10 months at the Jet Propulsion Laboratory, CA, USA.
+Solar irradiance from the GOES satellite is acquired for the same location.
+Solar PV array production is modeled from the satellite irradiance using a 6-parameter PV cell model and inverter efficiency lookup table.\label{tab:loadsectors}}
   \label{tab:data-summary}
-  \begin{tabularx}{\textwidth}{XXXXX}
+  \begin{tabularx}{\linewidth}{XXXXX}
+    % { >{\hsize=.25\hsize\linewidth=\hsize}X
+    %   >{\hsize=.25\hsize\linewidth=\hsize}X
+    %   >{\hsize=.7\hsize\linewidth=\hsize}X
+    %   >{\hsize=.1\hsize\linewidth=\hsize}X
+    %   >{\hsize=.2\hsize\linewidth=\hsize}X
+    % }
+    %\begin{tabularx}{llllll}
     \toprule
-  Timeseries Description & Location & Type & Interval / Length & Source  \\
+    Description                     & Location                                & Type                                                                                                             & Interval                               & Source            \\
     \midrule
-  \vtop{\hbox{\strut EV charging power}\hbox{\strut (\(kW_{ac}\))}} & Jet
-  Propulsion Lab, Pasadena CA, USA                                  & Measured and aggregated from multiple
-  EV chargers at single site                                        & 10 sec (average downsampled to 15 min) / 10
-  months                                                            & Caltech ACN \\
-
-  \vtop{\hbox{\strut Solar irradiance }\hbox{\strut (\(W/m^2\))}}   & GPS:
-  34.2013, -118.1721 (2x2 km square)                                & GOES satellite irradiance                                 & 5
-  minute / 10 months                                                & NSRDB PSMv3 \\
-
-  PV array production (\(kW_{ac}\))                                 & GPS: 34.2013, -118.1721 (2x2 km
-  square)                                                           & Modelled from satellite irradiance, 368 Prism Solar 350 W
-  bifacial modules, 368 Enphase IQH 380 W microinverters            & 15 minute / 10
-  months                                                            & SAM (Gilman 2015) \\
+    EV charging power $[kW_{ac}]$    & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                & 10 sec (average downsampled to 15 min) & Caltech ACN (JPL) \cite{Lee2021}  \\
+    Solar irradiance $[W/m^2]$       & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                        & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}       \\
+    PV array production $[kW_{ac}]$ & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from GOES satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min                                 & SAM \cite{NREL2022} \\
 
@@
 
-\hypertarget{battery}{%
-  \subsection{Battery}\label{battery}}
+%\hypertarget{battery}{%
+\subsection{Battery}\label{battery}%}
 
-A stationary, storage battery system is simulated as the primary
-decision variable in the peak shaving algorithm. In each timestep the
-battery is chosen to charge or discharge within its technical limits.
-Because the control action is to hold the power exchange with the grid
-to below a certain threshold, batteries with a larger power capacity or
-energy capacity will necessarily achieve a lower threshold if the entire
-battery capacity is used. For a given energy capacity (\(kWh\)) those
-limits are a charge or discharge rate no more than 1C and state of
-charge (SOC) between 0 and 100\% of rate. State of energy (SOE) is the
-SOC multiplied by nominal energy capacity and is used in plots because
-the units are more meaningful when comparing dispatch time series.
-Half-round-trip charge and discharge efficiency is constant at 90\% and
-no self discharge or thermal limiting are considered.
+A stationary, storage, AC battery system is simulated as the only dispatchable asset in the peak shaving algorithm.
+In each time step the battery is chosen to charge or discharge within its technical limits.
+Because the control action is to hold the grid power exchange below a chosen threshold, batteries with a larger power capacity or energy capacity will necessarily achieve a lower threshold if the entire battery capacity is used.
+For a given energy capacity (\(kWh\)) those limits are a charge or discharge rate of no more than 1C and a state of charge (SOC) between 0 and 100\%.
+State of energy (SOE) is the SOC multiplied by nominal energy capacity and is reported in plots because the units are more meaningful when comparing dispatch time series.
+Half-round-trip charge and discharge efficiencies are constant at 90\%.
+Self-discharge and thermal limiting are not modeled specifically.
 
-There are many strategies for optimal battery sizing, but the emphasis
-in this work is instead on understanding the dynamics between load,
-shape of the solar curve, and peak shaving algorithm for a given battery
-size. Therefore a sensitivity analysis is performed on the battery
-energy capacity, but no one battery size is declared economically
-optimal.
+There are many strategies for optimal battery sizing, but the emphasis in this work is instead on understanding the dynamics between load, the shape of the solar curve, and peak shaving algorithm for a given battery size.
+Therefore a sensitivity analysis is performed on the battery energy capacity, but no one battery size is declared economically optimal.
 
-Each simulation assumed charge and discharge rate are limited to 1C,
-usable SOC is assumed 100\%, and self discharge, parasitic losses, and
-thermal limiting are not considered.
+Each simulation assumed charge and discharge rate are limited to 1C, usable SOC is assumed 100\%, and self-discharge, parasitic losses, and thermal limiting are not considered.
 
-\hypertarget{electric-tariff}{%
-  \subsection{Electric Tariff}\label{electric-tariff}}
+%\hypertarget{electric-tariff}{%
+\subsection{Electric Tariff}\label{electric-tariff}%}
 
-A typical California electric tariff is applied at the point of the
-retail electric meter with several different TOU periods and prices. See Table \ref{tab:tariff}.
-For the chosen tariff each TOU period may have an energy price
-(\(\$/kWh\)), a power price (\(\$/kW\)), or both. The prices may also
-change between seasons, and have long term trends like any retail
-electric prices. Here a price on power ("demand charge") is understood
-as a \(\$/kW\) price applied to the monthly maximum power observed at
-the meter, calculated as the 15-minute average of real power.
+A typical California electric tariff is applied at the point of the retail electric meter with several different TOU periods and prices.
+See Table \ref{tab:tariff}.
+For the chosen tariff each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both.
+The prices may also change between seasons and have long-term trends like any retail electric prices.
 
@@
   \centering
-  \caption{Retail Electric Tariff. An applicable electric
-  tariff schedule with seven different TOU periods for energy and power
-  prices, varying by hours of the day and season of the year. From
-  California PG\&E.}
+  \caption{Retail Electric Tariff.
+An applicable electric tariff schedule with seven different TOU periods for energy and power prices, varying by hours of the day and season of the year.
+From California PG\&E.}
   \label{tab:tariff}
@@
     \toprule
-  Name                                   & TOU Period                                               & Summer (Jun 1 - Sept 30) {[}\${]}                   & Winter (Oct 1 -Feb 28) {[}\${]}   & Spring (Mar 1 - May 30) {[}\${]}  \\
+    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
     \midrule
-  All hours                              & 0:00-0:00                                                & 26.07 / kW                                          & 26.07 / kW      & 26.07 / kW \\
-  Super off-peak                         & 9:00-14:00                                               & -\/-                                                & -\/-            & 0.079 / kWh \\
-  Off-peak spring                        & \vtop{\hbox{\strut 0:00-9:00,14:00-16:00,}\hbox{\strut 21:00-0:00}} & -\/-                                                     & -\/-              & 0.132 / kWh \\
-  Off-peak winter                        & 0:00-16:00, 21:00-0:00                                   & -\/-                                                & 0.132 / kWh     & -\/-\\
-  Off-peak summer                        & 0:00-14:00, 23:00-0:00                                   & 0.132 / kWh                                         & -\/-            & -\/-\\
-  Partial-peak                           & 14:00-16:00, 21:00-23:00                                 & \vtop{\hbox{\strut 6.81 /
-  kW,}\hbox{\strut 0.159 / kWh}}         & -\/-                                                     & -\/-\\
-  Peak                                   & 16:00-21:00                                              & \vtop{\hbox{\strut 32.90 / kW,}\hbox{\strut 0.196 /
-  kWh}}                                  & \vtop{\hbox{\strut 2.22 / kW,}\hbox{\strut 0.172 / kWh}} & \vtop{\hbox{\strut 2.22 / kW}\hbox{\strut ,0.172 / kWh}}\\
-
-  Consequence of exceeding the threshold & Damage to infrastructure,possible outage & Monetary cost depending on tariff \\
+    All hours       & 0:00-0:00                          & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
+    Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
+    Off-peak spring & 0:00-9:00, 14:00-16:00, 21:00-0:00 & -\/-                            & -\/-                          & 0.132/$kWh$                    \\
+    Off-peak winter & 0:00-16:00, 21:00-0:00             & -\/-                            & 0.132/$kWh$                   & -\/-                           \\
+    Off-peak summer & 0:00-14:00, 23:00-0:00             & 0.132/$kWh$                     & -\/-                          & -\/-                           \\
+    Partial-peak    & 14:00-16:00, 21:00-23:00           & 6.81/$kW$, 0.159/$kWh$          & -\/-                          & -\/-                           \\
+    Peak            & 16:00-21:00                        & 32.90/$kW$, 0.196/$kWh$         & 2.22/$kW$, 0.172/$kWh$        & 2.22/$kW$, 0.172/$kWh$         \\
     \bottomrule
@@
 
-The total retail electric cost \(C\) for each month is then the sum of
-the energy cost and power cost for the month, where the energy and power
-costs are calculated separately for each TOU period. See Equation \ref{eq:cost}. The energy cost is
-the energy delivered to the site multiplied by the energy price for that
-TOU period. The power cost is the maximum 15-minute average power for
-the month multiplied by the power price for that TOU period. Only
-positive values of site load \(SL\) are used in the cost calculation
-since the monthly peak power for each TOU period must always be positive
-and necessarily cannot benefit from net metering (export to the grid).
+The total retail electric cost \(C\) for each month is then the sum of the energy cost and power cost for the month, where the energy and power costs are calculated separately for each TOU period.
+See Equation \ref{eq:cost}.
+The energy cost is the energy delivered to the site multiplied by the energy price for that TOU period.
+The power cost is the maximum of the 15-minute non-moving average load power for the month, multiplied by the power price for that TOU period.
+Only positive values of net load \(NL\) affect cost since the monthly peak power for each TOU period must always be positive and necessarily cannot benefit from net metering (export to the grid).
 
@@
   \begin{split}
-    C_m &= \Sigma_k^K [ p_{p,k,m} max(NL^+_{k,m} + B_d - B_c + p_{e,k,m} \Sigma (NL^+_{k,m} + B_d(t) - B_c(t)) ] \\
-    \\
+    C_m & = \Sigma_k^K [ p_{p,k,m} max(NL^+_{k,m} + B_d - B_c + p_{e,k,m} \Sigma (NL^+_{k,m} + B_d(t) - B_c(t)) ] \\
         & \text{where:}                                                                                           \\
-    & NL^+(t) = NL(t),\ \forall\ NL(t)>0\\
-    &B_c(t) \text{ is battery charging power time series(non-negative)}\ [kW]\\
-    &B_d(t) \text{ is battery discharging power time series(non-negative)}\ [kW] \\
-    &C_m \text{ is total retail electric cost for month}\ m\ [\$] \\
-    &p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  [\$/kW] \\
-    &p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ [\$/kWh] \\
-    &K \text{ is number of TOU periods}
+        & NL^+(t) = NL(t),\ \forall\ NL(t)>0                                                                      \\
+        & B_c(t) \text{ is battery charging power time series(non-negative)}\ [kW]                                \\
+        & B_d(t) \text{ is battery discharging power time series(non-negative)}\ [kW]                             \\
+        & C_m \text{ is total retail electric cost for month}\ m\ [\$]                                            \\
+        & p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  [\$/kW]                       \\
+        & p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ [\$/kWh]                      \\
+        & K \text{ is number of TOU periods}
   \end{split}
@@
 
-\hypertarget{peak-shaving-algorithm}{%
-  \subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}}
+%\hypertarget{peak-shaving-algorithm}{%
+\subsection{Peak Shaving Algorithm}\label{peak-shaving-algorithm}%}
 
-An optimal peak shaving strategy is used to minimized the total retail
-electric cost to the EV charging station. The strategy is operational
-only, and assumes the solar production timeseries and battery capacity
-are fixed. The state variable controlled by the algorithm is battery
-charge or discharge power. However the algorithm reframes the problem as
-one of choosing a power threshold \(T\ (kW)\) applied to the point of
-injection to the grid, the electric meter. The battery is then
-dispatched, within its technical limits, to hold the net load (natural
-load less solar production) below the threshold. When the algorithm is
-successful the different thresholds for each TOU period are met for an
-entire month. If the battery reaches a technical limit and net load
-exceeds a threshold, the simulation is not necessarily invalid but is
-not likely to minimize the retail electric cost to the site for that
-combination of solar and battery size. The peak shaving logic is
-described in Figure \ref{fig:peakshaving-flowchart}.
+An optimal peak shaving strategy is used to minimize the total retail electric cost to the EV charging station.
+The strategy is operational only and assumes the solar production time series and battery capacity are fixed.
+The state variable controlled by the algorithm is battery charge or discharge power.
+However, the algorithm reframes the problem as one of choosing a power threshold \(T\ [kW]\) applied to the point of injection to the grid, the electric meter.
+The battery is then dispatched, within its technical limits, to hold the net load ($L-S$) below the threshold.
+When the algorithm is successful the different thresholds for each TOU period are met for an entire month.
+If the battery reaches a technical limit and net load exceeds a threshold, the simulation is not necessarily invalid but is not likely to minimize the retail electric cost to the site for that combination of solar and battery size.
+The peak shaving logic is described in Figure \ref{fig:peakshaving-flowchart}.
 
@@
   \centering
-  \includegraphics[width=10cm,height=\textheight]{./images/peak shaving flowchart.png}
-  \caption{Peak Shaving Flowchart. Net load is the
-  timeseries of load less solar. There is one threshold value for one for
-  each TOU period with a non-zero power price. For each timestep of the
-  simulation the net load is compared to the threshold of that TOU period,
-  and the battery is discharged if the net load is greater than the
-  threshold and charged if the net load is less than the threshold. If the
-  two are equal the battery does nothing. For timesteps with no price on
-  power the the battery does nothing.}
+  \includegraphics[width=7.5cm]{./images/peak shaving flowchart.png}
+  \caption{Peak Shaving Flowchart.
+Net load is the time series of load less solar.
+There is one threshold value for one for each TOU period with a non-zero power price.
+For each timestep of the simulation the net load is compared to the threshold of the current TOU period.
+The battery is discharged if the net load is greater than the threshold and charged if the net load is less than the threshold.
+If the two are equal or if there is no power price the battery does nothing.}
   \label{fig:peakshaving-flowchart}
@@
 
-The peak shaving algorithm describes stepping through time and
-dispatching the battery according to power thresholds, but not how the
-thresholds are chosen.
+The peak shaving algorithm describes stepping through time and dispatching the battery according to given power thresholds, which are chosen separately by an optimizer.
 
-\hypertarget{threshold-optimizer}{%
-  \subsection{Threshold Optimizer}\label{threshold-optimizer}}
+%\hypertarget{threshold-optimizer}{%
+\subsection{Threshold Optimizer}\label{threshold-optimizer}%}
 
-The optimal demand thresholds (one per TOU period) are determined by a
-custom gradient descent optimizer. The objective function \(C\)
-minimizes the retail energy cost of one month, which is the billing
-interval of this retail electric tariff. See Equation \ref{eq:optimization}. In practice the optimal
-thresholds are different for each month. The threshold for each TOU
-period \(T_k\) is not enforced to be non-negative, but in practice is
-always is because the cost function \(C_m()\) cannot evaluate to a
-negative value.
+The optimal demand thresholds (one per TOU period) are determined by a custom gradient descent optimizer based on the Newton-Raphson method \cite{Truong2019}.
+The objective function \(C\) minimizes the retail energy cost of one month, which is the billing interval of this retail electric tariff.
+See Equation \ref{eq:optimization}.
+In practice, the optimal thresholds are different for each month.
+The threshold for each TOU period \(T_k\) is not enforced to be non-negative, but in practice always is because the cost function \(C_m()\) cannot evaluate to a negative value.
 
@@
     SOC_{min}         & \le SOC \le SOC_{max}                                                        \\
-    \\
                       & \text{where:}                                                                \\
@@
 
-Beginning from an initial guess the Newton-Raphson gradient descent
-optimizer calculates the batch gradient and updates parameters based on
-a learning rate of 0.01. This continues until the stopping condition is
-met, minimum cost for a patience of 50 iterations. The Newton-Raphson
-gradient descent based optimization method is preferred over linear
-programming because it will minimize over a variety of cost functions
-without needing to reformulate the linear program.
+Beginning from an initial guess the Newton-Raphson gradient descent optimizer calculates the batch gradient and updates parameters based on a learning rate of 0.01 \cite{Truong2019}.
+This continues until the stopping condition is met, minimum cost for a patience of 50 iterations.
+The Newton-Raphson gradient descent-based optimization method is preferred over linear programming because it will minimize a variety of cost functions without needing to reformulate the linear program for each case.
 
-\hypertarget{simulations}{%
-  \subsection{Simulations}\label{simulations}}
+%\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}%}
 
-Simulations are run one month at a time for a given solar array
-orientation and battery capacity, according to the flowchart in Figure \ref{fig:simulation-flowchart}.
-The computational environment is Python 3.8 in Windows 10 64-bit, on
-an Intel i9 CPU with 64 GB of RAM.
+Simulations are run one month at a time for a given solar array orientation and battery capacity, according to the flowchart in Figure \ref{fig:simulation-flowchart}.
+The computational environment is Python 3.8 in Windows 10 64-bit, on an Intel i9 CPU with 64 GB of RAM.
 
@@
   \centering
-  \includegraphics[width=15cm,height=\textheight]{./images/simulation flowchart.png}
-  \caption{Simulation Flowchart. Given a solar orientation
-  and chosen battery capacity, the net load timeseries is calculated from
-  EV charging load and solar production. The threshold optimizer produces
-  one threshold value (kW) for each TOU period with non-zero power prices.
-  This returns both optimal thresholds and a minimum cost. Lastly a 1
-  month simulation of the battery charging and discharging is performed to
-  ensure no violations of the battery technical limits, and to produce the
-  battery power timeseries for evaluation.}
+  \includegraphics[width=12cm]{./images/simulation flowchart.png}
+  \caption{Simulation Flowchart.
+Given a solar orientation and chosen battery capacity, the net load time series is calculated from the EV charging load and solar production.
+The threshold optimizer produces one threshold value (kW) for each TOU period with non-zero power prices.
+This returns both optimal thresholds and a minimum cost.
+Finally, a 1-month simulation of the battery charging and discharging is performed to ensure no violations of the battery technical limits and to produce the battery power time series for evaluation.}
   \label{fig:simulation-flowchart}
@@
 
-\hypertarget{case-studies}{%
-  \section{Case Studies}\label{case-studies}}
+%\hypertarget{case-studies}{%
+\section{Case Studies}\label{case-studies}%}
 
-Five case studies are evaluated, each relating to the orientation of the
-solar array but not changing the overall \(kW_{DC}\) capacity. See Table \ref{tab:casestudies}. All case
-studies use the Prism 350 W bifacial solar PV modules and the Enphase
-IQH 380 W microinverters.
+Five case studies are evaluated, each relating to the orientation of the solar array but without changing the overall \(kW_{DC}\) capacity.
+See Table \ref{tab:casestudies}.
+All case studies use one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.
 
-The first and baseline case is a South-facing array of 368 modules,
-tilted at 20˚. This is intended to be a typical rooftop solar plant,
-especially in northern latitudes where lower sun angles and winter snow
-make the research question of vertical bifacial modules even more
-relevant. The daily clearsky solar power curve is the familiar rounded
-triangle centered at solar noon. The array is sized such that the total
-energy produced is equal to the total energy consumption of the EV
-charging station. This "net zero" sizing is not necessarily economically
-optimal, but rather it is a reasonable or typical size solar plant for
-the load.
+The base case is a typical South-facing array tilted at 20˚.
+This is intended to be a reasonable rooftop solar design, especially in northern latitudes where lower sun angles and winter snow make the research question of vertical bifacial modules even more relevant.
+The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon.
+The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station.
+This "net zero" sizing is not necessarily economically optimal, but rather it is a reasonable assumption for a solar capacity given the load.
 
-The remaining case studies each consider a portion of the array to be
-instead rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%.
-Especially the last case is relatively extreme from a design
-perspective, but should be investigated since it represents the maximum
-amount that the daily clear sky power curve can be pushed toward the
-morning and evening hours. This M-shaped power curve rather than the
-typical rounded-triangle power curve is the basis of any advantage
-vertical bifacial modules have regarding peak shaving. Micro inverters
-are used in the design so that the cases with part of the array facing
-west can be thought of a linear combination of the M-shaped and
-rounded-triangle power curves.
+The remaining four case studies each consider a percentage of the array permanently rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%.
+The last case is extreme from a design perspective but should be investigated since it represents a maximum amount that midday power can be time-shifted into the late afternoon and evening without tracking or storage.
+The resulting M-shaped daily power profile is the basis of the advantage vertical bifacial modules may have regarding peak shaving.
+Microinverters are used in the design so that the cases with a percentage of the array facing West can are indeed a linear combination of the M-shaped and rounded-triangle power profiles.
 
@@
   \centering
-  \caption{Case Studies. All modules are the Prism 350 W
-  bifacial. The base case is South-facing array tilted to 20°. In the
-  following four cases a percentage of the modules are oriented such that
-  the primary high power module surface faces West and the modules are
-  tilted to 90°: 25\%, 50\%, 75\%, and 100\%. As an increasing portion of
-  the array is oriented West and vertical the total energy and solar yield
-  decrease linearly as expected.}
+  \caption{Case Studies.
+All modules are the Prism 350 W bifacial.
+The base case is a South-facing array tilted to 20°.
+In the following four cases, a percentage of the modules are oriented such that the primary high power module surface faces West and the modules are tilted to 90°: 25\%, 50\%, 75\%, and 100\%.
+As an increasing portion of the array is oriented West and vertical the total energy and solar yield decrease linearly as expected.}
   \label{tab:casestudies}
@@
     \toprule
-  Case Study                                   & No.
-Modules                               & Orientation & Tilt & \vtop{\hbox{\strut Total Energy }\hbox{\strut {[}\(MWh\){]}}}         & \vtop{\hbox{\strut Solar Yield}\hbox{\strut  {[}\(\frac{kWh}{kW_{DC}}\){]}}}\\
+    Case Study                     & Modules & Orientation & Tilt & Total Energy ($MWh$)   & Solar Yield ($\frac{kWh}{kW_{DC}}$) \\
     \midrule
-  South 20°                                    & 368                                       & South       & 20°  & 151.7                    & 1180.8\\
-  25\% West 90°                                & \vtop{\hbox{\strut 276}\hbox{\strut 92}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 146.5                                     & 1140.4\\
-  50\% West 90°                                & \vtop{\hbox{\strut 184}\hbox{\strut 184}} & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 141.1                                     & 1098.2\\
-  75\% West 90°                                & \vtop{\hbox{\strut 92}\hbox{\strut 276}}  & \vtop{\hbox{\strut South}\hbox{\strut West}} & \vtop{\hbox{\strut 20°}\hbox{\strut 90°}}    & 136.1                                     & 1059.6\\
-  100\% West 90°                               & 368                                       & West        & 90°  & 131.0                    & 1019.3\\
+    South 20°                      & 368     & South       & 20°  & 151.7                  & 1180.8                              \\
+    \hline
+    \multirow{2}{*}{25\% West 90°} & 276     & South       & 20°  & \multirow{2}{*}{146.5} & \multirow{2}{*}{1140.4}             \\
+                                   & 92      & West        & 90°  &                        &                                     \\
+    \hline
+    \multirow{2}{*}{50\% West 90°} & 184     & South       & 20°  & \multirow{2}{*}{141.1} & \multirow{2}{*}{1098.2}             \\
+                                   & 184     & West        & 90°  &                        &                                     \\
+    \hline
+    \multirow{2}{*}{75\% West 90°} & 92      & South       & 20°  & \multirow{2}{*}{136.1} & \multirow{2}{*}{1059.6}             \\
+                                   & 276     & West        & 90°  &                        &                                     \\
+    \hline
+    100\% West 90°                 & 368     & West        & 90°  & 131.0                  & 1019.3                              \\
     \bottomrule
@@
 
-\hypertarget{results}{%
-  \section{Results}\label{results}}
+%\hypertarget{results}{%
+\section{Results}\label{results}%}
 
-The peak shaving methodology produces an optimally low retail electric
-cost for each of the 10 months of data, which are summed up for total
-electric cost versus the battery capacity sensitivity analysis. See Figure \ref{fig:total-cost}.
-The costs monotonically decrease with battery capacity as
-expected because every marginal unit of added battery energy capacity
-allows the algorithm to hold a power threshold for longer, and since
-each battery is rated for 1C at charging and discharging, the battery
-will also have more power capacity to achieve lower thresholds relative
-to the same size peak. The 100\% West 90° array achieves a lower total
-cost than the baseline South 20°. All three combination arrays achieve a
-lower cost for all battery capacities up to 200 kWh, with a maximum
-reduction of \$1422 (6.7\%) relative to the South 20° with a 100 kWh
-battery. The largest percentage improvement of 7.10\% (\$1208) occurs
-for the same array but 150 kWh battery. The absolute cost reduction is
-likely more important than the relative reduction since it would be
-treated directly as revenue in a cash flow analysis to determine the
-economic performance of a given battery.
+The peak shaving methodology produces an optimally low retail electric cost for each of the 10 months of data, which are summed up for total electric cost versus the battery capacity sensitivity analysis.
+See Figure \ref{fig:total-cost}.
+The costs monotonically decrease with battery capacity as expected because every marginal unit of added battery energy capacity allows the algorithm to hold a power threshold for longer, and since each battery is rated for 1C at charging and discharging, the battery will also have more power capacity to achieve lower thresholds relative to the same size peak.
+The 100\% West 90° array achieves a lower total cost than the baseline South 20°.
+All three combination arrays achieve a lower cost for all battery capacities up to 200 kWh, with a maximum reduction of \$1422 (6.7\%) relative to the South 20° with a 100 kWh battery.
+The largest percentage improvement of 7.10\% (\$1208) occurs for the same array but 150 kWh battery.
+The absolute cost reduction is likely more important than the relative reduction since it would be treated directly as revenue in a cash flow analysis to determine the economic performance of a given battery.
 
@@
   \centering
-  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost.png}
-  \includegraphics[width=7.5cm,height=\textheight]{./images/total cost reduction.png}
-  \caption{Total Cost. Total Retail Electric Cost is calculated for each
-  solar array case study and a sensitivity analysis is performed on
-  battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90°
-  arrays have similarly high total costs, whereas the three combination
-  arrays are somewhat grouped a few percent below. Above 150 kW the total
-  costs for each case diverge somewhat, with the South 20° base case
-  attaining the lowest cost for the 400 kWh battery and larger.
-  RIGHT: Reduction in Total Retail Cost is likely the most important metric for
-  evaluating the peak shaving efficacy, since it can be directly used as
-  revenue in a cash flow analysis to calculate economic performance. The
-  combination 50\% West 90° array with 100 kWh battery achieve the largest
-  cost reduction of \$1422 (6.7\%) over the 10 month data period. A
-  selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
+  \includegraphics[width=6.8cm]{./images/total cost.png}
+  \includegraphics[width=6.8cm]{./images/total cost reduction.png}
+  \caption{Total Retail Electric Cost.
+Costs are calculated for each case study and a sensitivity analysis is performed on battery capacity (kWh).
+Below 150 kW the South 20° and 100\% West 90° arrays have similarly high total costs, whereas the three combination arrays are somewhat grouped a few percent below.
+Above 150 kW the total costs for each case diverge somewhat, with the South 20° base case attaining the lowest cost for the 400 kWh battery and larger.
+RIGHT: Reduction in Total Retail Cost is likely the most important metric for evaluating the peak shaving efficacy since it can be directly used as revenue in a cash flow analysis to calculate economic performance.
+The combination of the 50\% West 90° array and 100 kWh battery achieved the largest cost reduction of \$1422 (6.7\%) over the 10-month data period.
+A selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
   \label{fig:total-cost}
@@
 
-The benefit of vertical bifacial modules can be seen when comparing the
-simulated battery charge and discharge time series data. Figure \ref{fig:peak-shaving} shows
-the same day (June 6) for both the base Solar 20° case and the 100\%
-West 90° case, which is presented here as a clearer graphical example
-than the better performing 50\% West 90° array. For both cases June 6 is
-the limiting day for the month, where the battery reaches a technical
-limit, in these cases zero SOC. This is likely due to a particularly
-large evening peak load event from approximately 17:30 to 21:30, with a
-maximum power of 56 kW and total energy of 201 kW. For these simulations
-the battery capacity is 125 kWh nominal and 112.5 kWh after losses, and
-as specified the battery will charge and discharge at a maximum of 1C or
-125 kW.
-
-In Figure \ref{fig:peak-shaving} the base case of South 20° overproduces in the middle hours
-of the day and solar is exported to the network starting around 12:00.
-During the peak load event the South 20° only produces 18.8 kWh whereas
-the 100\% West 90° array produces 104 kWh. In each case the battery
-charges to 100\% (125 kWh) before the evening peak load event. The
-result is that the evening net load peak in the 100\% West 90° case
-starts later and contains less energy, though it reaches the same
-maximum power. Due to this the battery in the 100\% West 90° case can
-hold the site load to a lower threshold in \(kW\), which is directly
-proportional to reducing the retail electric cost. During the expensive
-"Peak" TOU period of 14:00-21:00 the base South 20° case only achieves a
-low threshold of 13.0 kW, whereas the 100\% West 90° case holds a
-threshold of 3.1 kW in the same period, a 76\% improvement.
-
-The retail electric cost isn't defined for only one day out of a typical
-month, since the power portion of the cost is calculated on the monthly
-peak. However if June 6 was the only day of the month with non-zero load
-the total cost would be \$983 for the South 20° case and \$560 for the
-50\% West 90° case, which is a 43\% reduction.
+The benefit of vertical bifacial modules can be seen when comparing the simulated battery charge and discharge time series data.
+Figure \ref{fig:peak-shaving} shows the same day (June 6) for both the base Solar 20° case and the 100\% West 90° case, which is presented here as a clearer graphical example than the better-performing 50\% West 90° array.
+For both cases, June 6 is the limiting day for the month, when the battery reaches a technical limit, in these cases zero SOC.
+This is likely due to a particularly large evening peak load event from approximately 17:30 to 21:30, with a maximum power of 56 kW and total energy of 201 kW.
+For these simulations, the battery capacity is 125 kWh nominal and 112.5 kWh after losses, and as specified the battery will charge and discharge at a maximum of 1C or 125 kW.
+In Figure \ref{fig:peak-shaving} the base case of South 20° overproduces in the middle hours of the day and solar is exported to the network starting around 12:00.
+During the peak load event the South 20° only produces 18.8 kWh whereas the 100\% West 90° array produces 104 kWh.
+In each case the battery charges to 100\% (125 kWh) before the evening peak load event.
+The result is that the evening net load peak in the 100\% West 90° case starts later and contains less energy, though it reaches the same maximum power.
+Due to this the battery in the 100\% West 90° case can hold the site load to a lower threshold in \(kW\), which is directly proportional to reducing the retail electric cost.
+During the expensive "Peak" TOU period of 14:00-21:00, the base South 20° case only achieves a low threshold of 13.0 kW, whereas the 100\% West 90° case holds a threshold of 3.1 kW in the same period, a 76\% improvement.
+The retail electric cost isn't defined for only one day out of a typical month, since the power portion of the cost is calculated on the monthly peak.
+However if June 6 was the only day of the month with non-zero load the total cost would be \$983 for the South 20° case and \$560 for the 50\% West 90° case, which is a 43\% reduction.
 
@@
   \centering
-  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving south.png}
-  \includegraphics[width=7.5cm,height=\textheight]{./images/single day of peak shaving west.png}
-  \caption{Single Day of Peak Shaving. The stacked
-  dispatch plots use a convention where EV charging load (magenta) and
-  stationary battery charging additional load (blue) are the solid lines,
-  whereas any source of energy including the discharging battery are solid
-  areas. Since load must always be equal to the sum of supplied energy,
-  the areas always stack up to meet the load lines. The only exception is
-  when energy is exported back to the network, as is the case with
-  afternoon solar production here. The TOU power thresholds are
-  represented by the four dashed line segments, which begin and end based
-  on the begin and end of the TOU period, and overlap in time where the
-  TOU periods overlap. SOE is the dash-dot line referenced to the right
-  vertical axis. The base South 20° solar array overproduces midday
-  and exports energy to the grid, leaving more energy in the evening peak
-  that the stationary battery needs to serve.
-  RIGHT: The 100\% West 90°
-  case exports less solar to the grid, and has more late afternoon
-  production aligned with the evening load peak, allowing the peak shaving
-  algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than
-  the South 20° array.}
+  \includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
+  \includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
+  \caption{Single Day of Peak Shaving.
+The stacked dispatch plots use a convention where the EV charging load (magenta) and stationary battery charging additional load (blue) are the solid lines, whereas any source of energy including the discharging battery is a solid area.
+Since the load must always be equal to the sum of the supplied energy, the areas always stack up to meet the load lines.
+The only exception is when energy is exported back to the network, as is the case with afternoon solar production here.
+The TOU power thresholds are represented by the four dashed line segments, which begin and end based on the TOU periods and overlap in time where the TOU periods overlap.
+SOE is the dash-dot line referenced to the right vertical axis.
+LEFT: The base South 20° solar array overproduces midday and exports energy to the grid, leaving more energy in the evening peak that the stationary battery needs to serve.
+RIGHT: The 100\% West 90° case exports less solar to the grid, and has more late afternoon production aligned with the evening load peak, allowing the peak shaving algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than the South 20° array.}
   \label{fig:peak-shaving}
@@
 
-In Table \ref{tab:total-cost} are some of the data from Figure \ref{fig:total-cost}, though not shown for
-conciseness are the 75\% West 90° and the 25\% West 90° cases. The
-largest cost reduction is \$1422 for the 50\% West 90° case and 100 kWh
-battery. Note that the largest reduction in retail cost may not be the
-best solution economically, since the 25 kWh battery achieves 65\% of
-the cost reduction at 20\% of the battery energy capacity, which is
-roughly proportional to capital cost.
+In Table \ref{tab:total-cost} are some of the data from Figure \ref{fig:total-cost}, though not shown for conciseness are the 75\% West 90° and the 25\% West 90° cases.
+The largest cost reduction is \$1422 for the 50\% West 90° case and 100 kWh battery.
+Note that the largest reduction in retail cost may not be the best solution economically, since the 25 kWh battery achieves 65\% of the cost reduction at 20\% of the battery energy capacity, which is roughly proportional to capital cost.
 
@@
   \centering
-  \caption{Total Retail Electric Cost. Simulated total
-  retail electric cost for three of the case studies (some omitted for
-  conciseness) over the 10 months of available data and a given battery
-  capacity. Cost reduction is calculated with respect to the South 20°
-  base case. The best reduction in total retail cost is \$1422 for the
-  50\% West 90° case.}
+  \caption{Total Retail Electric Cost.
+Simulated total retail electric cost for three of the case studies (some omitted for conciseness) over the 10 months of available data and a given battery capacity.
+Cost reduction is calculated with respect to the South 20° base case.
+The best reduction in total retail cost is \$1422 for the 50\% West 90° case.}
   \label{tab:total-cost}
@@
     \toprule
-  Battery {[}kWh{]} & Cost South 20° {[}\${]}                & Cost 50\% West 90°
-  {[}\${]}          & Cost 100\% West 90° {[}\${]}           & Cost Reduction 50\% West 90°
-  {[}\${]}          & Cost Reduction 100\% West 90° {[}\${]} & Cost Reduction 50\%
-  West 90° {[}\%{]} & Cost Reduction 100\% West 90°
-  {[}\%{]}\\
+    Battery $[kWh]$ & Cost South 20° $[\$]$ & Cost 50\% West 90° $[\$]$ & Cost 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\$]$ & Cost Reduction 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\%]$ & Cost Reduction 100\% West 90° $[\%]$ \\
     \midrule
-  25                & 31314.0                                & 30391.0                      & 31730.0 & 923.0           & -416.0  & 3.0  & -1.3\\
-  50                & 27132.0                                & 25773.0                      & 27022.0 & 1359.0          & 110.0   & 5.0  & 0.4\\
-  75                & 23893.0                                & 22775.0                      & 23625.0 & 1118.0          & 268.0   & 4.7  & 1.1\\
-  100               & 21229.0                                & 19807.0                      & 20804.0 & \textbf{1422.0} & 425.0   & 6.7  & 2.0\\
-  125               & 18954.0                                & 17623.0                      & 18564.0 & 1331.0          & 390.0   & 7.0  & 2.1\\
-  150               & 17094.0                                & 15886.0                      & 17286.0 & 1208.0          & -192.0  & 7.1  & -1.1\\
-  200               & 14547.0                                & 13689.0                      & 15282.0 & 858.0           & -735.0  & 5.9  & -5.0\\
-  400               & 10730.0                                & 10969.0                      & 12131.0 & -239.0          & -1401.0 & -2.2 & -13.1\\
-  600               & 8859.0                                 & 9140.0                       & 10333.0 & -281.0          & -1474.0 & -3.2 & -16.6\\
+    25              & 31314                 & 30391                     & 31730                      & 923                                 & -416                                 & 3.0                                 & -1.3                                 \\
+    50              & 27132                 & 25773                     & 27022                      & 1359                                & 110                                  & 5.0                                 & 0.4                                  \\
+    75              & 23893                 & 22775                     & 23625                      & 1118                                & 268                                  & 4.7                                 & 1.1                                  \\
+    100             & 21229                 & 19807                     & 20804                      & \textbf{1422}                       & 425                                  & 6.7                                 & 2.0                                  \\
+    125             & 18954                 & 17623                     & 18564                      & 1331                                & 390                                  & 7.0                                 & 2.1                                  \\
+    150             & 17094                 & 15886                     & 17286                      & 1208                                & -192                                 & 7.1                                 & -1.1                                 \\
+    200             & 14547                 & 13689                     & 15282                      & 858                                 & -735                                 & 5.9                                 & -5.0                                 \\
+    400             & 10730                 & 10969                     & 12131                      & -239                                & -1401                                & -2.2                                & -13.1                                \\
+    600             & 8859                  & 9140                      & 10333                      & -281                                & -1474                                & -3.2                                & -16.6                                \\
     \bottomrule
@@
 
-A sensitivity analysis on the size of the solar array is performed with
-the results in Figure \ref{fig:solar-sensitivity} and Table \ref{tab:solar-sensitivity}. The total retail cost decreases monotonically
-with the larger solar capacities, and the cost reduction increases by a
-factor of 10 from the smallest to largest solar capacity. This result is
-expected since the larger capacities create a more pronounced difference
-between the late afternoon production of the two arrays which the peak
-shaving strategy translates into lower power thresholds for the cases
-with some portion of the array in the 100\% West 90° orientation.
-
-The 50\% West 90° case performs best in the first four solar capacities
-at which point, for the first time, the best performing case is one
-where the majority of the modules are in the 100\% West 90° orientation
-(75\%). However the difference of \$19 is not substantial. At larger
-solar capacities the cost reductions for each case study are both larger
-in magnitude and closer together, however the increase in cost reduction
-is clearly less than linear with solar capacity. This suggests a
-diminishing returns problem where, after a certain capacity of 100\%
-West 90° modules is met, the additional South 20° and 100\% West 90°
-modules are providing energy when the battery is already at 100\% SOC.
+A sensitivity analysis on the size of the solar array is performed with the results in Figure \ref{fig:solar-sensitivity} and Table \ref{tab:solar-sensitivity}.
+The total retail cost decreases monotonically with the larger solar capacities and the cost reduction increases by a factor of 10 from the smallest to largest solar capacity.
+This result is expected since the larger capacities create a more pronounced difference between the late afternoon production of the two arrays and the peak shaving strategy translates into lower power thresholds for the cases with some portion of the array in the 100\% West 90° orientation.
+The 50\% West 90° case performs best in the first four solar capacities at which point, for the first time, the best performing case is one where the majority of the modules are in the 100\% West 90° orientation (75\%).
+However, the difference of \$19 is not substantial.
+At larger solar capacities the cost reductions for each case study are both larger in magnitude and closer together, however, the increase in cost reduction is clearly less than linear with solar capacity.
+This suggests a diminishing returns problem where, after a certain capacity of 100\% West 90° modules is met, the additional South 20° and 100\% West 90° modules are providing energy when the battery is already at 100\% SOC.
 
@@
   \centering
-  \caption{Solar capacity sensitivity analysis based on reduction in total
-  retail cost relative to the base South 20° case. While the 50\% West 90°
-  array continues to achieve the highest cost reduction, the battery
-  capacity increases from 25 kWh to 125 kWh.}
+  \caption{Solar capacity sensitivity analysis based on reduction in total retail cost relative to the base South 20° case.
+While the 50\% West 90° array continues to achieve the highest cost reduction, the battery capacity increases from 25 kWh to 125 kWh.}
   \label{tab:solar-sensitivity}
@@
     Cost Reduction {[}\${]}          & Best Cost Reduction Battery Capacity
-    {[}kWh{]}\\
+    {[}kWh{]}                                                                            \\
     \midrule
-    64.4 (0.5x)                      & 50\% West 90°                        & 260  & 25\\
-    128.8 (1.0x)                     & 50\% West 90°                        & 1422 & 100\\
-    193.2 (1.5x)                     & 50\% West 90°                        & 2211 & 125\\
-    257.6 (2.0x)                     & 75\% West 90°                        & 2579 & 125\\
+    64.4 (0.5x)                      & 50\% West 90°                        & 260  & 25  \\
+    128.8 (1.0x)                     & 50\% West 90°                        & 1422 & 100 \\
+    193.2 (1.5x)                     & 50\% West 90°                        & 2211 & 125 \\
+    257.6 (2.0x)                     & 75\% West 90°                        & 2579 & 125 \\
     \bottomrule
@@
   \centering
-  \includegraphics[width=10cm,height=\textheight]{./images/total cost reduction solar sensitivity.png}
-  \caption{Solar Capacity Sensitivity. A sensitivity
-  analysis on solar capacity shows more available cost reduction, which
-  increases less than linearly with solar capacity.}
+  \includegraphics[width=10cm]{./images/total cost reduction solar sensitivity.png}
+  \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
   \label{fig:solar-sensitivity}
@@
 
-The battery capacities increase from 25 kWh up to 125 kWh across the
-solar sizes, which is an unexpected finding. Despite the extra capacity
-the 100\% West 90° case in Figure \ref{fig:weekly-load-solar} is still mostly unable to affect the
-peak power of the evening peaks, and thus both the base South 20° and
-combination array cases have a similar maximum power to shave. Indeed
-the average of the monthly peak net load values is 74.5 kW for the South
-20° 2.0x case and 74.7 kW for the 100\% West 90° 2.0x case. However,
-when increasing the solar to 2.0x, the energy under the net load time
-series during the 17:00 to 22:00 period decreases by only 164 kWh for
-the South 20° versus 886 kWh for the 100\% West 90° case. With more
-solar production in the evening peak the optimizer is able to pursue
-driving the "Peak" TOU period to zero, which has a large economic
-benefit. This is unachievable with the small battery capacities and is
-more difficult without the late afternoon solar production of the 100\%
-West 90° modules. Indeed a large 200 kWh battery is required to achieve
-the first 0 kW "Peak" period threshold in the South 20° case for all
-solar capacities. Rather, the 100\% West 90° case achieves a 0 kW Peak
-period threshold with the 150 kWh battery at 100\% solar capacity and
-with the 125 kWh battery at 2.0x solar capacity.
+The battery capacities increase from 25 kWh up to 125 kWh across the solar sizes, which is an unexpected finding.
+Despite the extra capacity the 100\% West 90° case in Figure \ref{fig:weekly-load-solar} is still mostly unable to affect the peak power of the evening peaks, and thus both the base South 20° and combination array cases have a similar maximum power to shave.
+Indeed the average of the monthly peak net load values is 74.5 kW for the South 20° 2.0x case and 74.7 kW for the 100\% West 90° 2.0x case.
+However, when increasing the solar to 2.0x, the energy under the net load time series during the 17:00 to 22:00 period decreases by only 164 kWh for the South 20° versus 886 kWh for the 100\% West 90° case.
+With more solar production in the evening peak, the optimizer is able to pursue driving the "Peak" TOU period to zero, which has a large economic benefit.
+This is unachievable with the small battery capacities and is more difficult without the late afternoon solar production of the 100\% West 90° modules.
+Indeed a large 200 kWh battery is required to achieve the first 0 kW "Peak" period threshold in the South 20° case for all solar capacities.
+Rather, the 100\% West 90° case achieves a 0 kW Peak period threshold with the 150 kWh battery at 100\% solar capacity and with the 125 kWh battery at 2.0x solar capacity.
 
@@
   \centering
-  \includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
-  \caption{Weekly Overlaid Load and Solar Power. The
-  entire 10 month time series of EV charging load, Solar 20°, and 100\%
-  West 90° are superimposed on a weekly basis, beginning on Monday. The
-  100\% West 90° case provides a clearer graphical example than the better
-  performing cases.}
+  \includegraphics[width=10cm]{./images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
+  \caption{Weekly Overlaid Load and Solar Power.
+The entire 10-month time series of EV charging load, Solar 20°, and 100\% West 90° are superimposed on a weekly basis, beginning on Monday.
+The 100\% West 90° case provides a clearer graphical example than the better-performing cases.}
   \label{fig:weekly-load-solar}
@@
 
-\hypertarget{conclusion}{%
-  \section{Conclusion}\label{conclusion}}
+%\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}%}
 
-An optimal electric load peak shaving strategy is simulated on 10 months
-of EV charging power time series. The peak shaving asset is a storage
-battery with a maximum charge and discharge rate of 1C and a constant
-discharge and charge efficiency of 90\%. A co-located solar array is
-included in the simulation to study the effects of typical South facing
-modules vs West facing vertical bifacial modules. Five different array
-orientations are presented as different case studies. In addition
-sensitivity analyses on battery energy capacity and solar array capacity
-provide information about the dynamics of the optimal peak shaving
-algorithm. The best performing case is designed with 50\% of the array
-South facing tilted at 20° and 50\% facing West at 90°, which achieved a
-reduction in the total retail cost of energy of \$1422 (6.7\%) with a 25
-kWh battery. The cost reduction is relative to the base case array with
-all the modules facing South and tilted at 20°. When solar is increased
-to twice the net-zero capacity the best performing case is 75\% West 90°
-with a cost reduction of \$2579 (16.1\%) with a 125 kWh battery. The
-best percentage cost reduction overall is 20.0\%. Both data and code are
-shared to the public on GitHub.
+An optimal electric load peak shaving strategy is simulated on 10 months of EV charging power time series.
+The peak shaving asset is a storage battery with a maximum charge and discharge rate of 1C and a constant discharge and charge efficiency of 90\%.
+A co-located solar array is included in the simulation to study the effects of typical South-facing modules vs.
+West-facing vertical bifacial modules.
+Five different array orientations are presented as different case studies.
+In addition, sensitivity analyses on battery energy capacity and solar array capacity provide information about the dynamics of the optimal peak shaving algorithm.
+The best-performing case is designed with 50\% of the array South facing tilted at 20° and 50\% facing West at 90°, which achieved a reduction in the total retail cost of energy of \$1422 (6.7\%) with a 25 kWh battery.
+The cost reduction is relative to the base case array with all the modules facing South and tilted at 20°.
+When solar is increased to twice the net-zero capacity the best-performing case is 75\% West 90° with a cost reduction of \$2579 (16.1\%) with a 125 kWh battery.
+The best percentage cost reduction overall is 20.0\%.
+Both data and code are shared with the public on GitHub.
 
-Peak shaving a monthly peak power typically, depending on the load
-factor, results in dispatching the battery until its technical limits to
-achieve a minimum monthly peak power. Because the load, or net load
-after solar is dispatched, is often not very homogeneous there will be
-one limiting day where the battery is bound by its technical limits and
-the peak power of the month is set. The presence of this limiting day in
-the month simulation of Figure \ref{fig:peak-shaving} does not guarantee a global minimum
-cost, but the lack of a limiting day would suggest the global minimum
-was not found. Intuitively the limiting day can be thought of as the
-most difficult day for the battery to achieve the given thresholds, and
-if the day was somehow easier for the battery (less and more uniform net
-load) the power thresholds could be lowered and therefore a lower retail
-electric cost achieved. Because the results of each month typically
-depend strongly on one limiting day, small changes in the load or solar
-magnitude or temporal relationship can have a large impact on the
-overall results. For this reason peak shaving simulations require
-particular care into data selection, cleaning, and acquiring an
-appropriate large amount of data such that the probability space of true
-possible limiting is well represented in the selected sample of limiting
-days.
+Peak shaving a monthly peak power typically, depending on the load factor, results in dispatching the battery until its technical limits to achieve a minimum monthly peak power.
+Because the load, or net load after solar is dispatched, is often not very homogeneous there will be one limiting day where the battery is bound by its technical limits and the peak power of the month is set.
+The presence of this limiting day in the month simulation of Figure \ref{fig:peak-shaving} does not guarantee a global minimum cost, but the lack of a limiting day would suggest the global minimum was not found.
+Intuitively the limiting day can be thought of as the most difficult day for the battery to achieve the given thresholds, and if the day was somehow easier for the battery (less and more uniform net load) the power thresholds could be lowered and therefore a lower retail electric cost achieved.
+Because the results of each month typically depend strongly on one limiting day, small changes in the load or the solar power magnitude or temporal relationship can have a large impact on the overall results.
+For this reason, peak shaving simulations require particular care in data selection, cleaning, and acquiring an appropriately large amount of data such that the probability space of true possible limiting is well represented in the selected sample of limited days.
 
-Confidence in the results presented is medium-high given the use of true
-EV charging measurements, a robust Newton-Raphson gradient descent
-optimizer with verified optimality, a true electric tariff appropriate
-for the load site and solar data location, and sensitivity analyses
-performed on two variables. Future work should include a more load data
-sets with more months of data, a more comprehensive battery model, an
-operational version of the peak shaving strategy, and testing at the
-Politecnico di Milano M2GLab microgrid.
+Confidence in the results presented is medium-high given the use of true EV charging measurements, a robust Newton-Raphson gradient descent optimizer with verified optimality, a true electric tariff appropriate for the load site and solar data location, and sensitivity analyses performed on two variables.
+Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy, and testing at the Politecnico di Milano M2GLab microgrid.
 
-\hypertarget{bibliography}{%
-  \section{Bibliography}\label{bibliography}}
+%\hypertarget{bibliography}{%
+\section{Bibliography}\label{bibliography}%}
+
+\bibliography{mendeley.bib}
 

### 2023-12-20 Paper/make.sh
cleanup

@@ -6,4 +6,6 @@ pdflatex -interaction=nonstopmode paper;
 bibtex paper;
 pdflatex -interaction=nonstopmode paper;
 pdflatex -interaction=nonstopmode paper;
-mv paper.pdf ../paper.pdf;
+rm paper.tex
+rm mendeley.bib
+mv paper.pdf ../paper.pdf

### 2023-12-20 bifacial_peak_shaving.py
small config changes, plots for the paper, readme

@@ -23,17 +23,10 @@ class dotdict(dict):
     __delattr__ = dict.__delitem__
 
 
-def parse_inputs(config_file: str) -> dotdict:
+def read_configs(config_file: str) -> dotdict:
     cfg = dotdict(json.load(open(config_file, 'r')))
     
     assert cfg.version == __version__, f'Version mismatch: {cfg.version} != {__version__}'
-
-    if len(sys.argv) > 1:
-        for i, arg in enumerate(sys.argv[1:]):
-            if arg == 'GPU':
-                cfg.gpu = True
-            if arg == '-s':
-                cfg.solar_scaler = float(sys.argv[i + 2])
 
     cfg.output_filename_stub = (
         f'Output/{config_file.split(".")[0]}_v{__version__}_s{cfg.solar_scaler:.1f}_'
@@ -901,8 +894,8 @@ def optimize_thresholds(
     if test == True:
         angles, batt_kwhs, year_months = angles[:1], batt_kwhs[:1], year_months[:1]
 
-    rough_search_max = 100
-    rough_step = 10
+    rough_search_max = cfg.grid_search_max
+    rough_step = cfg.grid_search_step
 
     tic = pd.Timestamp.now()
 
@@ -1271,9 +1264,9 @@ def optimize_thresholds(
 
 # %%
 if __name__ == '__main__':
-    cfg = parse_inputs('caltech_ev.json')
+    cfg = read_configs('caltech_ev.json')
     load = read_load_data(cfg)
     solar = read_and_scale_solar(cfg, load.index)
     net_load = calculate_net_load(load, solar)
     tou = TimeOfUseTariff(cfg.tou)
-    optimize_thresholds(cfg, net_load, tou )# , test=True)
+    optimize_thresholds(cfg, net_load, tou , test=True)

### 2023-12-20 data_processing.py

@@ -919,6 +919,53 @@ def plot_daily(ds:pd.Series,
         cols = [f'{h}:00' for h in range(24)]
         pd.DataFrame(ds2.values.reshape(n_days,dpd).T,columns=cols).boxplot()
 
+def plot_daily_2(ds,
+                title:str=None,
+                ylabel:str=None,
+                alpha:float=0.1,
+                colors:list=['indigo','gold','magenta']):
+    """ Plot a series with days super-imposed on each other. Index should be complete (no gaps)
+    for this to work right. Trims any remaining data after an integer number of weeks.
+
+    Args:
+        ds (pd.Series or list): pandas series(es) to plot
+        title (str, optional): title
+        ylabel (str, optional): what to call the y-axis        
+        interval_min (int): timeseries data interval
+        alpha (float, optional): transparency of plot lines, defaults to 0.1
+        colors (list, optional): list of colors strings
+    """
+    if not isinstance(ds,(list,tuple)):
+        ylabel = ds.name
+        ds = [ds]
+        
+    interval_min = int(ds[0].index.to_series().diff().mean().seconds/60)
+    dpd = int(24*60/interval_min) # data per day
+    plt.figure(figsize=(10,5))
+    t = [x/dpd for x in range(dpd)] # days    
+
+    for ds2,color in zip(ds,colors):
+        ds2 = ds2.copy(deep=True)
+        dt_start = ds2.index.min()
+        if dt_start != dt_start.floor('1d'):
+            dt_start = dt_start.floor('1d') + pd.Timedelta(hours=24)
+        ds2 = ds2[dt_start:]
+        n_days = len(ds2)//(dpd)
+        ds2 = ds2.iloc[:int(n_days*dpd)]
+        if len(ds)>1:
+            plt.plot(t,ds2.values.reshape(n_days,dpd).T,color,alpha=alpha)
+        else:
+            plt.plot(t,ds2.values.reshape(n_days,dpd).T,alpha=alpha)
+    plt.ylabel(ylabel)
+    #plt.xlabel('Days from Monday 0:00')
+    plt.title(title)
+    if len(ds)>1:
+        legend_items = []
+        for s,color in zip(ds,colors):
+            legend_items.append(mpatches.Patch(color=color, label=s.name))
+        plt.legend(handles=legend_items)
+    plt.show()
+
 
 def plot_weekly(ds,
                 title:str=None,
@@ -969,10 +1016,60 @@ def plot_weekly(ds,
         legend_items = []
[…]

### 2023-12-21 Paper/paper.tex
working on ema changes

@@
 % Full title of the paper (Capitalized)
-\Title{Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load at the Jet Propulsion Laboratory}
+\Title{Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load}
 
@@
 
-\abstract{Electric load peak shaving is a challenging and important problem considering the rapid growth of high-power electric vehicle charging sites.
-A co-located solar array provides locally produced energy, but an additional storage battery is required for reliable peak shaving.
-With occasional evening load peaks and an electric tariff with a 16:00-21:00 peak time of use period, vertical bifacial modules facing West have an economic advantage due to more of the production being shifted into the late afternoon and early evening.
+\abstract{Electric load peak shaving is a challenging, unsolved problem considering the rapid growth of high-power electric vehicle charging sites.
+This novel study models vertically-oriented and West-facing bifacial solar photovoltaic modules to increase late afternoon production, and simulates optimal peak shaving using a storage battery system.
+With occasional evening load peaks and an electric tariff with a 16:00-21:00 peak time of use period, this late afternoon production aligns both with load and with higher electric prices.
 Exploiting this, an optimal electric load peak shaving simulator dispatches a stationary battery to minimize the retail electric cost incurred by a real electric vehicle charging site over 10 months.
@@
 Lastly, some carbon reduction is possible by reducing the on/off transitions of peaker plants due to load peaks \cite{Uddin2018}.
-Broadly speaking there are two categories of peak shaving goals: technical and economic.
+
+Broadly speaking there are two categories of peak shaving goals. technical and economic. Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.
 
@@
     Valid times of day                     & All                                       & Limited (e.g. 16:00 to 21:00)     \\
-    Peak is reset every..                  & Never                                    & Month, year, day (typical)        \\
+    Peak is recalculated every..           & Continuous (never recalculated)           & Month (also: day, year)        \\
     \bottomrule
@@
 
+The following paper is organized into the following sections: \ref{methodology}, \ref{case-studies}, \ref{results}, \ref{conclusion}, and \ref{bibliography}.
+
+%\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}%}
+
 This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:peakshaving}.
@@
 The minimum time interval of the threshold is 1 hour.
+
+The methodology of this study is a set of offline simulations involving (a) EV charging power measurements, (b) modeled solar photovoltaic (PV) production power, and (b) AC-coupled battery dispatch, all behind a retail electric meter.
+These are represented in Figure \ref{fig:oneline}.
+In each simulation, the battery power is chosen such that the net load (true load less solar production, Equation \ref{eq:net-load}) is held below a given threshold, which is optimally chosen by a gradient descent optimizer.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=7.5cm]{./images/oneline.png}
+  \caption{Charging Site One Line Schematic.
+Simplified one-line schematic of the simulated EV charging station with true measured EV charging power, modeled on-site solar generation, and a modeled stationary battery for economic peak shaving.}
+  \label{fig:oneline}
+\end{figure}
 
@@
 \end{equation}
-
-%\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}%}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=7.5cm]{./images/oneline.png}
-  \caption{Charging Site One Line Schematic.
-Simplified one-line schematic of the simulated EV charging station with true measured EV charging power, modeled on-site solar generation, and a modeled stationary battery for economic peak shaving.}
-  \label{fig:oneline}
-\end{figure}
-
-The methodology of this study is a set of offline simulations involving (a) EV charging power measurements, (b) modeled solar photovoltaic (PV) production power, and (b) AC-coupled battery dispatch, all behind a retail electric meter.
-These are represented in Figure \ref{fig:oneline}.
-In each simulation, the battery power is chosen such that the net load (true load less solar production, Equation \ref{eq:net-load}) is held below a given threshold, which is optimally chosen by a gradient descent optimizer.
 
@@
 
-%\hypertarget{data}{%
+The main novelty of this work is studying the benefit of vertical bifacial PV modules in a peak shaving application, considering the sensitivity of the solution to percentage of modules facing West and tilted vertical, battery capacity, and overall solar capacity.
+
 \subsection{Data}\label{data}%}
 
-%\hypertarget{ev-charging-load}{%
-%\subsubsection{\texorpdfstring{EV Charging Load
-%    }{EV Charging Load }}\label{ev-charging-load}%}
 \subsubsection{{EV Charging Load }}\label{ev-charging-load}%}
 
-The measured EV charging power ("load") is from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}.
-Each charging session provides time series active power, averaged over a 10-second interval.
-In the cases when complete time series data is not available for a session, the charging power is assumed constant such that the total charging energy delivered is consistent with the primary data.
-The disaggregated session data is summed into a total site charging power time series, which is then averaged over 15-minute intervals.
+Measured EV charging power is used as the true load in the simulations and is never curtailed or rescheduled.
+For some sessions the EV charging time series was unavailable but the total charging energy was provided, in which case a constant charging power was assumed.
+The disaggregated session data is summed into a total site charging power time series, which is then downsampled to 15-minute intervals using the average value.
 Timestamp indices refer to the beginning of the 15-minute interval.
-The data period is from 2018-5-1 00:00 to 2019-2-28 23:45.
 
-%\hypertarget{solar-production}{%
 \subsubsection{Solar Production}\label{solar-production}%}
 
-The modeled PV production power begins life as Geostationary Operational Environmental Satellite (GOES) satellite solar irradiance data from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}.
-These data are specific to the years in question and are not from a typical meteorological year (TMY) set.
-See Table \ref{tab:data-summary}.
-Prism Solar 350 W bifacial solar module DC electrical power is estimated using the California Energy Commission Performance Model, a 6-parameter physical PV cell model.
-The full AC array power is estimated given loss assumptions and an inverter efficiency lookup table in the US National Renewable Energy Laboratory (NREL) System Advisor Model (SAM) database \cite{NREL2022} for the Enphase IQH 380 W microinverter.
-All these functions are implemented in SAM v2022.11.21 \cite{NREL2022}.
-Five different solar array orientations are modeled and simulated in different case studies, summarized in Table \ref{tab:casestudies}.
-Each orientation has the same number and type of bifacial modules.
-In the first orientation, all modules face South at a 20° tilt.
-In the remaining four orientations a percentage of the modules face all modules face West at 90° tilt: 25\%, 50\%, 75\%, and then 100\%.
-Tilt is defined as 90° minus the altitude angle of the normal vector of the primary active face of the module.
-No shading is considered.
-Of the two sides of the bi-facial module, the primary active face is oriented West since the afternoon load is generally subject to higher prices.
+Satellite irradiance data from the Geostationary Operational Environmental Satellite (GOES) is used as the primary data for modeling solar production and is obtained from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}.
+The data is serially complete and is available in 2 km by 2 km spatial resolution and 5 minute temporal resolution from 2018 onward.
+Multi-channel measurements from GOES are fed into the two-step Physical Solar Model (PSM) v3  \cite{Sengupta2018}.
+In the first step cloud and aerosol properties are collected and passed to the second step where the Fast All-sky Radiation Model for Solar Applications (FARMS), which estimates the radiation transfer on a tilted surface \cite{Xie2016}.
+Global Horizontal Irradiance (GHI) is computed directly from FARMS, then either REST2 or DISC models are used to compute Diffuse Normal Irradiance (DNI) if the environment is cloudy or clear, respectively \cite{Xie2018}.
+Authors indicate that computing surface irradiance in cloudy environments is complicated due to absorption and scattering within clouds, which may be a source of error relative to true measured solar PV production.
+Note these data are not organized into Typical meteorological Year (TMY) but are true satellite measurements for the same day and location as the EV charging load data.
 
-\begin{table}[!h]
-  \centering
-  \caption{Timeseries Data Summary.
-EV charging power is measured every 10 seconds for 10 months at the Jet Propulsion Laboratory, CA, USA.
-Solar irradiance from the GOES satellite is acquired for the same location.
-Solar PV array production is modeled from the satellite irradiance using a 6-parameter PV cell model and inverter efficiency lookup table.\label{tab:loadsectors}}
-  \label{tab:data-summary}
-  \begin{tabularx}{\linewidth}{XXXXX}
-    % { >{\hsize=.25\hsize\linewidth=\hsize}X
-    %   >{\hsize=.25\hsize\linewidth=\hsize}X
-    %   >{\hsize=.7\hsize\linewidth=\hsize}X
-    %   >{\hsize=.1\hsize\linewidth=\hsize}X
-    %   >{\hsize=.2\hsize\linewidth=\hsize}X
-    % }
-    %\begin{tabularx}{llllll}
-    \toprule
-    Description                     & Location                                & Type                                                                                                             & Interval                               & Source            \\
-    \midrule
-    EV charging power $[kW_{ac}]$    & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                & 10 sec (average downsampled to 15 min) & Caltech ACN (JPL) \cite{Lee2021}  \\
-    Solar irradiance $[W/m^2]$       & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                        & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}       \\
-    PV array production $[kW_{ac}]$ & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from GOES satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min                                 & SAM \cite{NREL2022} \\
-
-    \bottomrule
-  \end{tabularx}
-\end{table}
+Solar DC power is modeled using the California Energy Commission Performance Model, a 6-parameter physical PV cell model The parameters are those for the Prism Solar 350 W bifacial solar module.
+The full AC array power is estimated given loss assumptions and an inverter efficiency lookup table specific to the Enphase IQH 380 W microinverter.
+All these functions are implemented in the US National Renewable Energy Laboratory (NREL) System Advisor Model (SAM) v2022.11.21 \cite{NREL2022}.
 
@@
 
-%\hypertarget{electric-tariff}{%
-\subsection{Electric Tariff}\label{electric-tariff}%}
-
-A typical California electric tariff is applied at the point of the retail electric meter with several different TOU periods and prices.
-See Table \ref{tab:tariff}.
-For the chosen tariff each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both.
-The prices may also change between seasons and have long-term trends like any retail electric prices.
-
-\begin{table}[!h]
-  \centering
-  \caption{Retail Electric Tariff.
-An applicable electric tariff schedule with seven different TOU periods for energy and power prices, varying by hours of the day and season of the year.
-From California PG\&E.}
-  \label{tab:tariff}
-  \begin{tabularx}{\textwidth}{XXXXX}
-    \toprule
-    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
-    \midrule
-    All hours       & 0:00-0:00                          & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
-    Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
-    Off-peak spring & 0:00-9:00, 14:00-16:00, 21:00-0:00 & -\/-                            & -\/-                          & 0.132/$kWh$                    \\
-    Off-peak winter & 0:00-16:00, 21:00-0:00             & -\/-                            & 0.132/$kWh$                   & -\/-                           \\
-    Off-peak summer & 0:00-14:00, 23:00-0:00             & 0.132/$kWh$                     & -\/-                          & -\/-                           \\
-    Partial-peak    & 14:00-16:00, 21:00-23:00           & 6.81/$kW$, 0.159/$kWh$          & -\/-                          & -\/-                           \\
-    Peak            & 16:00-21:00                        & 32.90/$kW$, 0.196/$kWh$         & 2.22/$kW$, 0.172/$kWh$        & 2.22/$kW$, 0.172/$kWh$         \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
+\subsection{Electric Tariff}\label{electric-tariff}
 
@@
 \end{equation}
+
+Since the problem in question is economic peak shaving, the retail tariff is an important study parameter because it shapes the cost function and determines the benefit of solar production shifted into the late afternoon.
+With non-zero power prices a threshold-based peak shaving approach is appropriate because it mimics the power component of the true cost function, which concerns the maximum value and not every individual power value.
+Once the threshold is met, the optimizer knows that "power is free" and will charge the battery up the threshold without penalty to the cost function.
+Energy of course is paid by the integral of power and therefore any marginal consumption results in a marginal cost.
 
@@
 Simulations are run one month at a time for a given solar array orientation and battery capacity, according to the flowchart in Figure \ref{fig:simulation-flowchart}.
+The threshold optimizer produces one threshold value (kW) for each TOU period with non-zero power prices.
+This returns both optimal thresholds and a minimum cost.
+Finally, a 1-month simulation of the battery charging and discharging is performed to ensure no violations of the battery technical limits and to produce the battery power time series for evaluation.
 The computational environment is Python 3.8 in Windows 10 64-bit, on an Intel i9 CPU with 64 GB of RAM.
@@
   \centering
-  \includegraphics[width=12cm]{./images/simulation flowchart.png}
-  \caption{Simulation Flowchart.
-Given a solar orientation and chosen battery capacity, the net load time series is calculated from the EV charging load and solar production.
-The threshold optimizer produces one threshold value (kW) for each TOU period with non-zero power prices.
-This returns both optimal thresholds and a minimum cost.
-Finally, a 1-month simulation of the battery charging and discharging is performed to ensure no violations of the battery technical limits and to produce the battery power time series for evaluation.}
+  \includegraphics[width=\linewidth]{./images/simulation flowchart.png}
+  \caption{Simulation Flowchart. For each solar array case, battery capacity, and set of power thresholds, a single simulation is performed on the data 1 month at a time.}
   \label{fig:simulation-flowchart}
@@
 
-Five case studies are evaluated, each relating to the orientation of the solar array but without changing the overall \(kW_{DC}\) capacity.
-See Table \ref{tab:casestudies}.
-All case studies use one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.
+All case studies use the same electric load and tariff, and solar production changes for each case.
 
-The base case is a typical South-facing array tilted at 20˚.
-This is intended to be a reasonable rooftop solar design, especially in northern latitudes where lower sun angles and winter snow make the research question of vertical bifacial modules even more relevant.
+The load is measured EV charging power ("load") from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}.
+The time series data interval is 10 s, and the data period is from 2018-5-1 00:00 to 2019-2-28 23:45.
+See Table \ref{tab:data-summary}.
+
+\begin{table}[!h]
+  \centering
+  \caption{Timeseries Data Summary. The primary data sources are Caltech ACN EV charging power and GOES solar irradiance. Solar production is modeled from irradiance.}
+  \label{tab:data-summary}
+  \begin{tabularx}{\linewidth}{XXXXX}
+    \toprule
+    Description                     & Location                                & Type                                                                                                                  & Interval                               & Source                           \\
+    \midrule
+    EV charging power $[kW_{ac}]$   & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                     & 10 sec (average downsampled to 15 min) & Caltech ACN (site JPL) \cite{Lee2021} \\
+    Solar irradiance $[W/m^2]$      & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                             & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}  \\
+    PV array production $[kW_{ac}]$ & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from GOES satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min                                 & SAM \cite{NREL2022}              \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+The electric tariff is typical for California and consists of several different TOU periods, summarized in Table \ref{tab:tariff}.
+Each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both.
+Some prices change seasonally as well.
+
+\begin{table}[!h]
+  \centering
+  \caption{Retail Electric Tariff. An applicable electric tariff schedule with power and energy prices for several different TOU periods. From California PG\&E.}
+  \label{tab:tariff}
+  \begin{tabularx}{\textwidth}{XXXXX}
+    \toprule
+    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
+    \midrule
+    All hours       & 0:00-0:00                          & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
+    Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
+    Off-peak spring & 0:00-9:00, 14:00-16:00, 21:00-0:00 & -\/-                            & -\/-                          & 0.132/$kWh$                    \\
+    Off-peak winter & 0:00-16:00, 21:00-0:00             & -\/-                            & 0.132/$kWh$                   & -\/-                           \\
+    Off-peak summer & 0:00-14:00, 23:00-0:00             & 0.132/$kWh$                     & -\/-                          & -\/-                           \\
+    Partial-peak    & 14:00-16:00, 21:00-23:00           & 6.81/$kW$, 0.159/$kWh$          & -\/-                          & -\/-                           \\
+    Peak            & 16:00-21:00                        & 32.90/$kW$, 0.196/$kWh$         & 2.22/$kW$, 0.172/$kWh$        & 2.22/$kW$, 0.172/$kWh$         \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+Different solar array orientations are modeled and simulated in different case studies, summarized in Table \ref{tab:casestudies}. Each orientation has the same number and type of bifacial modules.
+
+The production time series for all cases is modeled in SAM from GOES satellite irradiance, with one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.
+For irradiance data see Table \ref{tab:data-summary}.
+
+The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}.
+This is intended to be a compromise rooftop solar design, not achieving the high tilt angles suggested in the literature such as in \cite{Baghoolizadeh2022}, but not as low tilt as common commercial solar arrays especially in northern latitudes where lower sun angles and winter snow make the research question of vertical bifacial modules even more relevant.
 The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon.
@@
   \centering
-  \includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
-  \includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
-  \caption{Single Day of Peak Shaving.
-The stacked dispatch plots use a convention where the EV charging load (magenta) and stationary battery charging additional load (blue) are the solid lines, whereas any source of energy including the discharging battery is a solid area.
-Since the load must always be equal to the sum of the supplied energy, the areas always stack up to meet the load lines.
-The only exception is when energy is exported back to the network, as is the case with afternoon solar production here.
-The TOU power thresholds are represented by the four dashed line segments, which begin and end based on the TOU periods and overlap in time where the TOU periods overlap.
-SOE is the dash-dot line referenced to the right vertical axis.
-LEFT: The base South 20° solar array overproduces midday and exports energy to the grid, leaving more energy in the evening peak that the stationary battery needs to serve.
+  \includegraphics[width=\textwidth]{./images/single day of peak shaving.png}
+  %\includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
+  %\includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
+  \caption{Single Day of Simulated Peak Shaving (Stacked Dispatch).
+Solid lines are load: EV charging load (magenta) and additional storage battery charging load (blue).
+Solid areas are energy sources and always sum up to a solid line unless solar production is greater than the load and is exported to the grid.
+The TOU power thresholds are represented by the dashed line segments.
+The dash-dot line is SOE, referenced to the right vertical axis.
+LEFT: The base South 20° solar array overproduces midday and exports energy to the grid.
 RIGHT: The 100\% West 90° case exports less solar to the grid, and has more late afternoon production aligned with the evening load peak, allowing the peak shaving algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than the South 20° array.}

### 2023-12-21 Paper/paper.tex
paper v2 sent to ema

@@
 Peak load management, or peak shaving, is the process of reducing the maximum load at a given point in an electrical network.
-This will necessarily increase the load factor,$P_{load,avg} P_{load,max}^{-1}$, even if load curtailment is the only method used.
+This will necessarily increase the load factor ($P_{load,avg} P_{load,max}^{-1}$) even if load curtailment is the only method used.
 Other methods include load scheduling, load shifting using energy storage, and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}.
@@
   \label{tab:econ-tech-peak-shaving}
-  \begin{tabularx}{\textwidth}{XXX}
+  \begin{tabularx}{\linewidth}{X X X}
     \toprule
@@
     Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
-    Time resolution                        & $\mu s$ to 10 s                           & 15-60 min or 1 h (typical)        \\
+    Time resolution                        & $\mu s$ to 10 s                           & 15-60 min (typical)        \\
     Valid times of day                     & All                                       & Limited (e.g. 16:00 to 21:00)     \\
@@
 Each may vary with time of day, day of week, and season of the year, which is often referred to as time of use (TOU) or peak pricing.
-The power cost ($p_p max(P_{load}\ [\$])$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes.
-Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to load reschedule, shift, or curtail, or dispatch DG.
+The power cost ($p_p P_{load,max}\ [\$]$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes.
+Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to reschedule, shift, or curtail load, or dispatch DG.
 
@@
 
-This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:peakshaving}.
+This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:net-load}.
 The load may not be curtailed or rescheduled, but solar DG naturally reduces the load and a storage battery is dispatched in a threshold-based peak shaving strategy.
@@
 \begin{equation}
-  \label{eq:peakshaving}
-  \begin{split}
-    P_{threshold,h} & \ge P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}                     \\
-                    & \text{where:}                                                                               \\
-    P               & \text{ is average power (threshold, load, solar, battery) }\ [kW]                           \\
-    0               & \le  P_{load,h}, P_{solar,h}, P_{batt,discharge,h}, P_{batt,discharge,h}, P_{batt,charge,h} \\
-    h               & \in \{0,1,2,...,23\}                                                                        \\
-  \end{split}
-\end{equation}
-
-\begin{equation}
   \label{eq:net-load}
   \begin{split}
+    & \text{Given:} \\
     NL & = L - S                                                               \\
+    SL & = NL - B_d + B_c                                 \\
+    & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t \\
        & \text{where:}                                                         \\
-       & NL(t) \text{ is the net load time series (non-negative)}\ [kW]        \\
-       & L(t) \text{ is the EV charging load time series (non-negative)}\ [kW] \\
-       & S(t) \text{ is the solar production time series}\ [kW]                \\
+       NL(t) & \in \mathbb{R} [kW] \text{ is the net load time series }         \\
+       L(t) & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series } \\
+       S(t) &\in \mathbb{R}^+ [kW] \text{ is the solar production time series }                \\
+       SL(t) & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter }         \\
+       B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }  \\
+       B_d(t) &\in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }   \\
+       T(t) &\in \mathbb{R}^+ [kW] \text{ is power threshold }   \\
   \end{split}
@@
 
-The main novelty of this work is studying the benefit of vertical bifacial PV modules in a peak shaving application, considering the sensitivity of the solution to percentage of modules facing West and tilted vertical, battery capacity, and overall solar capacity.
+The main novelty of this work is studying the benefit of vertical bifacial PV modules in a peak shaving application, considering the sensitivity of the solution to a percentage of modules facing West and tilted vertically, battery capacity, and overall solar capacity.
 
@@
 
-\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}
+%\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}
 
@@
 
-\subsubsection{Solar Production}\label{solar-production}%}
+%\subsubsection{Solar Production}\label{solar-production}%}
 
 Satellite irradiance data from the Geostationary Operational Environmental Satellite (GOES) is used as the primary data for modeling solar production and is obtained from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}.
-The data is serially complete and is available in 2 km by 2 km spatial resolution and 5 minute temporal resolution from 2018 onward.
+The data is serially complete and is available in 2 km by 2 km spatial resolution and 5-minute temporal resolution from 2018 onward.
 Multi-channel measurements from GOES are fed into the two-step Physical Solar Model (PSM) v3  \cite{Sengupta2018}.
@@
   \begin{split}
-    C_m & = \Sigma_k^K [ p_{p,k,m} max(NL^+_{k,m} + B_d - B_c + p_{e,k,m} \Sigma (NL^+_{k,m} + B_d(t) - B_c(t)) ] \\
+    C_m & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ] \\
         & \text{where:}                                                                                           \\
-        & NL^+(t) = NL(t),\ \forall\ NL(t)>0                                                                      \\
-        & B_c(t) \text{ is battery charging power time series(non-negative)}\ [kW]                                \\
-        & B_d(t) \text{ is battery discharging power time series(non-negative)}\ [kW]                             \\
-        & C_m \text{ is total retail electric cost for month}\ m\ [\$]                                            \\
-        & p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  [\$/kW]                       \\
-        & p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ [\$/kWh]                      \\
-        & K \text{ is number of TOU periods}
+        SL_{k,m}^+(t) &= SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$} \\
+        C_m & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                                             \\
+        p_{p,k,m} & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\                         \\
+        p_{e,k,m} & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\                       \\
+        K & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
   \end{split}
@@
 Since the problem in question is economic peak shaving, the retail tariff is an important study parameter because it shapes the cost function and determines the benefit of solar production shifted into the late afternoon.
-With non-zero power prices a threshold-based peak shaving approach is appropriate because it mimics the power component of the true cost function, which concerns the maximum value and not every individual power value.
+With non-zero power prices, a threshold-based peak shaving approach is appropriate because it mimics the power component of the true cost function, which concerns the maximum value and not every individual power value.
 Once the threshold is met, the optimizer knows that "power is free" and will charge the battery up the threshold without penalty to the cost function.
@@
   \caption{Peak Shaving Flowchart.
-Net load is the time series of load less solar.
+Net load is the time series of load with solar subtracted.
 There is one threshold value for one for each TOU period with a non-zero power price.
-For each timestep of the simulation the net load is compared to the threshold of the current TOU period.
+For each timestep of the simulation, the net load is compared to the threshold of the current TOU period.
 The battery is discharged if the net load is greater than the threshold and charged if the net load is less than the threshold.
@@
                       & \text{where:}                                                                \\
-    T_k               & \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
-    SOC(t)            & \text{ is battery state of charge timeseries}\ [\frac{kWh}{kWh}]             \\
+    T_k               & \in \mathbb{R}^+ [kW] \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
+    SOC(t)            & \in \mathbb{R}^+ \le 1 [kWh/kWh]  \text{ is battery state of charge timeseries}\             \\
   \end{split}
@@
 All case studies use the same electric load and tariff, and solar production changes for each case.
-
 The load is measured EV charging power ("load") from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}.
@@
 See Table \ref{tab:data-summary}.
+The electric tariff is typical for California and consists of several different TOU periods, summarized in Table \ref{tab:tariff}.
+Each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both.
+Some prices change seasonally as well.
+
+% The two largest power prices are 26.07 $\$/kW$ associated with the "All hours" period for all seasons and 32.90 $\$/kW$ associated with the "Peak (Summer)" period of 16:00-21:00, when the vertical West-facing bifacial modules will produce more energy in the late afternoon and evening than the South-facing modules.
+Since load curtailment is not considered, the battery will only have the option to shift energy from the expensive Peak period to other periods.
+Since all other periods have the 26.07 $\$/kW$ price, the marginal power cost reduction for shifting 1 kW of peak load out of the Peak period is only \$32.90.
 
@@
 
-The electric tariff is typical for California and consists of several different TOU periods, summarized in Table \ref{tab:tariff}.
-Each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both.
-Some prices change seasonally as well.
-
 \begin{table}[!h]
@@
     \midrule
-    All hours       & 0:00-0:00                          & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
+    All hours       & 0:00-0:00     3                     & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
     Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
@@
 
-Different solar array orientations are modeled and simulated in different case studies, summarized in Table \ref{tab:casestudies}. Each orientation has the same number and type of bifacial modules.
-
-The production time series for all cases is modeled in SAM from GOES satellite irradiance, with one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.
-For irradiance data see Table \ref{tab:data-summary}.
+The five case studies in Table \ref{tab:casestudies} consider different solar orientations, each with an increasing percentage of the modules oriented West and tilted vertically.
+The solar production time series for all cases is modeled in SAM from GOES satellite irradiance (Table \ref{tab:data-summary}), with one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.
 
 The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}.
-This is intended to be a compromise rooftop solar design, not achieving the high tilt angles suggested in the literature such as in \cite{Baghoolizadeh2022}, but not as low tilt as common commercial solar arrays especially in northern latitudes where lower sun angles and winter snow make the research question of vertical bifacial modules even more relevant.
-The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon.
+This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by in industry for the higher coverage ratio and lower wind load \cite{Cao2013}.
+The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon, such as in Figure \ref{fig:weekly-load-solar}.
 The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station.
@@
 
-The remaining four case studies each consider a percentage of the array permanently rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%.
-The last case is extreme from a design perspective but should be investigated since it represents a maximum amount that midday power can be time-shifted into the late afternoon and evening without tracking or storage.
-The resulting M-shaped daily power profile is the basis of the advantage vertical bifacial modules may have regarding peak shaving.
+The remaining four case studies in Table \ref{tab:casestudies} consider a percentage of the array permanently rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%.
+The last case is extreme from a design perspective but should be investigated since it represents a maximum amount that midday production can be time-shifted into the late afternoon and evening without tracking or storage.
+Graphically that shift results from the M-shaped daily power profile seen in Figure \ref{fig:weekly-load-solar}.
 Microinverters are used in the design so that the cases with a percentage of the array facing West can are indeed a linear combination of the M-shaped and rounded-triangle power profiles.
@@
 All modules are the Prism 350 W bifacial.
-The base case is a South-facing array tilted to 20°.
-In the following four cases, a percentage of the modules are oriented such that the primary high power module surface faces West and the modules are tilted to 90°: 25\%, 50\%, 75\%, and 100\%.
-As an increasing portion of the array is oriented West and vertical the total energy and solar yield decrease linearly as expected.}
+The base case array faces South and is tilted to 20°.
+The following four cases orient an increasing percentage of the modules West and tilt to 90°, with an expected linear decrease in total energy and solar yield.}
   \label{tab:casestudies}
@@
     \midrule
-    South 20°                      & 368     & South       & 20°  & 151.7                  & 1180.8                              \\
+    South 20° (base)               & 368     & South       & 20°  & 151.7                  & 1180.8                              \\
     \hline
@@
   \centering
-  \includegraphics[width=6.8cm]{./images/total cost.png}
-  \includegraphics[width=6.8cm]{./images/total cost reduction.png}
+  \includegraphics[width=0.49\textwidth]{./images/total cost.png}
+  \includegraphics[width=0.49\textwidth]{./images/total cost reduction.png}
   \caption{Total Retail Electric Cost.
@@
   %\includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
-  \caption{Single Day of Simulated Peak Shaving (Stacked Dispatch).
-Solid lines are load: EV charging load (magenta) and additional storage battery charging load (blue).
-Solid areas are energy sources and always sum up to a solid line unless solar production is greater than the load and is exported to the grid.
-The TOU power thresholds are represented by the dashed line segments.
+  \caption{Single Day of Simulated Peak Shaving.
+Solid lines are load from EV charging (magenta) and the additional amount of storage battery charging (blue).
+Solid areas are energy sources and always sum up to the load unless solar production is greater than the load and is exported to the grid.
+Dashed line segments are TOU power thresholds.
 The dash-dot line is SOE, referenced to the right vertical axis.
 LEFT: The base South 20° solar array overproduces midday and exports energy to the grid.
-RIGHT: The 100\% West 90° case exports less solar to the grid, and has more late afternoon production aligned with the evening load peak, allowing the peak shaving algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than the South 20° array.}
+RIGHT: The 100\% West 90° case shifts production to the late afternoon, reducing the evening load energy and thereby the Peak period threshold to 7.7 kW, 42\% lower than the South 20° array.}
   \label{fig:peak-shaving}
@@
   \centering
-  \includegraphics[width=10cm]{./images/total cost reduction solar sensitivity.png}
+  \includegraphics[width=12cm]{./images/total cost reduction solar sensitivity.png}
   \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
@@
   \centering
-  \includegraphics[width=10cm]{./images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
+  \includegraphics[width=\linewidth]{./images/weekly load solar.png}
   \caption{Weekly Overlaid Load and Solar Power.

### 2023-12-22 Paper/paper.tex
paper v3 with 25 sources

@@
 
+Even in cases where the electric load isn't growing, large solar photovoltaic (PV) arrays relative to the load will create relative peaks and dips in the net load seen by the network as clouds pass overhead.
+As the solar ramp-down rate due to clouds can be much faster than the ramp-up rate of many traditional thermal generators, grid operators will need to predict and anticipate these relative peaks.
+With an all-sky camera and machine vision algorithms, 15-minute nowcasting cloud identification may only reach 84.2\% accuracy \cite{Nespoli2022}.
+The remaining peaks will likely need to be managed by battery or other energy storage systems with extremely fast power ramp rates.
+
 %\hypertarget{peak-shaving}{%
@@
 Technical peak shaving refers to the case where a load must operate under a technical limitation such as a maximum power agreement or distribution transformer size.
-The load power must remain under the threshold at all times, otherwise, overcurrent protection may be activated or permanent damage to equipment such as lines or transformers.
+The load power must remain under the threshold at all times, otherwise, overcurrent protection may be activated or permanent damage to equipment such as lines or transformers \cite{Greco2023}.
 Even if the current is technically able to rise above the threshold, doing so may violate a contract regarding maximum load power.
 The important consideration is that the economic cost of exceeding the threshold is prohibitively high.
-The time resolution of technical peak shaving control may need to be as low as seconds or milliseconds \cite{Iannarelli2020}.
+The time resolution of technical peak shaving control may need to be as low as seconds or milliseconds.
 Although technical peak shaving is complicated by a large network, many assets, or a dynamic threshold, from the perspective of dispatching the assets to shave the peak the problem is relatively simple.
@@
 Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to reschedule, shift, or curtail load, or dispatch DG.
+
+In the literature, peak shaving strategies that dispatch a battery system often don't consider the retail cost of energy and rarely use an optimized threshold approach or vertical bifacial solar PV.
+In \cite{Reihani2016} authors forecast load and choose a state of charge (SOC) trajectory to manage load peaks.
+Solar power smoothing is applied in works such as \cite{Lavrova2012}.
+Linear programming optimization in \cite{Lee2014} reduces the on-peak load of residential EV charging by dispatching a battery.
+In \cite{Gazafroudi2018} a multi-agent system buys and sells energy in a local energy market for a residence with solar PV and a dispatchable vehicle-to-home EV battery.
+In \cite{Zheng2015} authors optimize peak shaving based on a rate tariff and a technical power threshold.
+Distributed solar PV  helps reduce net load and tracking arrays produce more energy in the late afternoon \cite{Faranda2011} but the increase may be reduced by common backtracking methods \cite{Dolara2012}.
+Vertical bifacial has been benchmarked in the literature and evaluated for new applications such as public highway solar installations \cite{Niccolai2022}.
+Vertical bifacial solar is coupled with a storage battery in \cite{Wallberg2022} and in \cite{Castellucci2022} with a rule-based peak shaving algorithm, reducing EV charging load peaks by 38.6\% and 79\%, respectively.
+However, the retail energy cost isn't estimated and a comparison is not made to understand the relative merit of vertical bifacial compared to south-facing modules.
 
@@
       L(t)   & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series }                   \\
-       S(t) &\in \mathbb{R}^+ [kW] \text{ is the solar production time series }                \\
+      S(t)   & \in \mathbb{R}^+ [kW] \text{ is the solar production time series }                   \\
       SL(t)  & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter } \\
       B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }              \\
-       B_d(t) &\in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }   \\
-       T(t) &\in \mathbb{R}^+ [kW] \text{ is power threshold }   \\
+      B_d(t) & \in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }                  \\
+      T(t)   & \in \mathbb{R}^+ [kW] \text{ is power threshold }                                    \\
     \end{split}
@@
                     & \text{where:}                                                                             \\
-        SL_{k,m}^+(t) &= SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$} \\
+      SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
       C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
@@
     \toprule
-    Battery $[kWh]$ & Cost South 20° $[\$]$ & Cost 50\% West 90° $[\$]$ & Cost 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\$]$ & Cost Reduction 100\% West 90° $[\$]$ & Cost Reduction 50\% West 90° $[\%]$ & Cost Reduction 100\% West 90° $[\%]$ \\
+    Battery $[kWh]$ & \multicolumn{3}{l}{Cost $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\%]$}                                                                   \\
+                    & South 20°                       & 50\% West 90°                             & 100\% West 90°                            & 50\% West 90° & 100\% West 90° & 50\% West 90° & 100\% West 90° \\
     \midrule

### 2024-01-02 Paper/paper.tex
various changes from Dec 26

@@
 
+% \pagecolor{black}
+% \color{white}
+
 \section{Introduction}\label{introduction}
@@
 
-Broadly speaking there are two categories of peak shaving goals. technical and economic. Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.
+Broadly speaking there are two categories of peak shaving with respect to the goal: technical and economic.
+Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.
 
@@
     \midrule
-    Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
+    Consequence of exceeding the power threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
     Time resolution                              & $\mu s$ to 10 s                           & 15-60 min (typical)               \\
@@
     \begin{split}
-             & \text{Given:}                                                                        \\
+      \exists B_d, B_c &\text{ s.t. } T \ge SL \forall t                                    \\      
+             & \text{given:}                                                                        \\
       NL     & = L - S                                                                              \\
       SL     & = NL - B_d + B_c                                                                     \\
-             & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t                                    \\
              & \text{where:}                                                                        \\
+      t      & \in \mathbb{R}^+ [h] \text{ is the time step }      \\             
       NL(t)  & \in \mathbb{R} [kW] \text{ is the net load time series }                             \\
@@
     \begin{split}
-      C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ]         \\
+      C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}\Delta t) ]         \\
                     & \text{where:}                                                                             \\
@@
       p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
-      K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
+      K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods} \\
+      \Delta t      & = 0.25 [h] \\
     \end{split}
@@
 The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}.
-This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by in industry for the higher coverage ratio and lower wind load \cite{Cao2013}.
+This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by industry for the higher coverage ratio and lower wind load \cite{Cao2013}.
 The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon, such as in Figure \ref{fig:weekly-load-solar}.
@@
   \centering
-  \includegraphics[width=12cm]{./images/total cost reduction solar sensitivity.png}
+  \includegraphics[width=0.8\linewidth]{./images/total cost reduction solar sensitivity.png}
   \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
@@
 Confidence in the results presented is medium-high given the use of true EV charging measurements, a robust Newton-Raphson gradient descent optimizer with verified optimality, a true electric tariff appropriate for the load site and solar data location, and sensitivity analyses performed on two variables.
-Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy, and testing at the Politecnico di Milano M2GLab microgrid.
+Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy based on a load forecast, and testing at the Politecnico di Milano M2GLab microgrid.
 

### 2024-01-02 data_processing.py

@@ -1341,7 +1341,8 @@ def plotly_stacked_4tou(_df:pd.DataFrame,
                    units_energy='kWh',
                    round_digits=1,
                    upsample_min=None,
-                   template='plotly_white'):
+                   template='plotly_white',
+                   save_path=None):
     """ Make plotly graph with some data stacked in area-fill style.
     
     Template options are :['ggplot2', 'seaborn', 'simple_white', 'plotly',
@@ -1558,6 +1559,9 @@ def plotly_stacked_4tou(_df:pd.DataFrame,
         fig.update_yaxes(range=(ylim[0], ylim[1]),secondary_y=False)
         
     fig.show()
+    
+    if save_path is not None:
+        fig.write_image(save_path)    
     
 #
 #

### 2024-01-03 Paper/paper.tex
working through sonia edits

@@
 %----------
-% journal
+%journal
 %----------
@@
 
-\usepackage[acronym]{glossaries}
-\usepackage{hhline}
-\usepackage{threeparttable} % to use table notes
-%\usepackage[draft]{changes} % usage: \deleted{old} \added{new} \replaced{new}{old} also \hl{} for highlighted text
+%\usepackage[acronym]{glossaries}
+%\usepackage{hhline}
+%\usepackage{threeparttable} % to use table notes
+\usepackage[draft]{changes} % usage: \deleted{old} \added{new} \replaced{new}{old} also \hl{} for highlighted text
 %\usepackage[final]{changes}
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Optimal Peak Shaving With Storage Battery and Bifacial Solar PV}
+\TitleCitation{Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load}
 
@@
 
-Even in cases where the electric load isn't growing, large solar photovoltaic (PV) arrays relative to the load will create relative peaks and dips in the net load seen by the network as clouds pass overhead.
+Even in cases where the electric load isn't growing, solar photovoltaic (PV) arrays that are large relative to the load will create relative peaks and valleys in the load seen by the network as clouds pass overhead.
 As the solar ramp-down rate due to clouds can be much faster than the ramp-up rate of many traditional thermal generators, grid operators will need to predict and anticipate these relative peaks.
 With an all-sky camera and machine vision algorithms, 15-minute nowcasting cloud identification may only reach 84.2\% accuracy \cite{Nespoli2022}.
-The remaining peaks will likely need to be managed by battery or other energy storage systems with extremely fast power ramp rates.
+The remaining peaks will likely need to be managed by other means.
 
@@
 This will necessarily increase the load factor ($P_{load,avg} P_{load,max}^{-1}$) even if load curtailment is the only method used.
-Other methods include load scheduling, load shifting using energy storage, and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}.
+Other methods include load scheduling, load shifting using energy storage (battery or otherwise), and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}.
 Peak shaving may include the concept of a peak load threshold which defines a maximum desired peak load during a period, typically on the order of hours.
@@
 \begin{table}
-  \centering
   \caption{Economic and Technical Peak Shaving Comparison}
@@
 
-  In the literature, peak shaving strategies that dispatch a battery system often don't consider the retail cost of energy and rarely use an optimized threshold approach or vertical bifacial solar PV.
+In the literature, peak shaving papers often don't consider the retail cost of energy and rarely utilize vertical bifacial solar PV or a threshold-based approach.
 In \cite{Reihani2016} authors forecast load and choose a state of charge (SOC) trajectory to manage load peaks.
-Solar power smoothing is applied in works such as \cite{Lavrova2012}.
 Linear programming optimization in \cite{Lee2014} reduces the on-peak load of residential EV charging by dispatching a battery.
@@
 In \cite{Zheng2015} authors optimize peak shaving based on a rate tariff and a technical power threshold.
-Distributed solar PV  helps reduce net load and tracking arrays produce more energy in the late afternoon \cite{Faranda2011} but the increase may be reduced by common backtracking methods \cite{Dolara2012}.
 Vertical bifacial has been benchmarked in the literature and evaluated for new applications such as public highway solar installations \cite{Niccolai2022}.
@@
 However, the retail energy cost isn't estimated and a comparison is not made to understand the relative merit of vertical bifacial compared to south-facing modules.
+Bifacial PV has been studied extensively in the literature, performing around 11\% better than comparable monofacial PV \cite{Ogliari2023}, .
 
-  The following paper is organized into the following sections: \ref{methodology}, \ref{case-studies}, \ref{results}, \ref{conclusion}, and \ref{bibliography}.
+\hl{Considering the above, this work builds on the existing body of knowledge by uniquely considering the benefit of bifacial solar in a peak shaving application and does so with an optimal threshold power approach.
+The objectives are a reproducible methodology to quantify that benefit and to explore the system dynamics to inform future investigations.
+The rest of the paper is organized as follows.}
 
-  %\hypertarget{methodology}{%
+\begin{enumerate}
+	\item Methodology: Formal definition of the cost function and how the minimization problem is solved
+	\item Case Studies: Five specific contexts of the problem are solved, each with a different solar array configuration
+	\item Results: The minimal costs are evaluated for each case and compared to the case base, including sensitivity analysis
+	\item Conclusions: The important findings are summarized and future directions explored
+\end{enumerate}
+
 \section{Methodology}\label{methodology}%}
@@
 \begin{table}[!h]
-  \centering
   \caption{Timeseries Data Summary. The primary data sources are Caltech ACN EV charging power and GOES solar irradiance. Solar production is modeled from irradiance.}
@@
 \begin{table}[!h]
-  \centering
   \caption{Retail Electric Tariff. An applicable electric tariff schedule with power and energy prices for several different TOU periods. From California PG\&E.}
@@
 \begin{table}
-  \centering
   \caption{Case Studies.
@@
 \begin{table}[!h]
-  \centering
   \caption{Total Retail Electric Cost.
@@
 \begin{table}[!h]
-  \centering
   \caption{Solar capacity sensitivity analysis based on reduction in total retail cost relative to the base South 20° case.
@@
 
-%\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}%}
+\section{Conclusions}\label{conclusions}
 
@@
 Confidence in the results presented is medium-high given the use of true EV charging measurements, a robust Newton-Raphson gradient descent optimizer with verified optimality, a true electric tariff appropriate for the load site and solar data location, and sensitivity analyses performed on two variables.
-Future work should include more load data sets with more months of data, a more comprehensive battery model, an operational peak shaving strategy based on a load forecast, and testing at the Politecnico di Milano M2GLab microgrid.
 
-%\hypertarget{bibliography}{%
-\section{Bibliography}\label{bibliography}%}
+Future work should expand the load case studies including multiple years and true solar production measurements, \hl{improve the battery state of charge estimation such as in} \cite{Eleftheriadis2023}, \hl{perform simulations using forecasting load such as in} \cite{Wood2023}, and test with hardware in the loop at the Politecnico di Milano MG2Lab microgrid.
+
+\section{Bibliography}\label{bibliography}
 

### 2024-01-09 Paper/paper.tex
few paper edits

@@
 
-Even in cases where the electric load isn't growing, solar photovoltaic (PV) arrays that are large relative to the load will create relative peaks and valleys in the load seen by the network as clouds pass overhead.
+Even in cases where the electric load isn't growing, solar Photovoltaic (PV) arrays that are large relative to the load will create relative peaks and valleys in the load seen by the network as clouds pass overhead.
 As the solar ramp-down rate due to clouds can be much faster than the ramp-up rate of many traditional thermal generators, grid operators will need to predict and anticipate these relative peaks.
@@
 This will necessarily increase the load factor ($P_{load,avg} P_{load,max}^{-1}$) even if load curtailment is the only method used.
-Other methods include load scheduling, load shifting using energy storage (battery or otherwise), and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}.
+Other methods include load scheduling, load shifting using energy storage (battery or otherwise), and reduction of the effective load with Distributed Generation (DG) \cite{Uddin2018}.
 Peak shaving may include the concept of a peak load threshold which defines a maximum desired peak load during a period, typically on the order of hours.
@@
 
-Broadly speaking there are two categories of peak shaving with respect to the goal: technical and economic.
+Broadly speaking there are two categories of peak shaving with respect to the goal, technical and economic.
 Some major differences between the two are summarized in Table \ref{tab:econ-tech-peak-shaving}.
@@
 Medium and large electric consumers often pay an energy price ($p_e\ [\$/kWh]$) and a power price ($p_p\ [\$/kW]$), also called a demand charge.
-Each may vary with time of day, day of week, and season of the year, which is often referred to as time of use (TOU) or peak pricing.
+Each may vary with time of day, day of week, and season of the year, which is often referred to as Time of Use (TOU) or peak pricing.
 The power cost ($p_p P_{load,max}\ [\$]$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes.
@@
 In the literature, peak shaving papers often don't consider the retail cost of energy and rarely utilize vertical bifacial solar PV or a threshold-based approach.
-In \cite{Reihani2016} authors forecast load and choose a state of charge (SOC) trajectory to manage load peaks.
+In \cite{Reihani2016} authors forecast load and choose a State of Charge (SOC) trajectory to manage load peaks.
 Linear programming optimization in \cite{Lee2014} reduces the on-peak load of residential EV charging by dispatching a battery.
@@
 For a given energy capacity (\(kWh\)) those limits are a charge or discharge rate of no more than 1C and a state of charge (SOC) between 0 and 100\%.
-State of energy (SOE) is the SOC multiplied by nominal energy capacity and is reported in plots because the units are more meaningful when comparing dispatch time series.
+State of Energy (SOE) is the SOC multiplied by nominal energy capacity and is reported in plots because the units are more meaningful when comparing dispatch time series.
 Half-round-trip charge and discharge efficiencies are constant at 90\%.
@@
 However, the algorithm reframes the problem as one of choosing a power threshold \(T\ [kW]\) applied to the point of injection to the grid, the electric meter.
-The battery is then dispatched, within its technical limits, to hold the net load ($L-S$) below the threshold.
+The battery is then dispatched, within its technical limits, to hold the net load below the threshold.
 When the algorithm is successful the different thresholds for each TOU period are met for an entire month.
@@
   \caption{Peak Shaving Flowchart.
-Net load is the time series of load with solar subtracted.
+Net Load (NL) is the time series of load with solar subtracted.
 There is one threshold value for one for each TOU period with a non-zero power price.
@@
     \midrule
-    EV charging power $[kW_{ac}]$   & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                     & 10 sec (average downsampled to 15 min) & Caltech ACN (site JPL) \cite{Lee2021} \\
-    Solar irradiance $[W/m^2]$      & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                             & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}       \\
-    PV array production $[kW_{ac}]$ & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from GOES satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min                                 & SAM \cite{NREL2022}                   \\
+    EV charging power $(kW_{ac})$   & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                     & 10 sec (average downsampled to 15 min) & Caltech ACN (site JPL) \cite{Lee2021} \\
+    Solar irradiance $(W/m^2)$      & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                             & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}       \\
+    PV array production $(kW_{ac})$ & GPS: 34.2013, -118.1721 (2x2 km square) & Modelled from GOES satellite irradiance, 368 Prism Solar 350 W bifacial modules, 368 Enphase IQH 380 W microinverters & 15 min                                 & SAM \cite{NREL2022}                   \\
     \bottomrule
@@
     \toprule
-    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
+    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $(\$)$ & Winter (Oct 1 -Feb 28) $(\$)$ & Spring (Mar 1 - May 30) $(\$)$ \\
     \midrule

### 2024-01-10 Paper/paper.tex
sonia feedback

@@
 
-Two new categories of load growth that will strain electric networks in most countries are electric heating and cooling, including traditional air conditioning and heat pumps, and Electric vehicle (EV) charging \cite{Bobmann2015}.
+Two new categories of load growth that will strain electric networks in most countries are electric heating and cooling, including traditional air conditioning and heat pumps, and Electric Vehicle (EV) charging \cite{Bobmann2015}.
 Heat pump and air conditioning load factor may be increased with architectural features such as insulation and thermal storage, but building efficiency retrofits often experience barriers such as regulation and financing mechanisms due to permitting and other challenges \cite{Bertone2016}.
@@
   \caption{Charging Site One Line Schematic.
-Simplified one-line schematic of the simulated EV charging station with true measured EV charging power, modeled on-site solar generation, and a modeled stationary battery for economic peak shaving.}
+Simplified one-line schematic of the EV charging station with true measured EV charging power, modeled on-site solar generation, and a modeled stationary battery for economic peak shaving.}
   \label{fig:oneline}
@@
             & \text{where:}                                                                        \\
-    t      & \in \mathbb{R}^+ [h] \text{ is the time step }      \\             
-    NL(t)  & \in \mathbb{R} [kW] \text{ is the net load time series }                             \\
-    L(t)   & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series }                   \\
-    S(t)   & \in \mathbb{R}^+ [kW] \text{ is the solar production time series }                   \\
-    SL(t)  & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter } \\
-    B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }              \\
-    B_d(t) & \in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }                  \\
-    T(t)   & \in \mathbb{R}^+ [kW] \text{ is power threshold }                                    \\
+    t      & \in \mathbb{R}^+ (h) \text{ is the time step }      \\             
+    NL(t)  & \in \mathbb{R} (kW) \text{ is the net load time series }                             \\
+    L(t)   & \in \mathbb{R}^+ (kW) \text{ is the EV charging load time series }                   \\
+    S(t)   & \in \mathbb{R}^+ (kW) \text{ is the solar production time series }                   \\
+    SL(t)  & \in \mathbb{R} (kW) \text{ is the site load time series seen at the electric meter } \\
+    B_c(t) & \in \mathbb{R}^+ (kW) \text{ is the battery charging load time series }              \\
+    B_d(t) & \in \mathbb{R}^+ (kW) \text{ is the battery discharge time series }                  \\
+    T(t)   & \in \mathbb{R}^+ (kW) \text{ is power threshold }                                    \\
   \end{split}
@@
 The state variable controlled by the algorithm is battery charge or discharge power.
-However, the algorithm reframes the problem as one of choosing a power threshold \(T\ [kW]\) applied to the point of injection to the grid, the electric meter.
+However, the algorithm reframes the problem as one of choosing a power threshold $T (kW)$ applied to the point of injection to the grid, the electric meter.
 The battery is then dispatched, within its technical limits, to hold the net load below the threshold.
@@
     \midrule
-    EV charging power $(kW_{ac})$   & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                     & 10 sec (average downsampled to 15 min) & Caltech ACN (site JPL) \cite{Lee2021} \\
+    EV charging power $(kW)$   & Jet Propulsion Lab, Pasadena CA, USA    & Measured and aggregated from multiple  EV chargers at single site                                                     & 10 sec (average downsampled to 15 min) & Caltech ACN (site JPL) \cite{Lee2021} \\
     Solar irradiance $(W/m^2)$      & GPS: 34.2013, -118.1721 (2x2 km square) & GOES satellite irradiance                                                                                             & 5 min                                  & NSRDB PSMv3 \cite{Sengupta2018}       \\
@@
     \toprule
-    Battery $[kWh]$ & \multicolumn{3}{l}{Cost $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\$]$} & \multicolumn{2}{l}{Cost Reduction $[\%]$}                                                                   \\
+    Battery $(kWh)$ & \multicolumn{3}{l}{Cost $(\$)$} & \multicolumn{2}{l}{Cost Reduction $(\$)$} & \multicolumn{2}{l}{Cost Reduction $(\%)$}                                                                   \\
                     & South 20°                       & 50\% West 90°                             & 100\% West 90°                            & 50\% West 90° & 100\% West 90° & 50\% West 90° & 100\% West 90° \\
@@
     \toprule
-    Solar Capacity {[}\(kW_{DC}\){]} & Best Case for Cost Reduction         & Best
-    Cost Reduction {[}\${]}          & Best Cost Reduction Battery Capacity
-    {[}kWh{]}                                                                            \\
+    Solar Capacity $(kW_{DC})$ & Best Case for Cost Reduction         & Best
+    Cost Reduction $(\$)$          & Best Cost Reduction Battery Capacity
+    $(\$)$                                                                            \\
     \midrule

### 2024-01-10 Paper/paper.tex
couple last sonia edits

@@
     SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
-    C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
-    p_{p,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
-    p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
+    C_m           & \in \mathbb{R}^+ (\$) \text{ is total retail electric cost for month}\ m\                 \\
+    p_{p,k,m}     & \in \mathbb{R}^+ (\$/kW) \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
+    p_{e,k,m}     & \in \mathbb{R}^+ (\$/kWh) \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
     K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods} \\
-    \Delta t      & = 0.25 [h] \\
+    \Delta t      & = 0.25 h \\
   \end{split}
@@
                       & \text{where:}                                                                                      \\
-    T_k               & \in \mathbb{R}^+ [kW] \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
-    SOC(t)            & \in \mathbb{R}^+ \le 1 [kWh/kWh]  \text{ is battery state of charge timeseries}\                   \\
+    T_k               & \in \mathbb{R}^+ (kW) \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
+    SOC(t)            & \in \mathbb{R}^+ \le 1 (kWh/kWh)  \text{ is battery state of charge timeseries}\                   \\
   \end{split}

### 2024-05-25 reopt_interface.py
good results for changing load forecast

@@ -1,0 +1,747 @@
+""" utils.py
+Generally useufl utility functions
+"""
+
+__version__ = 28
+
+import os
+import sys
+import shutil
+import math
+import yaml
+import json
+import numpy as np
+import pandas as pd
+import plotly.graph_objects as go
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+from plotly.subplots import make_subplots
+from src.post_and_poll import get_api_results
+
+class dotdict(dict):
+    __getattr__ = dict.__getitem__
+    __setattr__ = dict.__setitem__
+    __delattr__ = dict.__delitem__
+    
+def setup(config_file:str=None) -> dotdict:
+    
+    if config_file is not None:
+        #cfg = dotdict(json.load(open(config_file, 'r')))
+                
+        with open(config_file, 'r') as stream:
+            d=yaml.safe_load(stream)
+        cfg = dotdict(d)
+
+    
+    note = ''
+
+    if len(sys.argv) > 1:
+        for i, arg in enumerate(sys.argv[1:]):
+            if arg[:3] == '--f':
+                break
+            if arg[-4:] == 'json':
+                config_file = arg
+                cfg = dotdict(json.load(open(config_file, 'r')))
+            if arg == '-a':
+                cfg.solar_angles = [sys.argv[i + 2]]
+                note += f'a{sys.argv[i + 2]}_'
+            if arg == '-s':
+                cfg.solar_scaler = float(sys.argv[i + 2])
+                note += f's{cfg.solar_scaler:.1f}_'
+            if arg == 'TEST':
+                cfg.test = True
+                note += 'TEST_'             
+            if arg == '-n':
+                note += sys.argv[i + 2] + '_'     
+                cfg = dotdict(json.load(open(config_file, 'r')))
+                
+    cfg['filename'] = config_file           
+                
+    if cfg.dev:
+        note += 'DEV_'
+    if 'energy_price_sell_vector' in cfg.keys():
+        cfg.energy_price_sell_vector = pd.read_csv( cfg.energy_price_sell_vector,
+                                                    comment='#',
+                                                    index_col=0,
+                                                    parse_dates=True)
+    if cfg.note is not None:
+        note += cfg.note + '_'
+    else:
+        note = ''
+        
+    cfg.solar_file = cfg.data_dir + cfg.solar_file
[…]

### 2024-05-25 utils.py

@@ -1,451 +1,0 @@
-""" utils.py
-Generally useufl utility functions
-"""
-
-__version__ = 27
-
-import os
-import sys
-import shutil
-import math
-import yaml
-import json
-import pandas as pd
-import plotly.graph_objects as go
-import matplotlib.pyplot as plt
-import matplotlib.patches as mpatches
-from plotly.subplots import make_subplots
-
-class dotdict(dict):
-    __getattr__ = dict.__getitem__
-    __setattr__ = dict.__setitem__
-    __delattr__ = dict.__delitem__
-    
-def setup(config_file:str=None) -> dotdict:
-    
-    if config_file is not None:
-        #cfg = dotdict(json.load(open(config_file, 'r')))
-                
-        with open(config_file, 'r') as stream:
-            d=yaml.safe_load(stream)
-        cfg = dotdict(d)
-
-    
-    note = ''
-
-    if len(sys.argv) > 1:
-        for i, arg in enumerate(sys.argv[1:]):
-            if arg[:3] == '--f':
-                break
-            if arg[-4:] == 'json':
-                config_file = arg
-                cfg = dotdict(json.load(open(config_file, 'r')))
-            if arg == '-a':
-                cfg.solar_angles = [sys.argv[i + 2]]
-                note += f'a{sys.argv[i + 2]}_'
-            if arg == '-s':
-                cfg.solar_scaler = float(sys.argv[i + 2])
-                note += f's{cfg.solar_scaler:.1f}_'
-            if arg == 'TEST':
-                cfg.test = True
-                note += 'TEST_'             
-            if arg == '-n':
-                note += sys.argv[i + 2] + '_'     
-                cfg = dotdict(json.load(open(config_file, 'r')))
-                
-    cfg['filename'] = config_file           
-                
-    if cfg.dev:
-        note += 'DEV_'
-    if 'energy_price_sell_vector' in cfg.keys():
-        cfg.energy_price_sell_vector = pd.read_csv( cfg.energy_price_sell_vector,
-                                                    comment='#',
-                                                    index_col=0,
-                                                    parse_dates=True)
-    if cfg.note is not None:
-        note += cfg.note + '_'
-    else:
-        note = ''
-        
-    cfg.solar_file = cfg.data_dir + cfg.solar_file
-    cfg.load_file = cfg.data_dir + cfg.load_file
-    cfg.tariff_file = cfg.data_dir + cfg.tariff_file
-
[…]

### 2024-05-27 paper/paper.tex
good results, paper submitted

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System}

\author{\IEEEauthorblockN{Michael Wood}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
Email: michael.wood@polimi.it}
\and
\IEEEauthorblockN{Emanuele Ogliari}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
}
%\and
%\IEEEauthorblockN{Travis Simpkins}
%\IEEEauthorblockA{muGrid Analytics\\
%Littleton, CO, USA\\
%}
\and
\IEEEauthorblockN{Sonia Leva}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
}
}

\maketitle

\begin{abstract}
    Distributed renewable microgrids will be a crucial technology during the energy transition. Still, many vehicle-to-grid, demand response, and storage battery resources are not utilized fully to reduce consumer electric costs or support the larger grid as needed. This is due to poor integration between systems, but also because of a challenging forecasting problem that is required to be solved to achieve near-optimal unit commitment. Traditional forecasting methods and also modern machine learning algorithms are often trained and evaluated on mean squared error, which may not optimize for or predict the performance of a forecast in an optimal energy management system. This novel work constructs several different forecasts with different error distributions to study the impact on simulated optimal battery dispatch. The findings are that forecast error is most important during peak load periods and peak price periods, especially with consumer demand charges in place, and a zero-bias forecast is not necessarily advantageous. Recommendations are made to train and validate forecasting models to be effective with a downstream decision maker and not simply be optimized for a chosen error metric.
    \end{abstract}

\begin{IEEEkeywords}
forecasting, optimization, error analysis, energy management, battery dispatch
\end{IEEEkeywords}

\section{Introduction}

Energy optimization relies heavily on accurate forecasts of electric load, dynamic prices, and renewable energy generation. From large power systems to small building microgrids, peak load events or sudden drops in solar generation can be mitigated with control actions such as demand response or dispatchable generation such as energy storage. However, depending on the control action, the cost of inaction, and other variables such as market opening and closing times, forecasting is required to anticipate the changes in load or generation, for instance by having enough State of Charge (SOC) in energy storage. This forecast-response paradigm will be increasingly important as certain regions experience more extreme weather events, and renewable generation adds uncertainty to power systems and markets.

For these reasons, errors in forecasts can significantly impact the efficiency and reliability of large and small power systems. And since forecasts are always acted upon by some downstream decision maker, a discussion of the forecast errors must also consider the decision maker. Therefore this work examines recent literature forecasting error in power systems and then simulates several statistically diverse forecasts in an optimal Energy Management System (EMS) to evaluate the effect of forecast error on the system's performance.

\subsection{Electric Load Forecasting}

Electric load forecasting is likely the oldest forecast in power systems. Long-term forecasts on the order of years were required to plan new generation and transmission infrastructure. Medium-term forecasts on the order of months were soon required to manage seasonal variations in load, especially regarding fuel storage and generator maintenance periods. In more recent times, short-term forecasts on the order of hours to a few days aided transmission operators in managing congestion and informed market participants after the re-regulation of energy markets in the latter half of the 20th century. Most recently, nowcasting on the order of minutes has become important to manage building and campus generation and loads in real-time, which don't benefit from the spatial aggregation of loads, and thus have more load variability.

Techniques for load forecasting include traditional statistical methods such as SARIMA and modern machine learning approaches like neural networks and support vector machines. According to \cite{b1}, while statistical methods offer robustness, machine learning models provide higher accuracy due to their ability to capture nonlinear patterns in the data. However, load forecasting errors can arise from various exogenous sources, including sudden weather changes, economic activities, and random anomalies in consumer behavior. In \cite{b2} authors emphasize the importance of error decomposition, which involves breaking down the total forecast error into systematic and random components, to better understand and mitigate the sources of inaccuracies.

\subsection{Solar Power Forecasting}

Solar power forecasting involves predicting the amount of power generated by solar PV systems. The error of these forecasts is affected by factors such as cloud cover, different types and elevations of clouds, temperature, wind, and electrical or mechanical phenomena in the PV system such as cell degradation and soiling. Typically the input features to a solar prediction model include a numerical weather prediction forecast and terrestrial solar radiation estimated by a clear sky model, such as in \cite{b7}.

Researchers in \cite{b3} demonstrated that statistical methods like ARIMA can be adapted for solar forecasting but often fall short in capturing the high variability. Instead, machine learning techniques, including ensemble methods and hybrid physically informed neural networks have shown improved performance as in \cite{b4} and \cite{b7}. Solar forecasting errors are often characterized by their dependence on weather conditions more than autocorrelation, making integration with real-time weather data critical.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{flowchart.png}
    \caption{Simulation Flowchart. The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery. The output is the hourly battery dispatch vector, which is optimal for the given inputs. The assumption is the battery dispatch vector is now directly in operation. Calculating the site load from the true load and solar vectors allows to calculate the final cost of electricity.}
    \label{fig:flowchart}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{step1.png}
%     \caption{Simulation Step 1. The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery. The outputs are an hourly battery dispatch vector, which is optimal for the given inputs, and the associated costs that would be incurred if the load and solar vectors were true.}
%     \label{fig:step1}
% \end{figure}

\subsection{Error Analysis and Mitigation}

Error analysis involves assessing the forecast accuracy using metrics such as Mean Absolute Error (MAE), Mean Squared Error (MSE), and Mean Absolute Percentage Error (MAPE), which are most common in deterministic forecasts. In \cite{b5} authors suggest that incorporating probabilistic forecasts, which provide a range of possible outcomes instead of a single point prediction, can enhance the robustness of energy optimization strategies. Therefore probabilistic metrics are needed also, such as the Prediction Interval Coverage Probability (PICP) and Prediction Interval Normalized Average Width (PINAW). Error metrics are powerful tools for comparing forecast models and are often required for parameters fitting, and can even incorporate a benchmark prediction such as MASE, proposed in \cite{b9}.

Summary statistical metrics are helpful but often the shape of model residuals tells more of the story. A common problem is forecast bias, the tendency to have a non-zero mean for all forecasted values or just during certain intervals. This may especially occur for particular clusters of intervals with common physical phenomena, such as grid outages or extreme weather events. Extreme magnitude clusters can have a large impact on the EMS performance and be difficult to predict, especially if the events are quite rare \cite{b10}.

Mitigating forecasting errors involves both improving forecast models and developing strategies to manage uncertainty. Authors in \cite{b6} highlight the use of ensemble forecasting, where multiple models are used to generate a range of possible outcomes, thus providing a measure of the forecast uncertainty. In \cite{b6i} forecast uncertainty is mitigated with a strategy to minimize starting SOC of a hot sodium nickel battery. Additionally, reinforcement learning algorithms can continuously learn and adjust from new data can help reduce errors over time. Bayesian statistics and approaches that consider decision-making under risk may aid the final EMS or decision-maker when the uncertainty is measurable \cite{b11}

\begin{figure}
    \centering
    \includegraphics[width=.87\linewidth]{one-line.png}
    \caption{The simulated system is a medium-sized municipal building in Wisconsin, USA, with actual on-site solar (111 kWp). A hypothetical 100 kW 200 kWh storage battery is simulated. Load and solar forecasts are derived from true 1-minute interval data form the site. One case study includes the real retail electric tariff at this site.}
    \label{fig:one-line}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{step2.png}
%     \caption{Simulation Step 2. The output battery dispatch vector is used, along with the true load and solar vectors, to calculate the grid exchange vector. This is then used to calculate what the actual retail electric cost would be if the battery had been dispatched according to the output from ReOpt.}
%     \label{fig:step2}
% \end{figure}

This paper aims to construct several statistically different electric load forecasts and simulate the performance of an optimal EMS. The EMS controls a storage battery to minimize the retail cost of electricity to a medium-sized municipal building. By keeping the MAE constant among almost all the forecasts, the differing final retail costs illustrate how the shape of forecast errors impacts the downstream decision-maker in specific ways.

Our main contribution to the literature is the novel approach of manually adding disturbances to the perfect forecast to create and study specific error distributions. The methodology is robust due to the use of true measured 1-minute interval electric load, true measured 1-minute solar PV production, a thoroughly validated optimal EMS (ReOpt by the National Renewable Energy Lab) \cite{b12}, a true retail electric tariff, and two modified tariffs to study the effects of price structures on the results. Simulation code and data are published on GitHub for reproducibility.

The rest of the paper is organized as follows. In Methodology, the approach is described in detail. Next in Case Studies the specific problem and context are explained including data. Next Results are presented and discussed. And finally, Conclusions are drawn including the next steps for future work.

\section{Methodology}

\subsection{ReOpt Simulations}

The study approach is a series of computer simulations. Each simulation consists of two steps, graphically depicted in Figure \ref{fig:flowchart}. Each simulation is performed on one year of time series data, solving the unit commitment problem for a behind-the-meter electric load, co-located solar photovoltaic (PV), and a co-located storage battery. The only controllable asset is the storage battery, which can charge or discharge in any time step within its technical limits of maximum power and SOC. When the perfect load forecast (true measured load) and perfect solar forecast (true measured solar) are simulated, the result is the theoretical optimal battery dispatch for that year of load and solar measurements. The following are some useful definitions:

\begin{itemize}
    \item Load consumption: $ L(i) \in \mathbb{R}_0^+ [kW]$
    \item Solar production: $ S(i) \in \mathbb{R}_0^+ [kW]$ 
    \item Battery net, charge, and discharge: $ B(i) \in \mathbb{R}  = B_{d}^+ - B_{c}^+ [kW]$
    \item Net load: $ L_{net} = L - S$
    \item Site load: $ L_{site} = L - S - B$
    \item True measured value: $ y_t(i) \in \mathbb{R}_0^+ $
    \item Forecasted value: $ y_f(i) \in \mathbb{R}_0^+ $
    \item Error: $ \epsilon \in \mathbb{R} = y_f - y_t $
    \item Time series interval: $ \Delta t \in \mathbb{R}^+ [h] $
\end{itemize}

If instead an imperfect load and solar forecast are provided, the result is the optimal battery dispatch given those inputs. In other words, the simulation finds a global minimum of retail electric cost believing the forecasted load and solar to be true. The simulation chooses the optimal battery dispatch given the forecasts and other inputs provided. Assuming that the battery dispatch is not modified by the EMS in the presence of true measurements, the imperfect forecasts result in a retail electric cost which is necessarily greater than or equal to the theoretical optimal given perfect forecasting.

ReOpt is a techno-economic distributed energy resource (DER) optimization tool, which is both free and open source, and is well validated in the literature \cite{b13}. It performs optimal operation and sizing of DERs, although it is not intended as a real-time optimal EMS. However, to optimally size DERs it must solve the unit commitment problem for one to several dispatchable DERs, which is the central task of an EMS. It does so by constructing and solving a mixed-integer linear program (MILP) which minimizes the life cycle cost of new and existing DERs from the perspective of the behind-the-meter DER owner. Binary decision variables are required, for instance, to prevent the battery from charging and discharging in the same time step. Depending somewhat on the particular solver used, optimality of the solution is guaranteed for moderate complexity problem formulations due to a convex cost function and continuously differentiable, linear constraints \cite{b14}. The tool is written using the JuMP library in the Julia programming language, but in this work the tool is accessed via web API and Python script.

\subsection{Forecast Construction}

\begin{table}
    \centering
    \caption{Forecasts and Two Benchmarks}
    \label{tab:forecasts}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l}
        \hline
        Error Description       & Forecast                    & nMAE  \\
        \hline
        \hline
        Perfect                 & (1) \(y_{perfect} = y_t\)           & 0.0    \\
        \hline
        Constant                & (2a) \(y_f = y_t + k\)      & 0.1   \\
                                & (2b) \(y_f = y_t - k\)      & 0.1   \\
        \hline
        Linear                  & (3a) \(y_f = y_t + ky_t\)   & 0.1   \\
                                & (3b) \(y_f = y_t - ky_t\)   & 0.1   \\
        \hline
        Quadratic               & (4a) \(y_f = y_t + ky_t^2\) & 0.1   \\
                                & (4b) \(y_f = y_t - ky_t^2\) & 0.1   \\
        \hline
        Energy (Prices)         & (5a) \(y_f = y_t + kp_e\)   & 0.1   \\
                                & (5b) \(y_f = y_t - kp_e\)   & 0.1   \\
        \hline
        Demand (Prices)         & (6a) \(y_f = y_t + kp_d\)   & 0.1   \\
                                & (6b)\(y_f = y_t - kp_d\)    & 0.1   \\
        \hline
        Random (Gaussian)       & (7) \(y_f = y_t + X\)       & 0.1   \\
        \\
        \hline
        Persistence             & (8) \(y_{persist} = y_t(i-168)\)    & 0.033 \\
        \hline
        \hline
        Solar Only (no battery) & (9) No forecast             & n/a   \\
        \hline
    \end{tabular}
\end{table}

Rather than train various traditional and machine learning models to predict a time series, in this work the forecasts are manually manipulated starting from the true time series. In this way, the shape of the forecast error can be controlled and the effect on the EMS performance can be studied.

\begin{enumerate}
\item One hypothesis is that errors during peak load periods is especially harmful to the EMS performance, especially when the rate tariff contains a price on peak demand, also called a demand charge.

\item A second hypothesis is that forecast errors during high energy prices is detrimental to EMS performance, especially in the absence of a demand charge.
\end{enumerate}

These hypotheses can be tested by manipulating the original load vector, which is a perfect forecast, with a disturbance that is proportional to the load magnitude, the load magnitude squared, energy prices, or demand prices. Table \ref{tab:forecasts} summarizes these constructed forecasts in rows 2 through 7, which are referenced as forecasts 2a through 7. Additionally, there is forecast 8 which is a seasonal persistence forecast where the lag value equals one week.

\begin{align}
    \text{nMAE } [\frac{kW}{kW}] = \frac{1}{N} \sum_{i=1}^N \frac{|y_f - y_t|}{max(y_t)} \label{eq:nmae} 
\end{align}

A linear scaling factor $k$ is fit and applied separately to each forecast such that the normalized mean absolute error (nMAE) of each forecast is exactly 0.10. The value of 0.10 was determined experimentally to show a good spread of results: with an nMAE too low all the forecasts would be nearly perfect and indistinguishable, and vice versa.  The exceptions are that a perfect forecast will have an nMAE of zero, and a seasonal persistence forecast is possibly more interesting without other disturbances since it is already a good benchmark forecast \cite{b9}. By forcing all the manipulated forecasts to have the same nMAE, any differences in the EMS performance can be attributed to the shape of the error distribution and not just the magnitude.

Because there are no regression or machine learning models to fit we don't separate the data into train, validation, and test subsets.

\subsection{Performance Evaluation}

A premise of this work is that the utility of a distributed energy forecast should be determined by how much it reduces the final retail electric cost compared to a benchmark. The operational electric cost here is defined as what a customer would pay on a bill, less any fixed charges and particularly difficult-to-model components of the tariff, such as the rolling annual demand charge. Revenue from selling extra solar energy to the grid will be represented as a negative cost. Each timestep in $L_{site}$ belongs to exactly one time-of-use (TOU) period from 1 to $K$. Then each TOU period is assigned an energy buy price, demand charge price, and energy sell price. Equation \ref{eq:cost} calculates the dot product of in-TOU-period site loads and prices for each period, as well as the maximum monthly site load for each TOU period, which is multiplied by the TOU period's associated demand charge.

\begin{align}
    C_t,m           & = \sum_{k=1}^K [p_{d,k,m}  max(L^+_{site,k,m})  \notag \\
                & + p_{e,k,m} \sum (L^+_{site,k,m}\Delta t)  \notag \\
                & + p_{s,k,m} \sum (L^-_{site,k,m}\Delta t) ] \label{eq:cost} \\
                 \text{subject to:}&  \notag \\
                L_{site,k,m}^+(i) & \ge 0 \text{ and } L_{site,k,m}^-(i) \le 0\ \forall\ i \notag \\
%\end{align}
%\begin{align*}
                \text{where:}& \notag \\
                k & \text{: TOU period} \notag \\
                K & \text{: total TOU periods} \notag \\
                m & \text{: month} \notag \\
    C_t,m         & \in \mathbb{R}^+ [\$] \text{: total monthly retail electric cost} \notag \\
    p_{x,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ or } [\$/kWh] \text{: price for TOU } k \notag 
\end{align}

\begin{table}
    \centering
    \caption{Retail Electric Tariff}
    \label{tab:tariff}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l l l}
        \hline
        Period & Hours & Buy Prices & Buy Prices & Sell Price  \\
         &  & (Jun 1 - Sep 30) & (Oct 1 - May 31) & (all months) \\
        \hline
        \hline
        Off peak & 0:00-9:00,  & 0.056 \$/kW  & 0.056 \$/kW & 0.050 \$/kWh \\
                  & 21:00-0:00 &              &        &       \\
        \hline
        Peak     & 9:00-21:00   & 0.075 \$/kWh, & 0.070 \$/kWh, & 0.050 \$/kWh \\
                 &              & 13 \$/kW & 11 \$/kW & \\
        \hline
    \end{tabular}
\end{table}

\begin{table}
    \centering
    \caption{Case Studies}
    \label{tab:case-studies}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l}
        \hline
        & Tariff & Modifications \\
        \hline
        \hline
        1 & Retail Electric Tariff (Table \ref{tab:tariff}) & \\
        2 & Retail Electric Tariff (Table \ref{tab:tariff}) & All \$/kW prices = 0  \\
        3 & Retail Electric Tariff (Table \ref{tab:tariff}) & Sell price = CA NEM3.0 \\
        \hline
    \end{tabular}
\end{table}

The two benchmarks in Table \ref{tab:forecasts} are forecast 1, the perfect forecast, and forecast 9, a solar-only benchmark, which has no battery. With no controllable DERs there are no decision variables and no forecasting to be done. The perfect forecast is a theoretical optimal (lowest cost) that can't be exceeded. The solar-only case should represent a low benchmark: an optimal EMS controlling a battery should be able to perform better than if the battery wasn't there at all.

\begin{align}
    P(C_x) [\frac{kW}{kW}]= & (C_x - C_{x,perfect}) \over (C_{x,solar-only} - C_{x,perfect}) \label{eq:performance} \\
    \text{where:}& \notag \\
    x  \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag \\
    C_x =& \text{ cost of forecast to be evaluated [\$]}  \notag \\
    C_{x,perfect} =& \text{ cost of perfect forecast [\$]}  \notag \\
    C_{x,solar-only} =& \text{ cost of solar-only benchmark [\$]}  \notag 
\end{align}

These two book-end benchmarks suggest a normalized performance metric where a sample cost value $C$ lies in the range between the perfect forecast (1) and solar-only benchmark (9). This "performance" $P$ takes a value of 0 when the forecast cost is equal to the solar-only benchmark and a value of 1 when the forecast cost equals the theoretical optimal.

\section{Case Studies}

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{weekly.png}
    \caption{The municipal building load overlaid weekly shows the daily seasonality, weekly seasonality, and much larger peaks which we confirm elsewhere to be during the summer months, and likely due to increased occupancy and air conditioning. }
    \label{fig:data-weekly}
\end{figure}

Three case studies are presented in Table \ref{tab:case-studies}, each with a different tariff structure, but all with the same forecasts, benchmarks, and simulated DERs and site. The base tariff in Table \ref{tab:tariff} is only slightly simplified compared to the in vivo one, due to limitations of ReOpt in including a rolling annual demand charge on the cost function. This would only add marginally to the demand cost: 0.056 \$/kW compared to 11 and 13 \$/kW for Winter and Spring, respectively. In the second case study all demand charges are zeroed to see how errors affect the EMS in two very different objective functions: the first with a strong incentive to shave peaks, and the second not. In the third case study the demand charges are left intact but instead of a fixed solar sellback price of 0.05 \$/kWh, the California NEM3.0 price is used, which is a time-varying price based on the wholesale market price. Due to the famous duck curve and the need for late summer evening generation, prices in NEM3.0 can reach over 3 \$/kWh.

In all three case studies only the load forecast is manipulated according to Table \ref{tab:forecasts}. Since solar PV has zero marginal cost it is always dispatched except for technical reasons for curtailment. Therefore the unit commitment problem can be reframed not as dispatching solar PV and storage to minimize the cost of electricity incurred by the load, but instead as dispatching only storage to minimize the cost of net load ($load - solar$, where $load$ and $solar \in \mathbb{R}_0^+$). Now a positive error in the load forecast is identical to a negative error in the solar forecast, and vice versa. Furthermore, the combination of a load positive error and solar negative error can be reframed as the combined magnitude error in the net load.

The nMAE of all forecasts is equal to 0.10 except the perfect forecast which is 0, seasonal persistence which is 0.033, and the solar-only benchmark which has no forecast.

The site in the case studies is a medium-sized municipal building in northern Wisconsin, USA. The site has previously installed solar PV and energy meters which capture 1-minute time series data. For the purpose of this study the battery and EMS are just abstractions. The simulations should somewhat accurately model power flows and battery charge and discharge of the site in Figure \ref{fig:one-line}. Conductor and transformer losses are estimated as a constant loss percentage, and real power reduction due to fluctuating power factor is not considered.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{hist.png}
    \caption{Error Distributions of Several Forecasts. The Persist errors are well-behaved with a zero mean, as expected for a differences seasonal time series. The Linear and Quad errors have substantial skew and then long tails away from zero, and the positive and negative bias forecasts are mirror images, as expected. The Quad forecast errors appear to have still more skew.}
    \label{fig:hist}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{perf_lines.png}
    \caption{Case Study 1 Performance. The horizontal axis is sorted for increasing total cost performance $P_{Ct}$ which rises quickly above 0.5. Some forecasts have a negative performance on revenue despite a good total cost performance. This is the same data as in Table \ref{tab:performance}.}
    \label{fig:perf-lines}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{monthly_peaks_lines.png}
    \caption{Case Study 1 Monthly Peaks by Forecast. For this case study demand cost is a good predictor of total cost. Some forecasts such as 2a and 2b are able to chase down demand peaks for all months, whereas others are less able especially in August, September, and October. }
    \label{fig:monthly-peaks-lines}
\end{figure}

\section{Results}

The error distributions in Figure \ref{fig:hist} reflect the intention to have different positive and negative forecast biases and to cluster the errors near peak values. In the 2a and 2b Constant forecasts the errors take a single positive or negative value to the constant positive or negative offset (not shown in the image).

The final calculated costs for case study 1 in Figure \ref{fig:perf-lines} (sorted in order of increasing $P_{Ct}$) show that demand cost $P_{Cd}$ is a good predictor of total cost. In fact, the Pearson correlation between the two is 0.94, whereas energy cost $P_{Ce}$ only correlates at 0.74 and revenue $P_{Re}$ is uncorrelated at 0.14. The Constant and Energy price forecasts are likely the best performing because both have fairly evenly distributed errors throughout the day, whereas Linear, Demand, and Quadratic forecasts focus the errors around load peaks or high demand prices. An unexpected finding is that the worst-performing constructed forecast is the Random gaussian disturbance. Any single timestep can set the demand peak of the month. It appears that the randomly meandering forecast, coupled with a load time series that routinely rises to near its monthly peak (Figure \ref{fig:data-weekly}), spells disaster for an EMS charged with always shaving peaks.

This is confirmed by case study 3 results, also deriving from a demand charge tariff, in Table \ref{tab:performance} where the Random forecast is again the worst performer. Both case studies 1 and 3 have the same four forecasts near or above 0.90: 2b Constant-, 2a Constant+, 5b Energy-, and 3b Linear-. Both case studies also have similar low performers: Random, Persist, and 6b Demand-, and in both forests the positive and negative bias forecasts don't show obvious trends.

\begin{table}%[!ht]
    \centering
    \caption{Case Study 1: Forecasts vs Retail Electric Cost}
    \label{tab:cs1-cost}
    \begin{tabular}{l l l l l}
    \hline
        ~ & $C_e [\$]$ & $C_d [\$]$ & $R_e [\$]$ & $C_t [\$]$ \\ \hline \hline
        1 Perfect & 21867.31 & 4608.50 & 8.00 & 26467.81 \\ \hline
        2b Constant- & 22256.94 & 4608.56 & 42.00 & 26823.50 \\ \hline
        2a Constant+ & 22805.10 & 4608.56 & 574.00 & 26839.66 \\ \hline
        5a Energy+ & 22959.75 & 4608.56 & 639.00 & 26929.31 \\ \hline
        5b Energy- & 22449.53 & 4608.56 & 39.00 & 27019.09 \\ \hline
        3b Linear- & 22293.84 & 4851.25 & 36.00 & 27109.09 \\ \hline
        6a Demand+ & 23256.18 & 4608.56 & 725.00 & 27139.74 \\ \hline
        3a Linear+ & 22786.99 & 4984.94 & 561.00 & 27210.93 \\ \hline
        4a Quad+ & 22742.46 & 5425.37 & 530.00 & 27637.83 \\ \hline
        4b Quad- & 22433.59 & 5340.66 & 29.00 & 27745.25 \\ \hline
        8 Persist & 22140.92 & 6105.94 & 136.00 & 28110.86 \\ \hline
        6b Demand- & 23527.14 & 4646.89 & 37.00 & 28137.03 \\ \hline
        7 Random & 22635.07 & 6810.84 & 372.00 & 29073.91 \\ \hline
        9 Solar & 24546.16 & 7951.44 & 476.00 & 32021.60 \\ \hline
    \end{tabular}
\end{table}

In case study 2 there is no demand charge, and now the energy cost $P_{Ce}$ correlates with the total cost at 0.92. Without the demand charge a forecast with errors concentrated around high demand prices should be relatively error-free during the other times of the day, and indeed the two best performing models are 6a and 6b Demand+ and Demand-. Persist performs above 0.90 for the first time and Random is 0.79, suggesting both of those error shapes are harmful to peak shaving.

% \begin{table}[!ht]
%     \centering
%     \caption{Case Study 1: Forecasts vs Performance}
%     \label{tab:cs1-performance}    
%     \begin{tabular}{l l l l l}
%     \hline
%         ~ & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
%         9 Solar & 0 & 0 & 0 & 0 \\ \hline
%         7 Random & 0.71 & 0.34 & 0.22 & 0.53 \\ \hline
%         6b Demand- & 0.38 & 0.99 & 0.94 & 0.70 \\ \hline
%         8 Persist & 0.90 & 0.55 & 0.73 & 0.70 \\ \hline
%         4b Quad- & 0.79 & 0.78 & 0.95 & 0.77 \\ \hline
%         4a Quad+ & 0.67 & 0.76 & -0.12 & 0.79 \\ \hline
%         3a Linear+ & 0.66 & 0.89 & -0.18 & 0.87 \\ \hline
%         6a Demand+ & 0.48 & 1.00 & -0.53 & 0.88 \\ \hline
%         3b Linear- & 0.84 & 0.93 & 0.94 & 0.89 \\ \hline
%         5b Energy- & 0.78 & 1.00 & 0.93 & 0.90 \\ \hline
%         5a Energy+ & 0.59 & 1.00 & -0.35 & 0.92 \\ \hline
%         2a Constant+ & 0.65 & 1.00 & -0.21 & 0.93 \\ \hline
%         2b Constant- & 0.85 & 1.00 & 0.93 & 0.94 \\ \hline
%         1 Perfect & 1 & 1 & 1 & 1 \\ \hline
%     \end{tabular}
% \end{table}

% \begin{table}[!ht]
%     \centering
%     \caption{Case Study 2 (No Demand Price): Forecasts vs Performance}
%     \label{tab:cs2-performance}    
%     \begin{tabular}{l l l l}
%     \hline
%         ~ & $P_{Ce}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
%         9 Solar & 0 & 0 & 0 \\ \hline
%         5a Energy+ & 0.44 & -0.75 & 0.69 \\ \hline
%         5b Energy- & 0.78 & 0.93 & 0.75 \\ \hline
%         4b Quad- & 0.79 & 0.95 & 0.75 \\ \hline
%         2a Constant+ & 0.54 & -0.49 & 0.76 \\ \hline
%         3a Linear+ & 0.55 & -0.45 & 0.77 \\ \hline
%         4a Quad+ & 0.58 & -0.36 & 0.78 \\ \hline
%         7 Random & 0.67 & 0.10 & 0.79 \\ \hline
%         3b Linear- & 0.84 & 0.94 & 0.82 \\ \hline
%         2b Constant- & 0.85 & 0.93 & 0.84 \\ \hline
%         8 Persist & 0.87 & 0.65 & 0.92 \\ \hline
%         6b Demand- & 1.00 & 1.00 & 1.00 \\ \hline
%         6a Demand+ & 1.00 & 1.00 & 1.00 \\ \hline
%         1 Perfect & 1 & 1 & 1 \\ \hline
%     \end{tabular}
% \end{table}

% \begin{table}[!ht]
%     \centering
%     \caption{Case Study 3 (NEM3.0 Sell Price): Forecasts vs Performance}
%     \label{tab:cs3-performance}    
%     \begin{tabular}{l l l l l}
%     \hline
%     ~ & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
%         9 Solar & 0 & 0 & 0 & 0 \\ \hline
%         7 Random & 0.73 & 0.21 & 0.25 & 0.45 \\ \hline
%         8 Persist & 0.90 & 0.55 & 0.73 & 0.70 \\ \hline
%         6b Demand- & 0.37 & 0.99 & 0.89 & 0.70 \\ \hline
%         4a Quad+ & 0.67 & 0.76 & -0.12 & 0.75 \\ \hline
%         4b Quad- & 0.79 & 0.78 & 0.94 & 0.78 \\ \hline
%         6a Demand+ & 0.48 & 1.00 & -0.57 & 0.82 \\ \hline
%         3a Linear+ & 0.66 & 0.89 & -0.19 & 0.82 \\ \hline
%         5a Energy+ & 0.59 & 1.00 & -0.37 & 0.87 \\ \hline
%         3b Linear- & 0.84 & 0.93 & 0.93 & 0.89 \\ \hline
%         2a Constant+ & 0.65 & 1.00 & -0.23 & 0.89 \\ \hline
%         5b Energy- & 0.78 & 1.00 & 0.92 & 0.90 \\ \hline
%         2b Constant- & 0.85 & 1.00 & 0.92 & 0.94 \\ \hline
%         1 Perfect & 1 & 1 & 1 & 1 \\ \hline
%     \end{tabular}
% \end{table}

%%%%%%%%%%%%%%%%%%%

\begin{table}%[!ht]
    \centering
    \caption{Case Studies 1-3: Forecasts vs Performance}
    \label{tab:performance}
    \setlength{\tabcolsep}{1pt}
    \begin{tabular}{l|l l l l|l l l| l l l l}
        \hline
        ~            & CS1      &          &          &               & CS2      &          &               & CS3      &          &          &          \\ \hline 
        ~            & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline 
        9 Solar      & 0        & 0        & 0        & 0             & 0        & 0        & 0             & 0        & 0        & 0        & 0        \\ \hline  
        8 Persist    & 0.90     & 0.55     & 0.73     & 0.70          & 0.87     & 0.65     & \textbf{0.92} & 0.90     & 0.55     & 0.73     & 0.70     \\ \hline
        7 Random     & 0.71     & 0.34     & 0.22     & 0.53          & 0.67     & 0.10     & 0.79          & 0.73     & 0.21     & 0.25     & 0.45     \\ \hline
        6b Demand-   & 0.38     & 0.99     & 0.94     & 0.70          & 1.00     & 1.00     & \textbf{1.00} & 0.37     & 0.99     & 0.89     & 0.70     \\ \hline
        6a Demand+   & 0.48     & 1.00     & -0.53    & 0.88          & 1.00     & 1.00     & \textbf{1.00} & 0.48     & 1.00     & -0.57    & 0.82     \\ \hline
        5b Energy-   & 0.78     & 1.00     & 0.93     & 0.90          & 0.78     & 0.93     & 0.75          & 0.78     & 1.00     & 0.92     & \textbf{0.90}     \\ \hline
        5a Energy+   & 0.59     & 1.00     & -0.35    & \textbf{0.92} & 0.44     & -0.75    & 0.69          & 0.59     & 1.00     & -0.37    & 0.87     \\ \hline
        4b Quad-     & 0.79     & 0.78     & 0.95     & 0.77          & 0.79     & 0.95     & 0.75          & 0.79     & 0.78     & 0.94     & 0.78     \\ \hline
        4a Quad+     & 0.67     & 0.76     & -0.12    & 0.79          & 0.58     & -0.36    & 0.78          & 0.67     & 0.76     & -0.12    & 0.75     \\ \hline
        3b Linear-   & 0.84     & 0.93     & 0.94     & 0.89          & 0.84     & 0.94     & 0.82          & 0.84     & 0.93     & 0.93     & \textbf{0.89}     \\ \hline
        3a Linear+   & 0.66     & 0.89     & -0.18    & 0.87          & 0.55     & -0.45    & 0.77          & 0.66     & 0.89     & -0.19    & 0.82     \\ \hline
        2b Constant- & 0.85     & 1.00     & 0.93     & \textbf{0.94} & 0.85     & 0.93     & 0.84          & 0.85     & 1.00     & 0.92     & \textbf{0.94}     \\ \hline
        2a Constant+ & 0.65     & 1.00     & -0.21    & \textbf{0.93} & 0.54     & -0.49    & 0.76          & 0.65     & 1.00     & -0.23    & \textbf{0.89}     \\ \hline
        1 Perfect    & 1        & 1        & 1        & 1             & 1        & 1        & 1             & 1        & 1        & 1        & 1        \\ \hline
    \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{hist_linscaledup.png}
%     \caption{Forecast 3+: Error $\alpha$ Load (positive). The errors have heavy skew to the low end and a long tail to the high end. This effect is mirrored for the forecast 3- for negative bias, and more pronounced for both forecast 4+ and 4- with the quadratic relationship.}
%     \label{fig:hist-linscaledup}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{hist_persist.png}
%     \caption{Forecast 8: Seasonal Persistence. Distribution of errors for the 7day persistence forecast, the only once with a lower nMAE than 0.10 (0.033).The errors are essentially the difference of the time series so we expect to see symmetry around a mean of zero.}
%     \label{fig:hist-persist}
% \end{figure}

\section{Conclusions}

Analyzing and mitigating errors in electric load and solar forecasts are crucial for optimizing energy systems because of the decision maker downstream of the forecast. The initial investigation has discovered that several different load forecasts with identical nMAE can have extremely different performances in a simulated EMS. Advances in machine learning, synthetic data, and transfer learning offers promising improvements in forecast accuracy. However ongoing research is essential to develop the right forecasts and not generic ones, especially regarding peak shaving and peak load forecasting.

Future work will include combined true error distributions from trained forecast models, and will combine solar and load forecast errors explicitly to discern if the errors often have similar properties or not. Future forecasting efforts will use tools like custom loss functions, Kalman filtering, and decision making under risk approaches to tune the forecast in the direction that is optimal for the EMS to reduce costs. Finally, the cost of carbon will be considered in a multi-objective optimization in addition to economic cost.

\begin{thebibliography}{00}

\bibitem{b1} Taylor, J. W., & McSharry, P. E. (2007). Short-term load forecasting methods: An evaluation based on European data. IEEE Transactions on Power Systems, 22(4), 2213-2219.

\bibitem{b2} Hong, T., Pinson, P., & Fan, S. (2016). Global energy forecasting competition 2012 and beyond. International Journal of Forecasting, 32(3), 896-913.

\bibitem{b3} Bacher, P., Madsen, H., & Nielsen, H. A. (2009). Online short-term solar power forecasting. Solar Energy, 83(10), 1772-1783.

\bibitem{b4} Yang, D., Kleissl, J., Gueymard, C. A., Pedro, H. T. C., & Coimbra, C. F. M. (2018). History and trends in solar irradiance and PV power forecasting: A preliminary assessment and review using text mining. Solar Energy, 168, 60-101.

\bibitem{b5} Zhang, G., Wang, J., & Zhang, W. (2018). Review on probabilistic forecasting of wind power generation. Renewable and Sustainable Energy Reviews, 32(3), 858-872.

\bibitem{b6} Pinson, P., & Kariniotakis, G. (2010). Conditional prediction intervals of wind power generation. IEEE Transactions on Power Systems, 25(4), 1845-1856.

\bibitem{b6i} Grillo, S., Marinelli, M., Massucco, S., & Silvestro, F. (2012). Optimal management strategy of a battery-based storage system to improve renewable energy integration in distribution networks. IEEE Transactions on Smart Grid, 3(2), 950-958.

\bibitem{b7} Costa, A., Crespo, A., Navarro, J., Lizcano, G., Madsen, H., & Feitosa, E. (2008). A review on the young history of the wind power short-term prediction. Renewable and Sustainable Energy Reviews, 12(6), 1725-1744.

\bibitem{b8} Leva, S., Dolara, A., Grimaccia, F., Mussetta, M., & Ogliari, E. (2017). Analysis and validation of 24 hours ahead neural network forecasting of photovoltaic output power. Mathematics and computers in simulation, 131, 88-100.

\bibitem{b9} Hyndman, R. J. (2006). Another look at forecast-accuracy metrics for intermittent demand. Foresight: The International Journal of Applied Forecasting, 4(4), 43-46.

\bibitem{b10} Cirillo, P., & Taleb, N. N. (2020). Tail risk of contagious diseases. Nature Physics, 16(6), 606-613.

\bibitem{b11} Reggiani, P., & Weerts, A. H. (2008). A Bayesian approach to decision-making under uncertainty: An application to real-time forecasting in the river Rhine. Journal of Hydrology, 356(1-2), 56-69.

\bibitem{b12} Simpkins, T., Cutler, D., Anderson, K., Olis, D., Elgqvist, E., Callahan, M., & Walker, A. (2014). REopt: a platform for energy system integration and optimization (Vol. 45875, p. V002T03+006). American Society of Mechanical Engineers.

\bibitem{b13} Mishra, S., Pohl, J., Laws, N., Cutler, D., Kwasnik, T., Becker, W., ... & Elgqvist, E. (2022). Computational framework for behind-the-meter DER techno-economic modeling and optimization: REopt Lite. Energy Systems, 13(2), 509-537.

\bibitem{b14} Ogunmodede, O., Anderson, K., Cutler, D., & Newman, A. (2021). Optimizing design and dispatch of a renewable energy system. Applied Energy, 287, 116527.

\end{thebibliography}

\end{document}

### 2024-05-27 reopt_interface.py

@@ -2,7 +2,7 @@
 Generally useufl utility functions
 """
 
-__version__ = 28
+__version__ = 30
 
 import os
 import sys
@@ -17,6 +17,8 @@ import matplotlib.pyplot as plt
 import matplotlib.patches as mpatches
 from plotly.subplots import make_subplots
 from src.post_and_poll import get_api_results
+
+pd.options.display.float_format = '{:.2f}'.format
 
 class dotdict(dict):
     __getattr__ = dict.__getitem__
@@ -46,8 +48,8 @@ def setup(config_file:str=None) -> dotdict:
                 cfg.solar_angles = [sys.argv[i + 2]]
                 note += f'a{sys.argv[i + 2]}_'
             if arg == '-s':
-                cfg.solar_scaler = float(sys.argv[i + 2])
-                note += f's{cfg.solar_scaler:.1f}_'
+                cfg.solar_capacity_kw = float(sys.argv[i + 2])
+                note += f's{cfg.solar_capacity_kw:.1f}_'
             if arg == 'TEST':
                 cfg.test = True
                 note += 'TEST_'             
@@ -68,10 +70,20 @@ def setup(config_file:str=None) -> dotdict:
         note += cfg.note + '_'
     else:
         note = ''
-        
-    cfg.solar_file = cfg.data_dir + cfg.solar_file
-    cfg.load_file = cfg.data_dir + cfg.load_file
+    
+    cfg.load_file = cfg.data_dir + cfg.load_file    
     cfg.tariff_file = cfg.data_dir + cfg.tariff_file
+    if 'solar_file' in cfg.keys():
+        cfg.solar_file = cfg.data_dir + cfg.solar_file
+    if 'load_forecast_file' in cfg.keys():
+        cfg.load_forecast_file = cfg.data_dir + cfg.load_forecast_file
+    if 'energy_price_buy_file' in cfg.keys():
+        cfg.energy_price_buy_file = cfg.data_dir + cfg.energy_price_buy_file
+    if 'energy_price_sell_file' in cfg.keys():
+        cfg.energy_price_sell_file = cfg.data_dir + cfg.energy_price_sell_file
+    if 'export_rate_beyond_net_metering_limit_file' in cfg.keys():
+        cfg.export_rate_beyond_net_metering_limit_file = cfg.data_dir \
+            + cfg.export_rate_beyond_net_metering_limit_file
 
     # outputs dir
[…]

### 2024-05-27 src/results_poller.py

@@ -7,7 +7,7 @@ import time
 from src.logger import log
 
 
-def poller(url, poll_interval=5):
+def poller(url, poll_interval=3):
     """
     Function for polling the REopt API results URL until status is not "Optimizing..."
     :param url: results url to poll
@@ -19,7 +19,10 @@ def poller(url, poll_interval=5):
     key_error_threshold = 3
     status = "Optimizing..."
     log.info("Polling {} for results with interval of {}s...".format(url, poll_interval))
-    while True:
+    tries = 0
+    while tries < 10:
+        tries += 1
+        print('Polling try',tries)
 
         resp = requests.get(url=url, verify=False)
         resp_dict = json.loads(resp.content)
@@ -42,7 +45,7 @@ def poller(url, poll_interval=5):
     return resp_dict
 
 
-def poller_v3(url, poll_interval=5):
+def poller_v3(url, poll_interval=3):
     """
     Function for polling the REopt API results URL until status is not "Optimizing..."
     :param url: results url to poll
@@ -54,7 +57,10 @@ def poller_v3(url, poll_interval=5):
     key_error_threshold = 3
     status = "Optimizing..."
     log.info("Polling {} for results with interval of {}s...".format(url, poll_interval))
-    while True:
+    tries = 0
+    while tries < 10:
+        tries += 1
+        print('Polling try',tries)
 
         resp = requests.get(url=url, verify=False)
         resp_dict = json.loads(resp.content)

### 2024-07-16 paper/paper.tex
final work for paper

@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System}
+\title{The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System \\
+\thanks{This study was carried out in MESSI – Management Energy Systems for Smart Islands project, within the PRIN PROGETTI DI RICERCA DI RILEVANTE INTERESSE NAZIONALE – Bando 2022 and received funding from the European Union Next-GenerationEU (PIANO NAZIONALE DI RIPRESAE RESILIENZA - PNRR MISSIONE 4 COMPONENTE 2, INVESTIMENTO 1.1 –D.D.
+n.
+104 del 02/02/2022, 2022HMYX2C).
+This manuscript reflects only the authors’ views and opinions, neither the European Union nor the European Commission can be considered responsible for them.}}
 
 \author{\IEEEauthorblockN{Michael Wood}
-\IEEEauthorblockA{Energy Department\\
+\IEEEauthorblockA{Department of Energy\\
 Politecnico di Milano\\
@@
 \IEEEauthorblockN{Emanuele Ogliari}
-\IEEEauthorblockA{Energy Department\\
+\IEEEauthorblockA{Department of Energy\\
 Politecnico di Milano\\
@@
 }
-%\and
-%\IEEEauthorblockN{Travis Simpkins}
-%\IEEEauthorblockA{muGrid Analytics\\
-%Littleton, CO, USA\\
-%}
 \and
 \IEEEauthorblockN{Sonia Leva}
-\IEEEauthorblockA{Energy Department\\
+\IEEEauthorblockA{Department of Energy\\
 Politecnico di Milano\\
@@
 \begin{abstract}
-    Distributed renewable microgrids will be a crucial technology during the energy transition.
-Still, many vehicle-to-grid, demand response, and storage battery resources are not utilized fully to reduce consumer electric costs or support the larger grid as needed.
-This is due to poor integration between systems, but also because of a challenging forecasting problem that is required to be solved to achieve near-optimal unit commitment.
-Traditional forecasting methods and also modern machine learning algorithms are often trained and evaluated on mean squared error, which may not optimize for or predict the performance of a forecast in an optimal energy management system.
-This novel work constructs several different forecasts with different error distributions to study the impact on simulated optimal battery dispatch.
-The findings are that forecast error is most important during peak load periods and peak price periods, especially with consumer demand charges in place, and a zero-bias forecast is not necessarily advantageous.
-Recommendations are made to train and validate forecasting models to be effective with a downstream decision maker and not simply be optimized for a chosen error metric.
+    Distributed renewable resources and microgrids will be a crucial technology during the energy transition.
+Fully utilizing these to reduce consumer electric costs will often necessitate forecasting electric load, required to solve the unit commitment problem.
+Traditional forecasting methods and also modern machine learning algorithms are often trained and evaluated on mean squared error, which may not be the best choice for designing forecasts that work effectively with a downstream decision maker: an optimal energy management system.
+This novel work constructs several different forecasts with different error distributions to study the error impact on simulated optimal battery dispatch in a building microgrid.
+The findings are that forecast error is most important during peak load periods and peak price periods, especially with consumer demand charges in place, and a zero-bias or random Gaussian error distribution is necessarily advantageous.
     \end{abstract}
@@
 However, depending on the control action, the cost of inaction, and other variables such as market opening and closing times, forecasting is required to anticipate the changes in load or generation, for instance by having enough State of Charge (SOC) in energy storage.
-This forecast-response paradigm will be increasingly important as certain regions experience more extreme weather events, and renewable generation adds uncertainty to power systems and markets.
+%This forecast-response paradigm will be increasingly important as certain regions experience more extreme weather events, and renewable generation adds uncertainty to power systems and markets.
 
-For these reasons, errors in forecasts can significantly impact the efficiency and reliability of large and small power systems.
-And since forecasts are always acted upon by some downstream decision maker, a discussion of the forecast errors must also consider the decision maker.
-Therefore this work examines recent literature forecasting error in power systems and then simulates several statistically diverse forecasts in an optimal Energy Management System (EMS) to evaluate the effect of forecast error on the system's performance.
+In a forecast-and-optimizer Energy Management System (EMS) approach, errors in forecasts can significantly impact the performance of downstream decision-makers.
+Therefore this work simulates several statistically diverse forecasts in an optimal EMS to evaluate the effect of forecast error on the system's performance.
 
@@
 Electric load forecasting is likely the oldest forecast in power systems.
-Long-term forecasts on the order of years were required to plan new generation and transmission infrastructure.
-Medium-term forecasts on the order of months were soon required to manage seasonal variations in load, especially regarding fuel storage and generator maintenance periods.
-In more recent times, short-term forecasts on the order of hours to a few days aided transmission operators in managing congestion and informed market participants after the re-regulation of energy markets in the latter half of the 20th century.
-Most recently, nowcasting on the order of minutes has become important to manage building and campus generation and loads in real-time, which don't benefit from the spatial aggregation of loads, and thus have more load variability.
+Recently short-term forecasts, on the order of hours to a few days, have been very important in supporting stable and efficient real-time market and operational decisions such as managing transmission congestion and informing market participants of their day-ahead bidding strategies.
 
-Techniques for load forecasting include traditional statistical methods such as SARIMA and modern machine learning approaches like neural networks and support vector machines.
-According to \cite{b1}, while statistical methods offer robustness, machine learning models provide higher accuracy due to their ability to capture nonlinear patterns in the data.
-However, load forecasting errors can arise from various exogenous sources, including sudden weather changes, economic activities, and random anomalies in consumer behavior.
-In \cite{b2} authors emphasize the importance of error decomposition, which involves breaking down the total forecast error into systematic and random components, to better understand and mitigate the sources of inaccuracies.
+Techniques for load forecasting include traditional statistical methods such as SARIMA, but modern machine learning approaches like recurrent neural networks may improve typical error metrics as in \cite{wood2023day} and \cite{matrone2024electric}.
+Load forecasting errors can be inherent to the model or arise from various exogenous sources, including sudden weather changes, economic activities, and random anomalies in consumer behavior.
+In \cite{hong2016probabilistic} authors emphasize the importance of error decomposition, which involves breaking down the total forecast error into systematic and random components, to better understand and mitigate the sources of inaccuracies.
 
@@
 
-Solar power forecasting involves predicting the amount of power generated by solar PV systems.
-The error of these forecasts is affected by factors such as cloud cover, different types and elevations of clouds, temperature, wind, and electrical or mechanical phenomena in the PV system such as cell degradation and soiling.
-Typically the input features to a solar prediction model include a numerical weather prediction forecast and terrestrial solar radiation estimated by a clear sky model, such as in \cite{b7}.
+Solar PV can be said to reduce the net load in many power systems because it is almost always dispatched immediately, having a near-zero marginal cost.
+Therefore a discussion of load forecasting errors should also consider solar PV forecast errors, which are affected by factors such as cloud cover, different types and elevations of clouds, temperature, wind, and electrical or mechanical phenomena in the PV system such as cell degradation and soiling \cite{leva2017analysis}.
 
-Researchers in \cite{b3} demonstrated that statistical methods like ARIMA can be adapted for solar forecasting but often fall short in capturing the high variability.
-Instead, machine learning techniques, including ensemble methods and hybrid physically informed neural networks have shown improved performance as in \cite{b4} and \cite{b7}.
-Solar forecasting errors are often characterized by their dependence on weather conditions more than autocorrelation, making integration with real-time weather data critical.
+Statistical methods like ARIMA can be adapted for solar forecasting but often fall short in capturing the high variability.
+Instead, machine learning techniques, including ensemble methods and hybrid physically informed neural networks have shown improved performance as in \cite{yang2018history} and \cite{matera2024time}.
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{flowchart.png}
-    \caption{Simulation Flowchart.
-The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery.
-The output is the hourly battery dispatch vector, which is optimal for the given inputs.
-The assumption is the battery dispatch vector is now directly in operation.
-Calculating the site load from the true load and solar vectors allows to calculate the final cost of electricity.}
+    \includegraphics[width=1\linewidth]{images/flowchart.png}
+    \caption{Simulation Flowchart}
     \label{fig:flowchart}
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\linewidth]{step1.png}
-%     \caption{Simulation Step 1.
-The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery.
-The outputs are an hourly battery dispatch vector, which is optimal for the given inputs, and the associated costs that would be incurred if the load and solar vectors were true.}
-%     \label{fig:step1}
-% \end{figure}
-
 \subsection{Error Analysis and Mitigation}
 
-Error analysis involves assessing the forecast accuracy using metrics such as Mean Absolute Error (MAE), Mean Squared Error (MSE), and Mean Absolute Percentage Error (MAPE), which are most common in deterministic forecasts.
-In \cite{b5} authors suggest that incorporating probabilistic forecasts, which provide a range of possible outcomes instead of a single point prediction, can enhance the robustness of energy optimization strategies.
-Therefore probabilistic metrics are needed also, such as the Prediction Interval Coverage Probability (PICP) and Prediction Interval Normalized Average Width (PINAW).
-Error metrics are powerful tools for comparing forecast models and are often required for parameters fitting, and can even incorporate a benchmark prediction such as MASE, proposed in \cite{b9}.
-
-Summary statistical metrics are helpful but often the shape of model residuals tells more of the story.
+Error analysis involves assessing the forecast accuracy using metrics.
+Common deterministic forecasts are Mean Absolute Error (MAE), Mean Squared Error (MSE),  Mean Absolute Percentage Error (MAPE), and Mean Absolute Scaled Error (MASE), the last of which scales to a simple persistence benchmark.
+Rather for stochastic methods, metrics are required such as the Prediction Interval Coverage Probability (PICP) and Prediction Interval Normalized Average Width (PINAW).
 A common problem is forecast bias, the tendency to have a non-zero mean for all forecasted values or just during certain intervals.
-This may especially occur for particular clusters of intervals with common physical phenomena, such as grid outages or extreme weather events.
-Extreme magnitude clusters can have a large impact on the EMS performance and be difficult to predict, especially if the events are quite rare \cite{b10}.
+Large errors are also caused by out-of-sample physical phenomena, such as grid outages or extreme weather events.
+Extreme magnitude clusters can have a large impact on the EMS performance and be difficult to predict, especially if the events are quite rare \cite{cirillo2020tail}.
 
 Mitigating forecasting errors involves both improving forecast models and developing strategies to manage uncertainty.
-Authors in \cite{b6} highlight the use of ensemble forecasting, where multiple models are used to generate a range of possible outcomes, thus providing a measure of the forecast uncertainty.
-In \cite{b6i} forecast uncertainty is mitigated with a strategy to minimize starting SOC of a hot sodium nickel battery.
-Additionally, reinforcement learning algorithms can continuously learn and adjust from new data can help reduce errors over time.
-Bayesian statistics and approaches that consider decision-making under risk may aid the final EMS or decision-maker when the uncertainty is measurable \cite{b11}
+Analysis in \cite{makridakis2022predicting} of the M5 competition results show that the highest performance methods often use ensemble approaches, where multiple models are used to generate a range of possible outcomes, thus providing a measure of the forecast uncertainty.
+In \cite{grillo2012optimal} forecast uncertainty is mitigated with a strategy to minimize the starting SOC of a hot sodium nickel battery.
+Bayesian deep learning \cite{sun2019using} and approaches that consider decision-making under risk may aid the final EMS or decision-maker when the uncertainty is measurable.
 
@@
     \centering
-    \includegraphics[width=.87\linewidth]{one-line.png}
-    \caption{The simulated system is a medium-sized municipal building in Wisconsin, USA, with actual on-site solar (111 kWp).
-A hypothetical 100 kW 200 kWh storage battery is simulated.
-Load and solar forecasts are derived from true 1-minute interval data form the site.
-One case study includes the real retail electric tariff at this site.}
+    \includegraphics[width=.78\linewidth]{images/one-line.png}
+    \caption{Site One-Line Diagram }
     \label{fig:one-line}
@@
 
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\linewidth]{step2.png}
-%     \caption{Simulation Step 2.
-The output battery dispatch vector is used, along with the true load and solar vectors, to calculate the grid exchange vector.
-This is then used to calculate what the actual retail electric cost would be if the battery had been dispatched according to the output from ReOpt.}
-%     \label{fig:step2}
-% \end{figure}
-
-This paper aims to construct several statistically different electric load forecasts and simulate the performance of an optimal EMS.
-The EMS controls a storage battery to minimize the retail cost of electricity to a medium-sized municipal building.
-By keeping the MAE constant among almost all the forecasts, the differing final retail costs illustrate how the shape of forecast errors impacts the downstream decision-maker in specific ways.
-
-Our main contribution to the literature is the novel approach of manually adding disturbances to the perfect forecast to create and study specific error distributions.
-The methodology is robust due to the use of true measured 1-minute interval electric load, true measured 1-minute solar PV production, a thoroughly validated optimal EMS (ReOpt by the National Renewable Energy Lab) \cite{b12}, a true retail electric tariff, and two modified tariffs to study the effects of price structures on the results.
+This study's novel contribution to the literature is the approach of manually adding disturbances to the perfect forecast to create and study specific error distributions.
+The methodology is robust due to the use of true measured 1-minute interval electric load, true measured 1-minute solar PV production, a thoroughly validated optimal EMS (ReOpt by the National Renewable Energy Lab) \cite{simpkins2014reopt}, a true retail electric tariff, and two modified tariffs to study the effects of price structures on the results.
 Simulation code and data are published on GitHub for reproducibility.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{images/weekly.png}
+    \caption{Load Time Series}
+    \label{fig:data-weekly}
+\end{figure}
+% The municipal building load overlaid weekly shows the daily seasonality, weekly seasonality, and much larger peaks which we confirm elsewhere to be during the summer months, and likely due to increased occupancy and air conditioning.
+The data is from one year of 1-minute interval average power measurements and is then mean downsampled to hourly for ReOpt.
+
 \section{Methodology}
 
-\subsection{ReOpt Simulations}
-
-The study approach is a series of computer simulations.
-Each simulation consists of two steps, graphically depicted in Figure \ref{fig:flowchart}.
-Each simulation is performed on one year of time series data, solving the unit commitment problem for a behind-the-meter electric load, co-located solar photovoltaic (PV), and a co-located storage battery.
-The only controllable asset is the storage battery, which can charge or discharge in any time step within its technical limits of maximum power and SOC.
-When the perfect load forecast (true measured load) and perfect solar forecast (true measured solar) are simulated, the result is the theoretical optimal battery dispatch for that year of load and solar measurements.
+The study approach is a series of computer simulations that consist of two steps, graphically depicted in Fig.~\ref{fig:flowchart}.
+Each forecast-and-optimize simulation is performed on one year of time series data, solving the unit commitment problem for a behind-the-meter electric load, a co-located solar photovoltaic (PV) array, and a co-located storage battery.
+The only controllable asset is the storage battery, which can charge or discharge at any time step within its technical limits of maximum power and SOC.
 The following are some useful definitions:
@@
     \item Solar production: $ S(i) \in \mathbb{R}_0^+ [kW]$ 
-    \item Battery net, charge, and discharge: $ B(i) \in \mathbb{R}  = B_{d}^+ - B_{c}^+ [kW]$
+    \item Battery charge, discharge: $ B_{c}(i), B_{d}(i) \in \mathbb{R}_0^+ [kW]$
+    \item Battery net: $ B(i) \in \mathbb{R}  = B_{d} - B_{c}$
     \item Net load: $ L_{net} = L - S$
@@
 
-If instead an imperfect load and solar forecast are provided, the result is the optimal battery dispatch given those inputs.
+\subsection{Optimizer}
+
+The unit commitment problem is solved by a centralized optimizer which is capable of modeling the the controllable assets, in this case only the battery.
+There are two different and important cases to consider:
+
+\begin{enumerate}
+    \item \textbf{Perfect Forecasting.} When the perfect load forecast (true measured load) and perfect solar forecast (true measured solar) are simulated, the result is the theoretical optimal battery dispatch for that year of load and solar measurements.
+    \item \textbf{Imperfect Forecasting.} If instead an imperfect load and solar forecast are provided, the result is the optimal battery dispatch as if those forecasts were the true values.
 In other words, the simulation finds a global minimum of retail electric cost believing the forecasted load and solar to be true.
-The simulation chooses the optimal battery dispatch given the forecasts and other inputs provided.
-Assuming that the battery dispatch is not modified by the EMS in the presence of true measurements, the imperfect forecasts result in a retail electric cost which is necessarily greater than or equal to the theoretical optimal given perfect forecasting.
+Assuming that the battery dispatch is not modified by the EMS in the presence of information about the true measurements, the imperfect forecasts result in a retail electric cost that is necessarily greater than or equal to the theoretical optimal given perfect forecasting.
+\end{enumerate}
 
-ReOpt is a techno-economic distributed energy resource (DER) optimization tool, which is both free and open source, and is well validated in the literature \cite{b13}.
+\subsubsection{ReOpt}
+
+The optimizer in this study is ReOpt, a techno-economic distributed energy resource (DER) planning tool, which is well-validated in the literature \cite{mishra2022computational}.
 It performs optimal operation and sizing of DERs, although it is not intended as a real-time optimal EMS.
@@
 It does so by constructing and solving a mixed-integer linear program (MILP) which minimizes the life cycle cost of new and existing DERs from the perspective of the behind-the-meter DER owner.
-Binary decision variables are required, for instance, to prevent the battery from charging and discharging in the same time step.
-Depending somewhat on the particular solver used, optimality of the solution is guaranteed for moderate complexity problem formulations due to a convex cost function and continuously differentiable, linear constraints \cite{b14}.
-The tool is written using the JuMP library in the Julia programming language, but in this work the tool is accessed via web API and Python script.
+Binary decision variables are required, for instance, to prevent the battery from charging and discharging at the same time step.
+
+Depending somewhat on the particular solver used, optimality of the solution is guaranteed for moderate complexity problem formulations due to a convex cost function and continuously differentiable, linear constraints \cite{ogunmodede2021optimizing}.
+Some disadvantages of ReOpt are the hourly interval which may contribute to errors relative to a real system (\cite{omoyele2024impact}), that forecasts cannot be updating in a rolling horizon manner, and some real-world losses are not considered such as battery heating and cooling.
+
+ReOpt is both free and open source and is written using the JuMP library in the Julia programming language.
+It can be accessed accessed via an interactive web application, or a web API and Python script as in the case of this study.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{images/hist.png}
+    \caption{Error Distributions of Several Forecasts}
+    \label{fig:hist}
+\end{figure}
 
 \subsection{Forecast Construction}
-
-\begin{table}
-    \centering
-    \caption{Forecasts and Two Benchmarks}
-    \label{tab:forecasts}
-    \setlength{\tabcolsep}{3pt}
-    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
-    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
-    \begin{tabular}{l l l}
-        \hline
-        Error Description       & Forecast                    & nMAE  \\
-        \hline
-        \hline
-        Perfect                 & (1) \(y_{perfect} = y_t\)           & 0.0    \\
-        \hline
-        Constant                & (2a) \(y_f = y_t + k\)      & 0.1   \\
-                                & (2b) \(y_f = y_t - k\)      & 0.1   \\
-        \hline
-        Linear                  & (3a) \(y_f = y_t + ky_t\)   & 0.1   \\
-                                & (3b) \(y_f = y_t - ky_t\)   & 0.1   \\
-        \hline
-        Quadratic               & (4a) \(y_f = y_t + ky_t^2\) & 0.1   \\
-                                & (4b) \(y_f = y_t - ky_t^2\) & 0.1   \\
-        \hline
-        Energy (Prices)         & (5a) \(y_f = y_t + kp_e\)   & 0.1   \\
-                                & (5b) \(y_f = y_t - kp_e\)   & 0.1   \\
-        \hline
-        Demand (Prices)         & (6a) \(y_f = y_t + kp_d\)   & 0.1   \\
-                                & (6b)\(y_f = y_t - kp_d\)    & 0.1   \\
-        \hline
-        Random (Gaussian)       & (7) \(y_f = y_t + X\)       & 0.1   \\
-        \\
-        \hline
-        Persistence             & (8) \(y_{persist} = y_t(i-168)\)    & 0.033 \\
-        \hline
-        \hline
-        Solar Only (no battery) & (9) No forecast             & n/a   \\
-        \hline
-    \end{tabular}
-\end{table}
 
@@
 \begin{enumerate}
-\item One hypothesis is that errors during peak load periods is especially harmful to the EMS performance, especially when the rate tariff contains a price on peak demand, also called a demand charge.
+\item One hypothesis is that errors during peak load periods are especially harmful to the EMS performance, especially when the rate tariff contains a price on peak demand, also called a demand charge.
 
-\item A second hypothesis is that forecast errors during high energy prices is detrimental to EMS performance, especially in the absence of a demand charge.
+\item A second hypothesis is that forecast errors during high energy prices are detrimental to EMS performance, especially in the absence of a demand charge.
 \end{enumerate}
@@
 The value of 0.10 was determined experimentally to show a good spread of results: with an nMAE too low all the forecasts would be nearly perfect and indistinguishable, and vice versa.
-The exceptions are that a perfect forecast will have an nMAE of zero, and a seasonal persistence forecast is possibly more interesting without other disturbances since it is already a good benchmark forecast \cite{b9}.
+The exceptions are that a perfect forecast will have an nMAE of zero, and a seasonal persistence forecast is possibly more interesting without other disturbances since it is already a good benchmark forecast \cite{hyndman2006another}.
 By forcing all the manipulated forecasts to have the same nMAE, any differences in the EMS performance can be attributed to the shape of the error distribution and not just the magnitude.
@@
 Because there are no regression or machine learning models to fit we don't separate the data into train, validation, and test subsets.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{images/perf_lines.png}
+    \caption{Case Study 1 Performance}
+    \label{fig:cs1-performance}
+\end{figure}
 
@@
 \begin{align}
-    C_t,m           & = \sum_{k=1}^K [p_{d,k,m}  max(L^+_{site,k,m})  \notag \\
-                & + p_{e,k,m} \sum (L^+_{site,k,m}\Delta t)  \notag \\
-                & + p_{s,k,m} \sum (L^-_{site,k,m}\Delta t) ] \label{eq:cost} \\
-                 \text{subject to:}&  \notag \\
+    C_t,m           & = \sum_{k=1}^K [p_{d,k,m}  max(L^+_{site,k,m}) ...  \notag \\
+                & +  \sum_{k=1}^K (p_{e,k,m} L^+_{site,k,m}\Delta t) ... \notag \\
+                & +  \sum_{k=1}^K (p_{r,k,m} L^-_{site,k,m}\Delta t) ] \label{eq:cost} \\
+                \text{where:}& \notag \\
                 L_{site,k,m}^+(i) & \ge 0 \text{ and } L_{site,k,m}^-(i) \le 0\ \forall\ i \notag \\
-%\end{align}
-%\begin{align*}
-                \text{where:}& \notag \\
                 k & \text{: TOU period} \notag \\
@@
     C_t,m         & \in \mathbb{R}^+ [\$] \text{: total monthly retail electric cost} \notag \\
-    p_{x,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ or } [\$/kWh] \text{: price for TOU } k \notag 
+    p_{x,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ or } [\$/kWh] \text{: price for TOU } k \notag \\
+    x \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag 
 \end{align}
 
-\begin{table}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{images/monthly_peaks_lines.png}
+    \caption{Case Study 1 Monthly Peaks}
+    \label{fig:cs1-peaks}
+\end{figure}
+
+The two benchmarks in Table \ref{tab:forecasts} are forecast 1, the perfect forecast, and forecast 9, a solar-only benchmark, which has no battery.
+With no controllable DERs there are no decision variables and no forecasting to be done.
+The perfect forecast is a theoretical optimal (lowest cost) that can't be exceeded.
+The solar-only case should represent a low benchmark: an optimal EMS controlling a battery should be able to perform better than if the battery wasn't there at all.
+
+\begin{align}
+    P(C_x) [\%]= & \frac{C_x - C_{x,perfect}}{C_{x,solar-only} - C_{x,perfect}} \times 100\% \label{eq:performance} \\
+    \text{where:}& \notag \\
+    C_x =& \text{ cost of forecast to be evaluated [\$]}  \notag \\
+    C_{x,perfect} =& \text{ cost of perfect forecast [\$]}  \notag \\
+    C_{x,solar-only} =& \text{ cost of solar-only benchmark [\$]}  \notag \\
+    x \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag 
+\end{align}
+
+These two book-end benchmarks suggest a normalized performance metric where a sample cost value $C$ lies in the range between the perfect forecast (1) and solar-only benchmark (9).
+This "performance" $P$ takes a value of 0\% when the forecast cost is equal to the solar-only benchmark and a value of 100\% when the forecast cost equals the theoretical optimal.
+
+\begin{table}[t]
+    \centering
+    \caption{Forecasts and Solar-Only Benchmark}
+    \label{tab:forecasts}
+    \setlength{\tabcolsep}{9pt}
+    \begin{tabular}{l l l l}
+        %\hline
+        Forecast               & Note                             & Definition & nMAE \\
+        \hline
+        \hline
+        1 Perfect & Benchmark &  \(y_{perfect} = y_t\)        & 0.0               \\
+        \hline
+        2a Constant+ &             & \(y_f = y_t + k\)           & 0.1               \\
+        2b Constant-  &            &  \(y_f = y_t - k\)           & 0.1               \\
+        \hline
+        3a Linear+     &           &  \(y_f = y_t + ky_t\)        & 0.1               \\
+        3b Linear-      &          &  \(y_f = y_t - ky_t\)        & 0.1               \\
+        \hline
+        4a Quad+         &         &  \(y_f = y_t + ky_t^2\)      & 0.1               \\
+        4b Quad-          &        &  \(y_f = y_t - ky_t^2\)      & 0.1               \\
+        \hline
+        5a Energy+ &Prices       &  \(y_f = y_t + kp_e\)        & 0.1               \\
+        5b Energy- &Prices       &  \(y_f = y_t - kp_e\)        & 0.1               \\
+        \hline
+        6a Demand+ &Prices       &  \(y_f = y_t + kp_d\)        & 0.1               \\
+        6b Demand- &Prices       &  \(y_f = y_t - kp_d\)        & 0.1               \\
+        \hline
+        7 Random &Gaussian      &  \(y_f = y_t + X\)            & 0.1               \\
+        \hline
+        8 Persist & 7 day               &  \(y_{persist} = y_t(i-168)\) & 0.033             \\
+        \hline
+        \hline
+        9 Solar Only & Benchmark &  No forecast                  & n/a               \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[t]
     \centering
@@
     \setlength{\tabcolsep}{3pt}
-    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
-    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
     \begin{tabular}{l l l l l}
-        \hline
+        %\hline
         Period & Hours & Buy Prices & Buy Prices & Sell Price  \\
@@
         \hline
-        Off peak & 0:00-9:00,  & 0.056 \$/kW  & 0.056 \$/kW & 0.050 \$/kWh \\
+        Off-peak & 0:00-9:00,  & 0.056 \$/kW  & 0.056 \$/kW & 0.050 \$/kWh \\
                   & 21:00-0:00 &              &        &       \\
@@
 
-\begin{table}
+\begin{table}[t]
     \centering
@@
     \label{tab:case-studies}
-    \setlength{\tabcolsep}{3pt}
-    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
-    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
+    \setlength{\tabcolsep}{6pt}
     \begin{tabular}{l l l}
-        \hline
+        %\hline
         & Tariff & Modifications \\
@@
         \hline
-        1 & Retail Electric Tariff (Table \ref{tab:tariff}) & \\
-        2 & Retail Electric Tariff (Table \ref{tab:tariff}) & All \$/kW prices = 0  \\
-        3 & Retail Electric Tariff (Table \ref{tab:tariff}) & Sell price = CA NEM3.0 \\
+        CS1 & Retail Electric Tariff (Table \ref{tab:tariff}) & \\
+        CS2 & Retail Electric Tariff (Table \ref{tab:tariff}) & All \$/kW prices = 0  \\
+        CS3 & Retail Electric Tariff (Table \ref{tab:tariff}) & Sell price = CA NEM3.0 \\
         \hline
@@
 
-The two benchmarks in Table \ref{tab:forecasts} are forecast 1, the perfect forecast, and forecast 9, a solar-only benchmark, which has no battery.
-With no controllable DERs there are no decision variables and no forecasting to be done.
-The perfect forecast is a theoretical optimal (lowest cost) that can't be exceeded.
-The solar-only case should represent a low benchmark: an optimal EMS controlling a battery should be able to perform better than if the battery wasn't there at all.
-
-\begin{align}
-    P(C_x) [\frac{kW}{kW}]= & (C_x - C_{x,perfect}) \over (C_{x,solar-only} - C_{x,perfect}) \label{eq:performance} \\
-    \text{where:}& \notag \\
-    x  \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag \\
-    C_x =& \text{ cost of forecast to be evaluated [\$]}  \notag \\
-    C_{x,perfect} =& \text{ cost of perfect forecast [\$]}  \notag \\
-    C_{x,solar-only} =& \text{ cost of solar-only benchmark [\$]}  \notag 
-\end{align}
-
-These two book-end benchmarks suggest a normalized performance metric where a sample cost value $C$ lies in the range between the perfect forecast (1) and solar-only benchmark (9).
-This "performance" $P$ takes a value of 0 when the forecast cost is equal to the solar-only benchmark and a value of 1 when the forecast cost equals the theoretical optimal.
+\begin{table}[t]%[!ht]
+    \centering
+    \caption{Case Studies 1-3: Forecasts vs Performance}
+    \label{tab:performance}
+    \setlength{\tabcolsep}{1.5pt}
+    \begin{tabular}{l r r r r r r r r r r r}
+        %\hline
+        Forecast            & CS1      &          &          &               & CS2      &          &               & CS3      &          &          &               \\ 
+        ~            & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$      \\ \hline \hline
+        1 Perfect    & 100      & 100      & 100      & 100           & 100      & 100      & 100           & 100      & 100      & 100      & 100           \\ \hline
+        2a Constant+ & 65     & 100     & -21    & \textbf{93} & 54     & -49    & 76          & 65     & 100     & -23    & \textbf{89} \\
+        2b Constant- & 85     & 100     & 93     & \textbf{94} & 85     & 93     & 84          & 85     & 100     & 92     & \textbf{94} \\ \hline
+        3a Linear+   & 66     & 89     & -18    & 87          & 55     & -45    & 77          & 66     & 89     & -19    & 82          \\
+        3b Linear-   & 84     & 93     & 94     & 89          & 84     & 94     & 82          & 84     & 93     & 93     & \textbf{89} \\ \hline
+        4a Quad+     & 67     & 76     & -12    & 79          & 58     & -36    & 78          & 67     & 76     & -12    & 75          \\
+        4b Quad-     & 79     & 78     & 95     & 77          & 79     & 95     & 75          & 79     & 78     & 94     & 78          \\ \hline
+        5a Energy+   & 59     & 100     & -35    & \textbf{92} & 44     & -75    & 69          & 59     & 100     & -37    & 87          \\
+        5b Energy-   & 78     & 100     & 93     & 90          & 78     & 93     & 75          & 78     & 100     & 92     & \textbf{90} \\ \hline
+        6a Demand+   & 48     & 00     & -53    & 88          & 100     & 100     & \textbf{100} & 48     & 100     & -57    & 82          \\
+        6b Demand-   & 38     & 99     & 94     & 70          & 100     & 100     & \textbf{100} & 37     & 99     & 89     & 70          \\ \hline
+        7 Random     & 71     & 34     & 22     & 53          & 67     & 10     & 79          & 73     & 21     & 25     & 45          \\ \hline
+        8 Persist    & 90     & 55     & 73     & 70          & 87     & 65     & \textbf{92} & 90     & 55     & 73     & 70          \\ \hline
+        9 Solar      & 0      & 0      & 0      & 0           & 0      & 0      & 0           & 0      & 0      & 0      & 0           \\ \hline
+    \end{tabular}
+\end{table}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\linewidth]{weekly.png}
-    \caption{The municipal building load overlaid weekly shows the daily seasonality, weekly seasonality, and much larger peaks which we confirm elsewhere to be during the summer months, and likely due to increased occupancy and air conditioning.
-}
-    \label{fig:data-weekly}
-\end{figure}
-
-Three case studies are presented in Table \ref{tab:case-studies}, each with a different tariff structure, but all with the same forecasts, benchmarks, and simulated DERs and site.
+Three case studies are built on the same building load data (Fig.~\ref{fig:data-weekly}) and are presented in Table \ref{tab:case-studies}, each with a different tariff structure but all with the same forecasts, benchmarks, and simulated DERs and site.
 The base tariff in Table \ref{tab:tariff} is only slightly simplified compared to the in vivo one, due to limitations of ReOpt in including a rolling annual demand charge on the cost function.
@@
 
-In all three case studies only the load forecast is manipulated according to Table \ref{tab:forecasts}.
+In all three case studies, only the load forecast is manipulated according to Table \ref{tab:forecasts}.
 Since solar PV has zero marginal cost it is always dispatched except for technical reasons for curtailment.
-Therefore the unit commitment problem can be reframed not as dispatching solar PV and storage to minimize the cost of electricity incurred by the load, but instead as dispatching only storage to minimize the cost of net load ($load - solar$, where $load$ and $solar \in \mathbb{R}_0^+$).
+Therefore the unit commitment problem can be reframed not as dispatching solar PV and storage to minimize the cost of electricity incurred by the load $L_{native}$, but instead as dispatching storage to minimize the cost of net load $L_{net}=L_{native}-S$.
 Now a positive error in the load forecast is identical to a negative error in the solar forecast, and vice versa.
-Furthermore, the combination of a load positive error and solar negative error can be reframed as the combined magnitude error in the net load.
+Furthermore, the combination of a positive load error and negative solar error can be reframed as the combined magnitude error in the net load.
 
-The nMAE of all forecasts is equal to 0.10 except the perfect forecast which is 0, seasonal persistence which is 0.033, and the solar-only benchmark which has no forecast.
+The nMAE of all forecasts is equal to 0.10 except for the perfect forecast which is 0, seasonal persistence which is 0.033, and the solar-only benchmark which has no forecast.
 
@@
 The site has previously installed solar PV and energy meters which capture 1-minute time series data.
-For the purpose of this study the battery and EMS are just abstractions.
-The simulations should somewhat accurately model power flows and battery charge and discharge of the site in Figure \ref{fig:one-line}.
-Conductor and transformer losses are estimated as a constant loss percentage, and real power reduction due to fluctuating power factor is not considered.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\linewidth]{hist.png}
-    \caption{Error Distributions of Several Forecasts.
-The Persist errors are well-behaved with a zero mean, as expected for a differences seasonal time series.
-The Linear and Quad errors have substantial skew and then long tails away from zero, and the positive and negative bias forecasts are mirror images, as expected.
-The Quad forecast errors appear to have still more skew.}
-    \label{fig:hist}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\linewidth]{perf_lines.png}
-    \caption{Case Study 1 Performance.
-The horizontal axis is sorted for increasing total cost performance $P_{Ct}$ which rises quickly above 0.5.
-Some forecasts have a negative performance on revenue despite a good total cost performance.
-This is the same data as in Table \ref{tab:performance}.}
-    \label{fig:perf-lines}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\linewidth]{monthly_peaks_lines.png}
-    \caption{Case Study 1 Monthly Peaks by Forecast.
-For this case study demand cost is a good predictor of total cost.
-Some forecasts such as 2a and 2b are able to chase down demand peaks for all months, whereas others are less able especially in August, September, and October.
-}
-    \label{fig:monthly-peaks-lines}
-\end{figure}
+For the purpose of this study, the battery and EMS are just abstractions.
+The simulations should somewhat accurately model power flows and battery charge and discharge of the site in Fig.~\ref{fig:one-line}.
+Conductor and transformer losses are estimated as a constant loss percentage, and real power reduction due to fluctuating power factors is not considered.
 
@@
 
-The error distributions in Figure \ref{fig:hist} reflect the intention to have different positive and negative forecast biases and to cluster the errors near peak values.
-In the 2a and 2b Constant forecasts the errors take a single positive or negative value to the constant positive or negative offset (not shown in the image).
+The error distributions in Fig.~\ref{fig:hist} reflect the intention to have different positive and negative forecast biases and to cluster the errors near peak values.
+In the 2a and 2b Constant forecasts, the errors take a single positive or negative value to the constant positive or negative offset (not shown in the image).
 
-The final calculated costs for case study 1 in Figure \ref{fig:perf-lines} (sorted in order of increasing $P_{Ct}$) show that demand cost $P_{Cd}$ is a good predictor of total cost.
+The final calculated costs for case study 1 in Fig.~\ref{fig:cs1-performance} (sorted in order of increasing $P_{Ct}$) show that demand cost $P_{Cd}$ is a good predictor of total cost.
 In fact, the Pearson correlation between the two is 0.94, whereas energy cost $P_{Ce}$ only correlates at 0.74 and revenue $P_{Re}$ is uncorrelated at 0.14.
 The Constant and Energy price forecasts are likely the best performing because both have fairly evenly distributed errors throughout the day, whereas Linear, Demand, and Quadratic forecasts focus the errors around load peaks or high demand prices.
-An unexpected finding is that the worst-performing constructed forecast is the Random gaussian disturbance.
-Any single timestep can set the demand peak of the month.
-It appears that the randomly meandering forecast, coupled with a load time series that routinely rises to near its monthly peak (Figure \ref{fig:data-weekly}), spells disaster for an EMS charged with always shaving peaks.
+
+An unexpected finding is that the worst-performing constructed forecast for a non-zero power price is the Random Gaussian disturbance ($P_{Cd}$ of 34\% in Table \ref{tab:case-studies}).
+This is due to the forecast not predicting many of the peak load events, any of which can set a fairly high peak of the month and therefore a high demand charge $C_d$ of the month.
+By comparison, the best-performing forecasts for $P_{Cd}$ (Cosntant +/-, Energy +/-, and Demand-) are those with the most constant error distributions in time, meaning that the forecasts temporally predict peaks well but not the magnitude.
+It's apparent from studying Fig.~\ref{fig:cs1-peaks} that the peak power is reduced (comparing Solar only to Perfect) by about 10 kW in winter and 20-30 kW in summer, which are not large values compared to the 100 kW 200 kWh battery simulated.
+The battery therefore has some buffer, or margin, available to effectively shave peaks as long as it is dispatched at 10-30 kW for a period that envelopes the true peak.
+This is to say that detecting the exact peak magnitude is not crucial to near-optimal demand charge reduction at this operating point.
 
 This is confirmed by case study 3 results, also deriving from a demand charge tariff, in Table \ref{tab:performance} where the Random forecast is again the worst performer.
-Both case studies 1 and 3 have the same four forecasts near or above 0.90: 2b Constant-, 2a Constant+, 5b Energy-, and 3b Linear-.
+Both case studies 1 and 3 have the same four forecasts near or above 90\%: 2b Constant-, 2a Constant+, 5b Energy-, and 3b Linear-.
 Both case studies also have similar low performers: Random, Persist, and 6b Demand-, and in both forests the positive and negative bias forecasts don't show obvious trends.
 
-\begin{table}%[!ht]
-    \centering
-    \caption{Case Study 1: Forecasts vs Retail Electric Cost}
-    \label{tab:cs1-cost}
-    \begin{tabular}{l l l l l}
-    \hline
-        ~ & $C_e [\$]$ & $C_d [\$]$ & $R_e [\$]$ & $C_t [\$]$ \\ \hline \hline
-        1 Perfect & 21867.31 & 4608.50 & 8.00 & 26467.81 \\ \hline
-        2b Constant- & 22256.94 & 4608.56 & 42.00 & 26823.50 \\ \hline
-        2a Constant+ & 22805.10 & 4608.56 & 574.00 & 26839.66 \\ \hline
-        5a Energy+ & 22959.75 & 4608.56 & 639.00 & 26929.31 \\ \hline
-        5b Energy- & 22449.53 & 4608.56 & 39.00 & 27019.09 \\ \hline
-        3b Linear- & 22293.84 & 4851.25 & 36.00 & 27109.09 \\ \hline
-        6a Demand+ & 23256.18 & 4608.56 & 725.00 & 27139.74 \\ \hline
-        3a Linear+ & 22786.99 & 4984.94 & 561.00 & 27210.93 \\ \hline
-        4a Quad+ & 22742.46 & 5425.37 & 530.00 & 27637.83 \\ \hline
-        4b Quad- & 22433.59 & 5340.66 & 29.00 & 27745.25 \\ \hline
-        8 Persist & 22140.92 & 6105.94 & 136.00 & 28110.86 \\ \hline
-        6b Demand- & 23527.14 & 4646.89 & 37.00 & 28137.03 \\ \hline
-        7 Random & 22635.07 & 6810.84 & 372.00 & 29073.91 \\ \hline
-        9 Solar & 24546.16 & 7951.44 & 476.00 & 32021.60 \\ \hline
-    \end{tabular}
-\end{table}
-
 In case study 2 there is no demand charge, and now the energy cost $P_{Ce}$ correlates with the total cost at 0.92.
-Without the demand charge a forecast with errors concentrated around high demand prices should be relatively error-free during the other times of the day, and indeed the two best performing models are 6a and 6b Demand+ and Demand-.
-Persist performs above 0.90 for the first time and Random is 0.79, suggesting both of those error shapes are harmful to peak shaving.
-
-% \begin{table}[!ht]
-%     \centering
-%     \caption{Case Study 1: Forecasts vs Performance}
-%     \label{tab:cs1-performance}    
-%     \begin{tabular}{l l l l l}
-%     \hline
-%         ~ & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
-%         9 Solar & 0 & 0 & 0 & 0 \\ \hline
-%         7 Random & 0.71 & 0.34 & 0.22 & 0.53 \\ \hline
-%         6b Demand- & 0.38 & 0.99 & 0.94 & 0.70 \\ \hline
-%         8 Persist & 0.90 & 0.55 & 0.73 & 0.70 \\ \hline
-%         4b Quad- & 0.79 & 0.78 & 0.95 & 0.77 \\ \hline
-%         4a Quad+ & 0.67 & 0.76 & -0.12 & 0.79 \\ \hline
-%         3a Linear+ & 0.66 & 0.89 & -0.18 & 0.87 \\ \hline
-%         6a Demand+ & 0.48 & 1.00 & -0.53 & 0.88 \\ \hline
-%         3b Linear- & 0.84 & 0.93 & 0.94 & 0.89 \\ \hline
-%         5b Energy- & 0.78 & 1.00 & 0.93 & 0.90 \\ \hline
-%         5a Energy+ & 0.59 & 1.00 & -0.35 & 0.92 \\ \hline
-%         2a Constant+ & 0.65 & 1.00 & -0.21 & 0.93 \\ \hline
-%         2b Constant- & 0.85 & 1.00 & 0.93 & 0.94 \\ \hline
-%         1 Perfect & 1 & 1 & 1 & 1 \\ \hline
-%     \end{tabular}
-% \end{table}
-
-% \begin{table}[!ht]
-%     \centering
-%     \caption{Case Study 2 (No Demand Price): Forecasts vs Performance}
-%     \label{tab:cs2-performance}    
-%     \begin{tabular}{l l l l}
-%     \hline
-%         ~ & $P_{Ce}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
-%         9 Solar & 0 & 0 & 0 \\ \hline
-%         5a Energy+ & 0.44 & -0.75 & 0.69 \\ \hline
-%         5b Energy- & 0.78 & 0.93 & 0.75 \\ \hline
-%         4b Quad- & 0.79 & 0.95 & 0.75 \\ \hline
-%         2a Constant+ & 0.54 & -0.49 & 0.76 \\ \hline
-%         3a Linear+ & 0.55 & -0.45 & 0.77 \\ \hline
-%         4a Quad+ & 0.58 & -0.36 & 0.78 \\ \hline
-%         7 Random & 0.67 & 0.10 & 0.79 \\ \hline
-%         3b Linear- & 0.84 & 0.94 & 0.82 \\ \hline
-%         2b Constant- & 0.85 & 0.93 & 0.84 \\ \hline
-%         8 Persist & 0.87 & 0.65 & 0.92 \\ \hline
-%         6b Demand- & 1.00 & 1.00 & 1.00 \\ \hline
-%         6a Demand+ & 1.00 & 1.00 & 1.00 \\ \hline
-%         1 Perfect & 1 & 1 & 1 \\ \hline
-%     \end{tabular}
-% \end{table}
-
-% \begin{table}[!ht]
-%     \centering
-%     \caption{Case Study 3 (NEM3.0 Sell Price): Forecasts vs Performance}
-%     \label{tab:cs3-performance}    
-%     \begin{tabular}{l l l l l}
-%     \hline
-%     ~ & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline
-%         9 Solar & 0 & 0 & 0 & 0 \\ \hline
-%         7 Random & 0.73 & 0.21 & 0.25 & 0.45 \\ \hline
-%         8 Persist & 0.90 & 0.55 & 0.73 & 0.70 \\ \hline
-%         6b Demand- & 0.37 & 0.99 & 0.89 & 0.70 \\ \hline
-%         4a Quad+ & 0.67 & 0.76 & -0.12 & 0.75 \\ \hline
-%         4b Quad- & 0.79 & 0.78 & 0.94 & 0.78 \\ \hline
-%         6a Demand+ & 0.48 & 1.00 & -0.57 & 0.82 \\ \hline
-%         3a Linear+ & 0.66 & 0.89 & -0.19 & 0.82 \\ \hline
-%         5a Energy+ & 0.59 & 1.00 & -0.37 & 0.87 \\ \hline
-%         3b Linear- & 0.84 & 0.93 & 0.93 & 0.89 \\ \hline
-%         2a Constant+ & 0.65 & 1.00 & -0.23 & 0.89 \\ \hline
-%         5b Energy- & 0.78 & 1.00 & 0.92 & 0.90 \\ \hline
-%         2b Constant- & 0.85 & 1.00 & 0.92 & 0.94 \\ \hline
-%         1 Perfect & 1 & 1 & 1 & 1 \\ \hline
-%     \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%
-
-\begin{table}%[!ht]
-    \centering
-    \caption{Case Studies 1-3: Forecasts vs Performance}
-    \label{tab:performance}
-    \setlength{\tabcolsep}{1pt}
-    \begin{tabular}{l|l l l l|l l l| l l l l}
-        \hline
-        ~            & CS1      &          &          &               & CS2      &          &               & CS3      &          &          &          \\ \hline 
-        ~            & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Re}$ & $P_{Ct}$      & $P_{Ce}$ & $P_{Cd}$ & $P_{Re}$ & $P_{Ct}$ \\ \hline \hline 
-        9 Solar      & 0        & 0        & 0        & 0             & 0        & 0        & 0             & 0        & 0        & 0        & 0        \\ \hline  
-        8 Persist    & 0.90     & 0.55     & 0.73     & 0.70          & 0.87     & 0.65     & \textbf{0.92} & 0.90     & 0.55     & 0.73     & 0.70     \\ \hline
-        7 Random     & 0.71     & 0.34     & 0.22     & 0.53          & 0.67     & 0.10     & 0.79          & 0.73     & 0.21     & 0.25     & 0.45     \\ \hline
-        6b Demand-   & 0.38     & 0.99     & 0.94     & 0.70          & 1.00     & 1.00     & \textbf{1.00} & 0.37     & 0.99     & 0.89     & 0.70     \\ \hline
-        6a Demand+   & 0.48     & 1.00     & -0.53    & 0.88          & 1.00     & 1.00     & \textbf{1.00} & 0.48     & 1.00     & -0.57    & 0.82     \\ \hline
-        5b Energy-   & 0.78     & 1.00     & 0.93     & 0.90          & 0.78     & 0.93     & 0.75          & 0.78     & 1.00     & 0.92     & \textbf{0.90}     \\ \hline
-        5a Energy+   & 0.59     & 1.00     & -0.35    & \textbf{0.92} & 0.44     & -0.75    & 0.69          & 0.59     & 1.00     & -0.37    & 0.87     \\ \hline
-        4b Quad-     & 0.79     & 0.78     & 0.95     & 0.77          & 0.79     & 0.95     & 0.75          & 0.79     & 0.78     & 0.94     & 0.78     \\ \hline
-        4a Quad+     & 0.67     & 0.76     & -0.12    & 0.79          & 0.58     & -0.36    & 0.78          & 0.67     & 0.76     & -0.12    & 0.75     \\ \hline
-        3b Linear-   & 0.84     & 0.93     & 0.94     & 0.89          & 0.84     & 0.94     & 0.82          & 0.84     & 0.93     & 0.93     & \textbf{0.89}     \\ \hline
-        3a Linear+   & 0.66     & 0.89     & -0.18    & 0.87          & 0.55     & -0.45    & 0.77          & 0.66     & 0.89     & -0.19    & 0.82     \\ \hline
-        2b Constant- & 0.85     & 1.00     & 0.93     & \textbf{0.94} & 0.85     & 0.93     & 0.84          & 0.85     & 1.00     & 0.92     & \textbf{0.94}     \\ \hline
-        2a Constant+ & 0.65     & 1.00     & -0.21    & \textbf{0.93} & 0.54     & -0.49    & 0.76          & 0.65     & 1.00     & -0.23    & \textbf{0.89}     \\ \hline
-        1 Perfect    & 1        & 1        & 1        & 1             & 1        & 1        & 1             & 1        & 1        & 1        & 1        \\ \hline
-    \end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\linewidth]{hist_linscaledup.png}
-%     \caption{Forecast 3+: Error $\alpha$ Load (positive).
-The errors have heavy skew to the low end and a long tail to the high end.
-This effect is mirrored for the forecast 3- for negative bias, and more pronounced for both forecast 4+ and 4- with the quadratic relationship.}
-%     \label{fig:hist-linscaledup}
-% \end{figure}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\linewidth]{hist_persist.png}
-%     \caption{Forecast 8: Seasonal Persistence.
-Distribution of errors for the 7day persistence forecast, the only once with a lower nMAE than 0.10 (0.033).The errors are essentially the difference of the time series so we expect to see symmetry around a mean of zero.}
-%     \label{fig:hist-persist}
-% \end{figure}
+Without the demand charge, a forecast with errors concentrated around high demand prices should be relatively error-free during the other times of the day, and indeed the two best performing models are 6a and 6b Demand+ and Demand-.
+Persist performs above 90\% for the first time and Random is 79\%, suggesting both of those error shapes are harmful to peak shaving.
 
@@
 The initial investigation has discovered that several different load forecasts with identical nMAE can have extremely different performances in a simulated EMS.
-Advances in machine learning, synthetic data, and transfer learning offers promising improvements in forecast accuracy.
+Advances in machine learning, synthetic data, and transfer learning offer promising improvements in forecast accuracy.
 However ongoing research is essential to develop the right forecasts and not generic ones, especially regarding peak shaving and peak load forecasting.
+An important finding is that a random Gaussian error distribution performs very poorly for a non-zero power price, suggesting that regression parameter fitting to minimize error in this way may suffer relative to other training or forecast methods.
 
-Future work will include combined true error distributions from trained forecast models, and will combine solar and load forecast errors explicitly to discern if the errors often have similar properties or not.
-Future forecasting efforts will use tools like custom loss functions, Kalman filtering, and decision making under risk approaches to tune the forecast in the direction that is optimal for the EMS to reduce costs.
-Finally, the cost of carbon will be considered in a multi-objective optimization in addition to economic cost.
+The application of this work is in designing better forecasts for EMS operations.
+Whereas fitting SARIMA according to MSE could be effective in predicting day-ahead market prices, this study shows that a custom loss function should be used that emphasizes error reduction around peaks.
+Also, a given forecast with a higher statistical metric (such as MAE) might be preferable if the errors are more temporarily constant, even if there is non-zero bias.
 
-\begin{thebibliography}{00}
+Some limitations of the study are: not including typical forecast models like regression or neural networks, not separately considering load and forecasting errors, using a single battery capacity, and not using a rolling horizon approach.
+Therefore future work will include various trained load and solar forecast models and a complete rolling-horizon optimal EMS.
+Future forecasting efforts will use tools like custom loss functions, Kalman filtering, and decision-making under risk approaches to tune the forecast in the direction that is optimal for the EMS to reduce costs, as well as investigate the role of load vs solar forecast errors.
+Finally, the cost of carbon should be considered in a multi-objective optimization in addition to economic cost.
 
-\bibitem{b1} Taylor, J. W., & McSharry, P. E. (2007). Short-term load forecasting methods: An evaluation based on European data. IEEE Transactions on Power Systems, 22(4), 2213-2219.
-
-\bibitem{b2} Hong, T., Pinson, P., & Fan, S. (2016). Global energy forecasting competition 2012 and beyond. International Journal of Forecasting, 32(3), 896-913.
-
-\bibitem{b3} Bacher, P., Madsen, H., & Nielsen, H. A. (2009). Online short-term solar power forecasting. Solar Energy, 83(10), 1772-1783.
-
-\bibitem{b4} Yang, D., Kleissl, J., Gueymard, C.
-A., Pedro, H.
-T.
-C., & Coimbra, C.
-F.
-M.
-(2018).
-History and trends in solar irradiance and PV power forecasting: A preliminary assessment and review using text mining.
-Solar Energy, 168, 60-101.
-
-\bibitem{b5} Zhang, G., Wang, J., & Zhang, W. (2018). Review on probabilistic forecasting of wind power generation. Renewable and Sustainable Energy Reviews, 32(3), 858-872.
-
-\bibitem{b6} Pinson, P., & Kariniotakis, G. (2010). Conditional prediction intervals of wind power generation. IEEE Transactions on Power Systems, 25(4), 1845-1856.
-
-\bibitem{b6i} Grillo, S., Marinelli, M., Massucco, S., & Silvestro, F.
-(2012).
-Optimal management strategy of a battery-based storage system to improve renewable energy integration in distribution networks.
-IEEE Transactions on Smart Grid, 3(2), 950-958.
-
-\bibitem{b7} Costa, A., Crespo, A., Navarro, J., Lizcano, G., Madsen, H., & Feitosa, E.
-(2008).
-A review on the young history of the wind power short-term prediction.
-Renewable and Sustainable Energy Reviews, 12(6), 1725-1744.
-
-\bibitem{b8} Leva, S., Dolara, A., Grimaccia, F., Mussetta, M., & Ogliari, E.
-(2017).
-Analysis and validation of 24 hours ahead neural network forecasting of photovoltaic output power.
-Mathematics and computers in simulation, 131, 88-100.
-
-\bibitem{b9} Hyndman, R. J. (2006). Another look at forecast-accuracy metrics for intermittent demand. Foresight: The International Journal of Applied Forecasting, 4(4), 43-46.
-
-\bibitem{b10} Cirillo, P., & Taleb, N. N. (2020). Tail risk of contagious diseases. Nature Physics, 16(6), 606-613.
-
-\bibitem{b11} Reggiani, P., & Weerts, A.
-H.
-(2008).
-A Bayesian approach to decision-making under uncertainty: An application to real-time forecasting in the river Rhine.
-Journal of Hydrology, 356(1-2), 56-69.
-
-\bibitem{b12} Simpkins, T., Cutler, D., Anderson, K., Olis, D., Elgqvist, E., Callahan, M., & Walker, A.
-(2014).
-REopt: a platform for energy system integration and optimization (Vol.
-45875, p.
-V002T03+006).
-American Society of Mechanical Engineers.
-
-\bibitem{b13} Mishra, S., Pohl, J., Laws, N., Cutler, D., Kwasnik, T., Becker, W., ...
-& Elgqvist, E.
-(2022).
-Computational framework for behind-the-meter DER techno-economic modeling and optimization: REopt Lite.
-Energy Systems, 13(2), 509-537.
-
-\bibitem{b14} Ogunmodede, O., Anderson, K., Cutler, D., & Newman, A. (2021). Optimizing design and dispatch of a renewable energy system. Applied Energy, 287, 116527.
-
-\end{thebibliography}
+\bibliographystyle{IEEEtran}
+\bibliography{mendeley}
 

### 2024-07-16 paper/make.sh

@@ -1,16 +1,15 @@
 #!/bin/bash
-#cp paper.tex ./tex/paper.tex;
-#cp mendeley.bib ./tex/mendeley.bib;
-#cd tex;
+cd paper
+
 pdflatex -interaction=nonstopmode paper;
 bibtex paper;
 pdflatex -interaction=nonstopmode paper;
 pdflatex -interaction=nonstopmode paper;
-#rm paper.tex
-#rm mendeley.bib
-#mv paper.pdf ../paper.pdf
+
+#mv paper.pdf paper/paper.pdf
 
 rm paper.aux;
 rm paper.bbl;
 rm paper.blg;
-rm paper.log;
+#rm paper.log;
+rm paper.out;
